### 2019-05-13 article.tex
Initial commit, need to transform journal to conference tempalte

\documentclass[sigconf, review=true, screen=true, anonymous=true]{acmart}

\usepackage{booktabs}
\usepackage[ruled]{algorithm2e} % For algorithms

\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}

\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmJournal{TAP}
%\acmVolume{9}
%\acmNumber{4}
%\acmArticle{39}
%\acmYear{2010}
%\acmMonth{3}
%\acmArticleSeq{11}

%Copyright
\setcopyright{usgovmixed}

% DOI
\acmDOI{0000001.0000001}

% Paper history
\received{March 2018}

\begin{document}

\title{An Audio Interface for an Active Perception Navigation Aid for Blind People}

\author{Jacobus C. Lock}
\affiliation{%
  \institution{University of Lincoln}
  \streetaddress{Brayford Pool}
  \city{Lincoln}
  \state{Lincolnshire}
  \postcode{LN6 7TS}
  \country{United Kingdom}}

\author{Iain Gilchrist}
\affiliation{%
  \institution{University of Bristol}
  \streetaddress{Priory Road}
  \city{Bristol}
  \state{Bristol}
  \postcode{BS8 1TU}
  \country{United Kingdom}}

\author{Grzegorz Cielniak}
\affiliation{%
  \institution{University of Lincoln}
  \streetaddress{Brayford Pool}
  \city{Lincoln}
  \state{Lincolnshire}
  \postcode{LN6 7TS}
  \country{United Kingdom}}

\author{Nicola Bellotto}
\affiliation{%
  \institution{University of Lincoln}
  \streetaddress{Brayford Pool}
  \city{Lincoln}
  \state{Lincolnshire}
  \postcode{LN6 7TS}
  \country{United Kingdom}}

\begin{abstract}
	Our aim is to build a portable active navigation system for the visually impaired that uses active perception techniques and a combination of feedback modes to identify a scene and guide the user to his/her destination. In this paper, we investigate the effectiveness of a spatial audio tone with a varying pitch component, played through bone-conducting headphones, in conveying the pan and tilt angles of a target to the user in a pointing task. We also wish to see how changes to the rate of change of the pitch affects the user's performance. We conducted a set of experiments with blindfolded and visually impaired users and found that the varying pitch component gives an average error of approximately \SI{20}{\degree} when searching for a target; in line with previous results from other authors. Furthermore, we were able to demonstrate that the audio interface adheres to Fitts's Law and used it as a metric to determine which pitch setting produces the best results. We discovered a trade-off between the speed and accuracy in the pointing task, which are maximised when the tone's pitch is adjusted to a low and high rate of change respectively. 
\end{abstract}

 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003121.10011748</concept_id>
<concept_desc>Human-centered computing~Empirical studies in HCI</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10003122.10003334</concept_id>
<concept_desc>Human-centered computing~User studies</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Empirical studies in HCI}
\ccsdesc[300]{Human-centered computing~User studies}

\keywords{Human-machine interface, vision impairment, navigation aid, spatialised sound, Fitts's Law, pointing task}

\maketitle
\renewcommand{\shortauthors}{JC Lock et al.}

\section{Introduction}

In recent years, governments have spearheaded numerous initiatives to support people with disabilities and enable them to play a more active role in modern society. In the UK, the Royal National Institute of Blind People (RNIB) has prioritised enabling people with visual impairments to use some of the services and products many people take for granted, such as public transport and cellphones~\cite{rnib-objectives}. Improvements in modern computing have made it possible for new and innovative solutions for these problems to come to the fore. In particular, researchers in the field of active vision have have made much progress in allowing a machine to autonomously manipulate a camera to gain more information about an environment to complete mapping and object and face tracking tasks, for example~\cite{bajcsy2018revisiting}. There is, however, a significant research question about whether techniques from active machine vision can be applied to humans, i.e.\ can a machine identify a point of interest in a scene and direct a human, instead of an electronic servo, to focus a camera on that point? If this can be done, it would be beneficial to people with visual impairments and will allow them to search for an arbitrary point of interest or identify an unknown scene.

To this end, we are developing a mobile device-based navigation system using a Google Project Tango device\footnote{https://developers.google.com/tango}, pictured in Fig.~\ref{fig:tango-headphone}, that caters to the perception limitations of people with limited vision by using a non-visual interface. This system will ultimately allow users with visual impairments to reach a target location in the final leg of their journey, i.e.\ the so-called `last 10 yards' problem~\cite{google2016blind,bellotto2013}. The ideas here can also be extended and applied to existing macronavigation tools, such as Google Maps. A Tango-enabled device comes pre-equipped with powerful image-processing, localisation and depth-perception capabilities and is built on top of a standard Android platform, providing access to the entire set of input/output options that this operating system has to offer. The final system will use multiple feedback modes (vibration, audio and voice) to guide a user toward a target destination while providing information on any oncoming obstacles.

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=0.85\textwidth]{figures/tango_headphone.png}
    \caption{The Tango device and bone-conducting headset used by the participants. }
    \label{fig:tango-headphone}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/camera_coordinate.pdf}
    \caption{A diagram showing the Tango's frame of reference and the target's pan ($\phi$) and tilt ($\theta$) angles.}
    \label{fig:cam-coords}
  \end{subfigure}
  \caption{The hardware used during the experiment, as well as a diagram showing the Tango device's coordinate system. }
\end{figure}

In this paper we focus on the audio feedback mode and discuss how it is used in our system. We present experiments we performed to determine its effectiveness at directing a user to complete a pointing task and how its parameter values affect a user's target-search performance. For the pointing task, we presented blindfolded and partially sighted participants with a set of virtual targets, one after another, and asked them to simply point a camera to where they thought the targets were. The targets' pan and tilt angles w.r.t.\ the Tango's vertical plane, shown in Fig.~\ref{fig:cam-coords}, were given to the participants through a spatial tone with varying pitch played via a set of bone-conducting headphones. We use the latter to not interfere with the user's normal hearing function, which people with visual impairments typically rely on. Because these headphones bypass the external structure of the ear responsible for localising a sound source's elevation, it is necessary to convey the target's tilt angle using another method. Therefore, we opted for a tone with varying pitch to convey the angle adjustment required to point the camera in a particular direction.

Unfortunately, there is a gap in the literature regarding the use of a such an audio interface for pointing tasks with regards to a mobile device. It is also unclear whether popular metrics, such as Fitts's Law~\cite{fitts1954information}, can be applied in this case. Fitts's Law is a predictive model in the field of psychomotor research and often used in the human-machine interfacing field that relates the time it takes a user to direct a pointing device toward a target as a function of the difficulty of finding the target (i.e.\ the ratio between the distance to the target and its size). If a Fitts relationship is found, it can be used as a metric to anticipate whether future adjustments to the pitch's rate of change will have a positive effect on target-search performance.

The main contributions of this paper are two-fold:

\begin{itemize}
  \item we provide the first experimental results on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with bone-conducting headsets; 
  \item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
\end{itemize}

The remainder of this paper is organised as follows: Section~\ref{sec:lit-review} gives an overview of existing navigation systems and audio interfaces for people living with visual impairments. Section~\ref{sec:portable-navigation} discusses the navigation device's hardware and interface setup and describes how the pan and tilt angles are conveyed to the user. The experiments that were conducted are explained in Section~\ref{sec:experiments} and the results are presented and discussed in Section~\ref{sec:results}. Finally, Section~\ref{sec:conclusion} concludes this paper with a summary of the findings and comments on our future work.

\section{Previous Work}
\label{sec:lit-review}

Attempting to deliver a system that allows people with visual impairments to independently navigate and accomplish everyday tasks is not new; in fact, there are multiple commercial systems and research prototypes already available on the market. One approach that has been investigated is to outfit the existing white walking cane with various sensors, such as sonar, radar, motor encoders, etc.~\cite{ulrich1997, marion2008batcane} to warn the user of upcoming obstacles, instead of relying on haptic feedback from the impact between the cane and the obstacle. Another approach is to outfit a walking cane to act as a radio-frequency identification (RFID) antenna that can read a set of RFID tags placed at strategic locations around the environment at key spots or along a path~\cite{faria2010electronic, willis2005}. This modification to the traditional cane is more discreet than the systems mentioned earlier and has been shown to work well. Bluetooth tags and a smartphone can also be used in a similar manner~\cite{sato2017navcog3}. However, the major drawbacks here are the significant cost and effort of modifying existing infrastructure with RFID and Bluetooth tags and maintaining them to stay up to date with a changing environment. GPS-based systems~\cite{ran2004drishti, loomis2001navigating, kammoun2012navigation}, while cheap and reliable in outdoor environments, are not applicable in built-up urban areas and indoors where GPS signals are notoriously unreliable. Computer vision-based systems provide a good compromise between usability, cost and accuracy and have been the focus of much research recently~\cite{manduchi2014last}. One increasingly popular solution is to use RGB-D depth sensing cameras, which are becoming increasingly more accurate and cost-effective, to build a 3D image map of the environment, allowing a user to safely traverse through it~\cite{lee2015, rodriguez2012obstacle}. Another approach is to use vision-based object recognition techniques to detect various objects and landmarks, such as doors, staircases, etc., and communicate their relative location to the user~\cite{schauerte2012assistive, tian2013b, fiannaca2014headlock}, or use audio instructions to instruct a user with vision impairment to fully capture an object of interest~\cite{vazquez2012helping}.

An important feature of user-centric systems is a human-machine interface (HMI) that enables effective and seamless two-way communication between the system and the user. In previous surveys, researchers found that people with visual impairments prefer receiving feedback and instructions in the form of speech and haptic feedback cues~\cite{khoo2016multimodal, ross2000wearable, vazquez2012helping}. However, haptic feedback modes typically have a lower bandwidth when compared to audio feedback and also require the user to wear a special device in order to transmit the haptic signals to the user effectively. Work has also been done in translating a visual scene into non-visual formats, with so-called sensory substitution systems (e.g. `The Voice'~\cite{meijer2010}) and virtual audio reality (VAR) systems~\cite{frauenberger2003} reporting favourable results. However, The Voice, while helpful, has a very steep learning curve that has proven to be a significant barrier to entry. With VAR systems, it is not clear how unknown environments, where markers have not yet been encoded, would be handled and described to the user.

%####################################################
REVIEW SECTION - MAKE SURE TO MENTION DIFFERENCE BETWEEN BLIND AND SIGHTED , sonification of 3d scenes in an electronic travel aid for the blind.
Spatial audio has also been considered to convey the direction of a target. Experiments have previously determined that people are able to find the location of a stationary sound source with an error of $\pm$\SI{35}{\degree}, in both the pan and tilt dimensions~\cite{zwiers2001spatial}, for both early-blind and normally-sighted people. However, in~\cite{lewald2013exceptional, lessard1998early} it was found that the blind have a clear advantage in localisation accuracy over sighted people when presented with more difficult tasks, such as targets in motion and narrow-band stimuli, with~\cite{lewald2013exceptional} reporting an average absolute localisation error of around \SI{10}{\degree} in the pan and tilt dimensions. Other authors found that the minimum difference in the spatial sound's angle for the user to be able to perceive movement is approximately \SI{1.7}{\degree}. During the experiments, an audio speaker was physically manoeuvred to provide the participant with a spatialised sound tone~\cite{ashmead1998spatial}. Researchers have also tried using simulated spatial audio to inform the user from which direction a sound is originating~\cite{holland2002audiogps, kammoun2012navigation, rebillat2009smart, menelas2010audio, wilson2007swan, zotkin2004rendering}. In these works, a sound was played through a set of headphones and the source spatialised with a head-related transfer function (HRTF), tricking the listener into thinking the sound source was located at some arbitrary 3D location. Various audition techniques and methods were then used to guide the user along a path. Other authors have also provided a framework for evaluating the quality of this 3D sound in terms of its psychoacoustic properties~\cite{guastavino2004perceptual, nicol2014roadmap}. There are also experimental results about how well users can find targets presented with spatial sound in the tilt and panning dimensions with normal headphones~\cite{katz2011spatial, zwiers2001spatial}, as well as work that has shown similar levels of localisation performance between normal and bone-conducting headphones in the pan dimension~\cite{macdonald2006spatial}. However, to our knowledge no extensive work or experiments have been done to determine how well users respond to tilt adjustment instructions using a tone with \emph{varying pitch}, in particular when using bone-conducting headphones. 
%########################################################

Researchers have previously used Fitts's Law~\cite{fitts1954information}, and more recently MacKenzie's modified version of it~\cite{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@. Fitts's Law was originally proposed for visual target search tasks. However, it has been applied in non-visual target search tasks as well. For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\cite{ahmaniemi2009augmented}. The authors showed that the search time adheres to Fitts's Law. However, they also note that it is not a perfect fit, citing the fact that Fitts's Law does not take into account a user's search strategy. Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\cite{marentakis2006effects}. Here, participants pointed to where they thought the targets were, on their left or right, as they traversed a path. Their results show a good relation between target difficulty and search time, providing a strong argument that Fitts's Law can be used to describe the performance of a spatial audio interface. These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\cite{wu2010fitts}. However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.

\section{Portable Navigation System}
\label{sec:portable-navigation}

\subsection{System Setup}

The system we intend to ultimately deliver is a portable navigation device that is capable of guiding a user with visual impairments on the last leg of their journey, e.g.\ to a specific aisle and shelf in a shop. To do this, we will use a combination of different feedback modes to facilitate two-way communication between the user and the device. A large amount of data need to be translated from a visual form into a format that is useful to people with limited or no vision. We therefore plan to use a combination of voice, audio and vibration cues to translate the visual navigation data as effectively as possible and overcome the bandwidth limitation of the human ear.

The system is based on a concept proposed in~\cite{bellotto2013, lock2017portable}, which uses a Google Tango device. This is an Android-based cellphone or tablet device that comes equipped with an RGB-D camera to sense colour and depth. It combines an inertial measurement unit with powerful and robust landmark recognition and image processing algorithms to localise itself. An added benefit of this platform is its familiar, compact form-factor which will help overcome the hurdle of user-acceptance and usability.

We use a set of bone-conducting headphones (see Fig.~\ref{fig:tango-headphone}) that are placed externally on the user's head so that the system does not occlude the perception of real-world sounds and does not interfere with a user's normal hearing function. In the future, our system will use multiple feedback modes to provide the user with navigation and obstacle avoidance instructions. However, for this paper, we only considered the spatialised audio mode and its variation in pitch in order to determine its effectiveness in conveying a target's pan and tilt angles.

A diagram of the experimental system pipeline is shown in Fig.~\ref{fig:pipeline}. Here, the arrows indicate the direction of the flow of information. When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the Tango's current position and orientation. The audio generator then produces a tone based on the difference between the Tango and the target's positions (in the Tango's global coordinate system) and sends it to the audio output channel, which plays it back to the user. The WiFi recording module is constantly monitoring the different parameter values of the Tango and target's positions, as well as the system's output, and records it to a remotely stored datafile.

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=50 120 80 50, width=0.55\textwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }
\label{fig:pipeline}
\end{figure}

\subsection{Audio Interface}

For the series of experiments performed in this work, only the audio feedback mode was used to interface with the user. The audio component is responsible for conveying the 2D position of a target on the vertical plane w.r.t.\ the Tango's coordinate system, showed in Fig.~\ref{fig:cam-coords}, in terms of pan and tilt angles. Distance to the target can be rendered by adjusting the audio signal's amplitude as a function of the distance. However, in this work, this was not implemented. The audio signal is a sinusoidal sound wave that is continuously played (refreshed at $\sim$\SI{10}{\hertz}) to the user through bone-conducting headphones. We select a sinusoidal wave because it is relatively simple to manipulate and analyse. A richer and more natural tone will be implemented at a later stage of the project.

The audio is spatialised in the pan dimension using an HRTF provided by the OpenAL sound library\footnote{http://openal.org}, while the tilt angle is conveyed by varying the pitch of the audio tone. We use this approach because the external set of bone-conducting headphones plays the sound through the user's cheekbones instead of their outer ears, bypassing the ears' pennae that provide humans their ability to localise elevated sound sources~\cite{roffler1968factors, algazi2001elevation}. This makes an HRTF less effective in conveying the target's tilt angle and therefore needs to be conveyed using another method; a varying pitch tone in this case. The difference between the target's angular position and the angular orientation of the Tango device are used to generate the audio signals.

\subsubsection{Pan Direction}

The pan angle describes the angle which the user needs to rotate the camera vector around the vertical $z$-axis in Fig.~\ref{fig:cam-coords}, i.e.\ how far the target is to the left or right of the user. We use an HRTF to add a spatial element to the audio tone that the system plays to the user, making the tone sound like it is coming from the direction of the target. Humans determine the pan direction by subconsciously analysing the time difference between a sound reaching both of your ears. For example, if you hear a sound in your left ear first, you interpret the sound as coming from your left. The greater the so-called inter-aural time difference~\cite{wightman1992dominant}, the greater the perceived angular distance to the sound source.

We implement OpenAL's default HRTF, based on the MIT's KEMAR dataset\footnote{http://sound.media.mit.edu/resources/KEMAR.html}, to generate a sinusoidal sound wave based on the difference between the user and target's positions. The library takes position values as input and outputs a tone based on the angle between the two position vectors.

\subsubsection{Tilt Direction}

The system adjusts the tone's pitch to convey the target's tilt angle w.r.t.\ the camera's current pointing vector, $C$, as shown in Fig.~\ref{fig:cam-coords}. Here, a high pitch means the target is above the camera vector (i.e.\ the user should look up) and a low pitch means the target is below the camera vector (the user should look down). This high/low association scheme is chosen because humans naturally associate high-pitched sounds with higher objects and lower-pitched noises with lower objects~\cite{pratt1930spatial, blauert1997spatial}. We use a logarithmic, octave-based gain function for the pitch, since an increase in octave provides a distinct perceptible change while keeping the timbre roughly constant~\cite{shepard1964circularity}.

We wish to determine how the gradient of the pitch gain function affects a user's performance. For example, does an increased gain rate in the pitch as a function of the tilt angle lead to an increased target acquisition rate? For this we select three different pitch gain gradients, referred to here as low (\emph{lo}), medium (\emph{med}) and high (\emph{hi}) gain presets. To find these gradients, we set the maximum and minimum limits for the tilt angle and the maximum and minimum frequencies for the pitch. Furthermore, for the sake of consistency, each gradient setting is set to generate the same pitch when the user is pointing the camera towards the target.

After practical tests with the Tango and headphones, we set the neutral, on-target tone to a frequency of \SI{512}{\hertz} for its audibility. For the \emph{lo} setting, we set the maximum and minimum pitches to be one octave higher and lower than the neutral tone, giving limits of \SI{1024}{\hertz} and \SI{256}{\hertz} respectively. The \emph{med} preset is set to two octaves higher and lower than the neutral tone (\SI{2048}{\hertz} and \SI{128}{\hertz}) and the \emph{hi} to three octaves higher and lower (\SI{4096}{\hertz} and \SI{64}{\hertz}). We selected these limits for practical reasons, given the fact that the bone conducting headphones we use have low volume gain at very high and low frequencies, making it difficult to hear.

The frequency is selected using Equation~\ref{eq:pitch-eq}, where $\theta$ is the tilt angle and $m$ and $c$ are parameters calculated using a linear equation (seen in Equation~\ref{eq:linear}) and the cut-off frequency values. Here, $y_m$ is a cut-off frequency, $x_m$ its corresponding angle and $m$ the gradient for the setting, calculated as $m = \frac{\Delta y}{\Delta x}$. The pitch gain functions are shown in Fig.~\ref{fig:pitch-gain}.

\begin{equation}
  \label{eq:pitch-eq}
  f = 2^{-m \theta + c}
\end{equation}

\begin{equation}
  \label{eq:linear}
  y - y_m = m(x - x_m)
\end{equation}

\begin{figure}
  \centering
  \includegraphics[width=0.55\textwidth]{figures/pitch_gain_functions.png}
  \caption{The pitch gain functions for the 3 different gain settings. }
  \label{fig:pitch-gain}
\end{figure}

The \SI{0}{\radian} position is directly in front of the user. We set the range of angles the system can convey to $[-\frac{\pi}{2}; \frac{\pi}{2}]$; anything outside this range implies that the target is behind the user, and was therefore not considered in this series of experiments.

\section{Experiments}
\label{sec:experiments}

We performed a set of experiments with our audio interface to determine how effective it is at directing a user to adjust the pan and tilt angles of a camera for point it to a target. Furthermore, we also carried out a set of pre-screening experiments to determine each participant's hearing characteristics. The participants were given time before the experiments commenced to familiarise themselves with the device and the tones it emits, as well as what the `on-target' tone sounds like. We also tested the system with 3 legally blind participants and compared their data to the blindfolded dataset. Furthermore, these tests provided us with subjective feedback on the system that can be used to improve future iterations of the system. The results from the experiments we performed allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimise the behaviour of the feedback modes in our portable navigation aid.

\subsection{Experimental Procedure}

For the experiments we used two groups of participants, with one including 42 sighted and blindfolded participants and the other 11 legally blind volunteers with varying degrees of vision impairment. We refer to these 2 groups as G1 and G2.
%(see Fig.~\ref{fig:participants} for pictures of two participants during the experiments)
The participants of each group performed a series of experiments using our system with a pair of bone-conducting headphones.
The participants were recruited on a volunteer-basis and consisted of a diverse group of undergraduate students, professionals and retirees with ages ranging between 17 and 95 years (18 male, 35 female).
Some of the participants were using hearing aids.
However, this was not an issue, since we used bone-conducting headsets which bypass the outer ear structure and the hearing aids.

The participants took part in three experiments.
The first two were performed to determine each participant's hearing characteristics and provide some context to the results generated during the target-search experiment.
These characterisation experiments also indicate any pre-existing biases the participant-base might have in their hearing behaviour for our third, target search experiment.

%\begin{figure}
  %\centering
  %\begin{subfigure}[t]{0.45\textwidth}
    %\centering
    %\includegraphics[width=0.5\textwidth]{figures/sighted_participant.png}
    %\caption{A sighted and blindfolded participant. }
  %\end{subfigure}\hfill
  %\begin{subfigure}[t]{0.45\textwidth}
    %\centering
    %\includegraphics[width=0.5\textwidth]{figures/vi_participant2.jpg}
    %\caption{A visually impaired participant. }
  %\end{subfigure}
  %\caption{Participants in the study using the Tango device during the target-search task. }
  %\label{fig:participants}
%\end{figure}

The distance between a participant and the target is not considered here and the 3D targets are therefore generated at a constant distance of \SI{2}{\metre} from the participant.
Throughout the experiments, various parameters of the target and the participant are recorded and streamed in real-time to a laptop computer via a WiFi connection.
Prior to the target search experiment, participants from G1 were given a few minutes without a blindfold to familiarise themselves with the system and the audio tone's behaviour as the target's position changes.
This was done verbally with the participants from G2 to inform them of the pitch they were aiming for that indicated that they were on-target.

\subsection{Participant Characterisation}

\subsubsection{Spatial Awareness}

In this experiment, we evaluated a participant's ability to determine the lateral direction a sound is coming from.
To do this, we played a continuous \SI{512}{\hertz} sinusoidal tone to the participant through the headphones and applied an HRTF to spatialise and place its source to the participant's left or right.
The participant then had to select the direction the sound came from.
The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly difficult to distinguish between the left and right direction of the sound.

For this progressive increase in difficulty, a 2-up, 1-down step procedure is used~\cite{wetherill1965sequential,levitt1971transformed}, meaning that for every 2 correct answers, the distance to the centre-front halves, making the lateral direction harder to determine.
Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre-front.
We also set  different step sequences: one starting at a large angular distance (\SI{45}{\degree}) from the participant's centre-front and the other at the minimum angular distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' step respectively.
The terminating condition for the experiment is when the hard and easy step sequences converge to within 2 steps of one another (i.e.\ the difference between the hard and easy sequences are 4 times larger or smaller than one another) for 3 consecutive guesses.
This gives an angular distance band which indicates each participant's ability to localise the sound source's lateral position.
Each participant performed this experiment three times.

\subsubsection{Pitch Discrimination}

Next we determined each participant's ability to differentiate an audio tone's pitch, i.e.\ how well they can tell if a tone is high or low pitched.
We played 2 tones after another to each participant, with the second tone being higher or lower-pitched than the first tone.
The participants then had to indicate whether they thought the second tone as higher or lower-pitched than the first.

The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first.
This tone difference depends on how well the participant can tell the tones apart.
Like the spatial awareness experiment, a 2-up, 1-down step process is used: for every 2 consecutive correct answers, the pitch difference between the tones is halved, and the difference is doubled for every incorrect answer.
Two step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}). 
The termination condition is when the two step sequences are within one octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2^1$) for 3 consecutive answers.
Each participant performed this experiment twice.

\subsection{Target Search}

\subsubsection{Task Description}

The final experiment is the main one and will answer the question we are most interested in: how well does a spatial tone with varying pitch direct a person to look in a specific direction, and how do the parameters of this tone affect a person's performance in this task?

For this experiment, the participants given a Tango device running an app purpose-written for this experiment.
When started, a set of virtual targets were presented one at a time to each participant on the Tango device.
Then, depending on the direction the participant was currently pointing the camera relative to the target's position, the Tango generated and played an audio tone via bone-conducting headphones to indicate the pan and tilt angle adjustment required to point the camera to the target.
%These instructions are spatialised tones with varying pitch: an HRTF indicates the pan direction (left or right) and the pitch indicates whether the participant should be looking up (high pitch) or down (low pitch) to find the target.

Once a participant pointed the Tango's camera toward the target, the system generated a neutral tone with a pitch of \SI{512}{\hertz}, which we used as the `on-target' pitch for all of our experiments.
A participant then had to manually confirm the direction they believed the target was after hearing the tone's pitch change to the \SI{512}{\hertz}, on-target tone, and tap the screen to confirm the location.
At this point a new search target was presented and the process was repeated.
To minimise any speed/accuracy trade-off bias in the results, we asked the participants to search for the targets without placing particular emphasis on accuracy or time.

A total of 28 targets were presented to each participant per experiment run.
The positions of these targets were randomly generated and equally spread across the 4 quadrants on the vertical plane to prevent a clustering of targets at the same location.
After every experiment run, the parameters controlling the tone's behaviour were adjusted.
In this case, the rate of change of the tone's pitch was adjusted to make the pitch increase at a lower or higher rate as a function of the tilt angle between the target and the participant's current pointing direction.
This was done to determine whether, for example, a more rapid increase in pitch would help the participant find the target faster or more accurately. 
The order in which the settings were set for each participant was randomised in order to minimise any learning effect the participant population might display between experiments.

\subsubsection{Metrics}

We use 2 different metrics to compare the 3 different pitch gradient settings, namely target acquisition accuracy and search time.
The accuracy is given as the difference between the location the Tango's camera was pointing at the time a participant selected a target's location and the target's actual position.
We separate the results of the tilt and pan dimensions in order to see how the different pitch gradients affect a participant's pointing accuracy.

We also compare the performance of the 3 pitch gradient settings in terms of the time it took each participant to find a target.
However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
Instead, we use Fitts's Law~\cite{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\cite{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty (the ratio between the distance to the target and its width).
It also provides us with an additional metric called the `index of performance' that we can use to compare the results between the 3 configurations. 
Here we briefly summarise the equations and quantities involved in this metric. 
Fitts's Law is given by

\begin{equation}
  \label{eq:fitts-base}
  t = a + bID,
\end{equation}

\noindent
where $t$ is the time it takes to find a target, $a$ and $b$ are constants determined through regression and $ID$ is a target's index of difficulty, given as logarithmic function of the ratio between the distance to the target and the target's width.
In this case, the targets have no width since they are points in space, and we use MacKenzie's modified form for $ID$, given by

\begin{equation}
  \label{eq:fitts-id}
  ID = \log_2\left(\frac{\theta}{w_e} + 1\right).
\end{equation}

\noindent
Here $\theta$ is the angular distance between subsequent target centres and $w_e$ is the targets' effective angular width~\cite{welford1968fundamentals}, given by

\begin{equation}
  \label{eq:fitts-we}
  w_e = \sqrt{2\pi e}\sigma = 4.133\sigma,
\end{equation}

\noindent
where $\sigma$ is the standard deviation of the error data, taken as the angle between a participant's target selection and the target's actual position. 
Fitts's index of performance, $IP$, can then be calculated with

\begin{equation}
  \label{eq:fitts-performance}
  IP = \frac{ID}{t},
\end{equation}

\noindent
where $IP = \frac{1}{t}$ when $\sigma=0$.

\section{Experiment Results and Discussion}
\label{sec:results}

\subsection{Participant Characterisation}
\label{sec:character}

Fig.~\ref{fig:location-guesses} shows the results for the spatial awareness experiment in the pan direction where each participant determined the location of the sound they were played.

\begin{figure}
  \centering
  \includegraphics[clip, trim=100 20 150 100, width=0.5\textwidth]{figures/location_guesses_sighted.png}
  \caption{Histograms of the spatial awareness experiment in the pan dimension showing the proportion of correct/incorrect guesses per bin interval. }
  \label{fig:location-guesses}
\end{figure}

MEME INSERT BLIND FIGURE

With a relatively low number of erroneous guesses, we see that the participants were accurate in guessing the location of the sound source.
This is further supported by the large number of samples at the minimum difference of \textasciitilde\SI{3}{\cm}, indicating that the participants reached this level more frequently and consistently. We can therefore conclude that the participants had little difficulty determining the pan angle of a sound source. These results are in line with what we expected and they are supported by literature which indicates that humans are very adept at localising a sound source, and this ability was apparent for the HRTF-generated pan locations.

The results recorded during the pitch discrimination experiment are shown in Fig.~\ref{fig:tone-guesses}, where a bar plot is used to show the number of correct guesses for each tone difference level. The latter is given in terms of the relative semitone difference between the tones which are obtained using the following relation:

\begin{equation}
\label{eq:semitone-difference}
  \Delta f = 12\log_2\frac{f_0}{f_1}.
\end{equation}

From Fig.~\ref{fig:tone-guesses-sighted}, we can see that the guesses are normally spread around a 0 semitone difference for the blindfolded participants in G1, with roughly an equal number of samples with positive and negative difference values.
As expected, a larger proportion of incorrect guesses occur around the smaller differences with the majority of samples for correct and incorrect guesses being recorded in the $[-0.25, 0.25]$ semitone difference level.
However, the results from the participants from G2 in Fig.~\ref{fig:tone-guesses-blind} are less evenly spread and more concentrated around the 0 semitone difference level, with a skewing of wrong guesses values towards the positive side, possibly indicating a perception bias amongst our pool of participants with vision impairments. However, one possible reason for this bias may simply be a lack of data, and we may see that more samples from larger group of participants with vision impairments in G2 would provide a more normal spread, similar to the plot in Fig.~\ref{fig:tone-guesses-sighted}.

Assuming these differences are normally distributed, we fitted a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
We then used the CDF's parameters to determine the semitone difference where a participant could could no longer reliably tell tones apart.
%See Fig.~\ref{fig:cdf-semitone} for an example showing the actual CDF of a participant and its approximated normal CDF\@. 
We set this threshold to a difference level that includes 75\% of the correct guesses.
We found that the median threshold is approximately 0.28 semitones for G1 and 0.22 semitones for G2.
We used the absolute values of the difference data and therefore used the median values of the data an ANOVA of the 2 threshold sets show that there is no significant difference between the 2 groups ($p=0.99$).
The plot showing the participants' threshold distribution can be seen in Fig.~\ref{fig:tone-threshold}.

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=80 0 150 100, width=0.95\textwidth]{figures/tone_guesses_sighted.png}
    \caption{Results for G1. }
    \label{fig:tone-guesses-sighted}
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=120 0 120 70, width=0.95\textwidth]{figures/tone_guesses_blind.png}
    \caption{Results for G2. }
    \label{fig:cdf-semitone-blind}
  \end{subfigure}
  %\begin{subfigure}[t]{0.5\textwidth}
    %\centering
    %\includegraphics[clip, trim=120 0 120 70, width=0.95\textwidth]{figures/cdf_tone_guesses.png}
    %\caption{Cumulative distribution of the number of correct guesses for one participant. }
    %\label{fig:cdf-semitone}
  %\end{subfigure}
  \caption{Histograms of the tone limit experiment showing the proportion of correct/incorrect guesses per bin interval. }
  \label{fig:tone-guesses}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=80 20 120 0, width=0.95\textwidth]{figures/tone_threshold_sighted.png}
    \caption{Results for G2. }
    \label{fig:tone-threshold}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=80 20 120 0, width=0.95\textwidth]{figures/tone_threshold_blind.png}
    \caption{Results for G2. }
    \label{fig:tone-threshold}
  \end{subfigure}\hfill
  %\begin{subfigure}[t]{0.5\textwidth}
    %\centering
    %\includegraphics[clip, trim=80 20 120 0, width=0.95\textwidth]{figures/tone_medians_sighted.png}
    %\caption{A distribution of the median cut-off frequency thresholds along with the median 75\% cut-off threshold. }
    %\label{fig:tone-medians}
  %\end{subfigure}
  %\caption{Distribution plots showing the cut-off frequencies for the sample group. }
  \caption{A distribution of the 75\% cut-off frequencies. }
\end{figure}

\subsection{Target Search}

\subsubsection{Panning Results}

The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in Figs.~\ref{fig:err-results-lo} to~\ref{fig:err-results-hi}, where the angular errors in the pan and tilt directions are plotted against each other for both participant groups.
A set of box-plots of the pan errors' medians and standard deviations for each setting are also given in Figs.~\ref{fig:err-boxplots-medians} and~\ref{fig:err-boxplots-stds} and the results for both groups are summarised in Table~\ref{tab:results}.

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_lo_sighted.png}
    \caption{Results for G1. }
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_lo_blind.png}
    \caption{Results for G2. }
  \end{subfigure}
  \caption{\emph{Lo} setting. }
\label{fig:err-results-lo}
\end{figure}
\begin{figure}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_med_sighted.png}
    \caption{Results for G1. }
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_med_blind.png}
    \caption{Results for G2. }
  \end{subfigure}
  \caption{\emph{Med} setting. }
\label{fig:err-results-med}
\end{figure}
\begin{figure}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_hi_sighted.png}
    \caption{Results for G1. }
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_hi_blind.png}
    \caption{Results for G2. }
  \end{subfigure}
  \caption{\emph{Hi} setting. }
\label{fig:err-results-hi}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[clip, trim=30 -70 100 0, width=0.95\textwidth]{figures/err_boxplot_medians_sighted.png}
    \caption{Results for G1.}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[clip, trim=30 -70 100 0, width=0.95\textwidth]{figures/err_boxplot_medians_blind.png}
    \caption{Results for G2. }
  \end{subfigure}
  \caption{Boxplots of the medians for the pan and tilt error results from the target search experiment.}
  \label{fig:err-boxplots-medians}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[clip, trim=80 -70 100 0, width=0.95\textwidth]{figures/err_boxplot_std_sighted.png}
    \caption{Results for G1.}%
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[clip, trim=80 -70 100 0, width=0.95\textwidth]{figures/err_boxplot_std_blind.png}
    \caption{Results for G2.}
  \end{subfigure}
  \caption{Boxplots of the standard deviations for the pan and tilt error results from the target search experiment.}
  \label{fig:err-boxplots-stds}
\end{figure}

\begin{table}
  \centering
  \caption{A table of the pan and tilt angular error results for the target search experiment. The results include the absolute average error ($\mu_{abs}$), average error ($\mu$) and standard deviations ($\sigma$) given in radians, as well as the Spearman ($R$) correlation scores.}
  \label{tab:results}
  \begin{tabular}{cclcccc}
    \toprule
    \multicolumn{3}{c}{} & $\mu_{abs}$ & $\mu$ & $\sigma$ & $R$ \\\midrule
    \multirow{6}{*}{G1}  & & \emph{lo}  & 0.23 & -0.02 & 0.32 & 0.75 \\
	 & Pan [rad] & \emph{med} & 0.21 & -0.01 & 0.28 & 0.77 \\
	 & & \emph{hi}  & 0.22 & -0.05 & 0.31 & 0.75 \\\cmidrule{3-7}
	 & & \emph{lo}  & 0.40 & -0.14 & 0.46 & 0.38 \\
	 & Tilt [rad] & \emph{med} & 0.32 & -0.12 & 0.36 & 0.48 \\
	 & & \emph{hi}  & 0.34 & -0.16 & 0.39 & 0.55 \\\midrule
    \multirow{6}{*}{G2} & & \emph{lo}  & 0.42 & -0.01 & 0.48 & N/A \\
	 & Pan [rad] & \emph{med} & 0.42 & 0.07 & 0.49 & 0.14 \\
	 & & \emph{hi}  & 0.40 & 0.05 & 0.48 & 0.13 \\\cmidrule{3-7}
	 & & \emph{lo}  & 0.52 & -0.50 & 0.38 & 0.14 \\
	 & Tilt [rad] & \emph{med} & 0.44 & -0.41 & 0.34 & 0.32 \\
	 & & \emph{hi}  & 0.41 & -0.38 & 0.33 & 0.36 \\
    \bottomrule
  \end{tabular}
\end{table}

The results in Figs.~\ref{fig:err-results-lo} to~\ref{fig:err-results-hi} for both groups suggest that the data in the pan dimension are approximately normally distributed around \SI{0}{\degree}, at least visually.
However, results from the Shapiro-Wilkes test that fall below the critical threshold, $\alpha=0.05$, and inspection of the quantile-quantile (Q-Q) plots do not give enough confidence to consider the data as normally distributed and we therefore analyse the data using non-parametric techniques.

%####################################################################################################################
%####################################################################################################################
%####################################################################################################################
%####################################################################################################################
%####################################################################################################################

For the participants in G1, there is a strong linear correlation between the participants' guesses and the targets' true pan angles, shown by the high Spearman correlation scores of approximately 0.75 ($p < 0.001$) for all of the datasets, with the \emph{med} configuration displaying the marginally best result of 0.77.
The three settings have similar average errors and standard deviations around \SI{0}{\radian}, with the \emph{med} setting again producing the marginally best results with the smallest average error and standard deviation.
However, the differences are small (approximately 6\%) and are not significant enough (Friedman test $p=0.3>\alpha$) to conclude that the pitch gradient has an effect on the performance in the pan dimension.
With very low Spearman, or statistically insignificant, scores, the data for G2 show that there is a very weak positive relationship between the targets' pan positions and the participants' guesses. 
The pan angle error is still centred around \SI{0}{\radian}, but displays a wider spread with a larger standard deviation and absolute mean than the errors in G1. 
These statistical results are listed in Table~\ref{tab:err-results}.

\begin{table}
  \centering
  \caption{A table summarising Friedman ($T_F$) and Wilcoxon ($T_W$) test results applied to the 3 different settings in the pan and tilt dimensions. }
  \label{tab:err-results}
  \begin{tabular}{ccccc}
    \toprule
    & & & $\alpha$ & $p$ \\\midrule
    \multirow{5}{*}{G1} & Pan & $T_F$ & 0.05 & 0.3 \\\cmidrule{3-5}
	 & \multirow{4}{*}{Tilt} & $T_F$ & 0.05 & 0.002 \\ 
	 & & $T_{W, lo - med}$ & 0.016 & $<0.001$ \\ 
	 & & $T_{W, lo - hi}$  & 0.016 & $<0.001$ \\ 
	 & & $T_{W, med - hi}$ & 0.016 & 0.42 \\\midrule 
    \multirow{2}{*}{G2} & Pan & $T_F$ & 0.05 & 0.5 \\\cmidrule{3-5}
	 & Tilt & $T_F$ & 0.05 & 0.3 \\ 
    \bottomrule
  \end{tabular}
\end{table}

%The data collected from the participants with partial eyesight follow a similar trend to that of the blindfolded participants: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all three settings. These results are summarised in Table~\ref{tab:vi-results}. Unfortunately, not enough samples could be collected to draw any final conclusions. However, these results are in line with results from previous work~\cite{zwiers2001spatial}, indicating that the groups with partial and normal eyesight respond with similar levels of accuracy to spatialised sound when presented with simple tasks.

%\begin{table}
  %\centering
  %\caption{A table summarising the target search results of the participants with partial eyesight (P1 - P3). The results include the average error ($\mu$) and standard deviation ($\sigma$), given in radians in the pan and tilt dimensions.}
  %\label{tab:vi-results}
  %\begin{tabular}{cccccccc}
    %\toprule
    %\multicolumn{2}{c}{} & \multicolumn{2}{c}{\emph{lo}} & \multicolumn{2}{c}{\emph{med}} & \multicolumn{2}{c}{\emph{hi}} \\
    %\multicolumn{2}{c}{} & $\mu_l$ & $\sigma_l$ & $\mu_m$ & $\sigma_m$ & $\mu_h$ & $\sigma_h$ \\\midrule
    %& P1 & 0.25 & 0.44 & 0.21 & 0.45 & 0.29 & 0.40 \\ 
    %Pan [rad] & P2 & 0.18 & 0.85 & 0.05 & 0.49 & -0.08 & 0.32 \\ 
    %& P3 & -0.10 & 0.67 & -0.08 & 0.61 & -0.08 & 0.50 \\ \midrule
    %& P1 & -0.17 & 0.21 & -0.10 & 0.2 & -0.25 & 0.21 \\ 
    %Tilt [rad] & P2 & -0.87 & 0.26 & -0.05 & 0.21 & -0.15 & 0.18 \\ 
    %& P3 & -0.57 & 0.31 & -0.57 & 0.45 & -0.38 & 0.39 \\ 
    %\bottomrule
  %\end{tabular}
%\end{table}

%Based on previous research~\cite{zwiers2001spatial}, these results were somewhat expected. In addition, they also confirm that a participant's target search capability in the pan dimension is robust to the changing pitch for the target's tilt angle which is a useful result in support of the effectiveness of our audio interface.

\subsubsection{Tilt Results}
\label{sec:tilt-results}

The ordinates in Figs.~\ref{fig:err-results-lo} to~\ref{fig:err-results-hi} also show the results for the target search experiment in the tilt direction.
The box-plots in in Fig.~\ref{fig:err-boxplots-median} and~\ref{fig:err-boxplots-std} also show the median difference between the participants' guesses and the targets' true tilt positions. 
All of the results are summarised in Table~\ref{tab:err-results}. 
The data here were found to be non-normally normally distributed following inspections of the Q-Q plots and $p$-scores from the Shapiro-Wilkes test and are analysed accordingly.

The results for the participants in G1 show that there is a reasonably significant correlation between the participants' guesses and the actual tilt angle locations of the targets, shown by moderate Spearman correlation scores of approximately 0.38 for \emph{lo}, 0.48 for \emph{med} and the \emph{hi} gradient giving the strongest R-score of the three with a score of 0.55 ($p < 0.001$ for all 3 settings). 
This indicates that the varying pitch is working as expected and the participants are generally interpreting the cues correctly.

MEME UPDATE RESULTS FOR G2

The average errors of the datasets are relatively close to one another, with the \emph{lo} gradient giving the largest absolute error and standard deviation at \SI{0.40}{\radian} and \SI{0.46}{\radian}. The \emph{med} and \emph{hi} have similar absolute errors of \SI{0.32}{\radian} and \SI{0.34}{\radian} respectively. This is in line with the correlation scores, with the \emph{lo} gradient giving a worse result than the \emph{med} and \emph{hi} gradients and the \emph{hi} gradient giving the best results overall, with its high correlation score and relatively low absolute angular errors and standard deviation. This translates to an average position error of around \SI{25}{\centi\meter} at the \SI{2}{\meter} distance the targets were presented during the experiment.

We use the Friedman test on the medians of the data to find the statistical significance of the differences between the datasets. We use the median values here since the data are not normally distributed and there is significant noise within the data which may contaminate the mean values. Setting the critical threshold to $\alpha=0.05$, we find that there is indeed a significant difference between the three settings with $p=0.002$. Applying a Bonferroni correction to $\alpha$ for the 3 conditions ($\alpha_c=\frac{\alpha}{3}=0.016$) and running a Wilcoxon signed rank test shows that both the \emph{med} and \emph{hi} settings are significantly different than the \emph{lo} setting ($p=0.001<\alpha_c$ for both settings), but that the \emph{med} and \emph{hi} settings do not produce significantly different results from one another ($p=0.42>\alpha_c$). This is supported by the earlier observations made on the average and standard deviations of the error data which indicate that the \emph{lo} setting gives the highest average errors, while the \emph{med} and \emph{hi} settings produce similar error levels.

From Fig.~\ref{fig:err-boxplots} it can be seen that the data show a significant skewing to the negative side, indicating a potential bias amongst the experiment's participant-base that must be taken into account. From the results, it is not completely clear what causes this negative bias in the pitch dimension. However, a possible explanation is that the floor introduces a position constraint within the participants' minds, since the target cannot appear below the ground. It can potentially appear above the participants' head though, giving variable upper an lower limits that depend on the participants' height and individual perception. Future improvements to our audio interface should consider a non-linear increase in pitch as a function of tilt angle instead of the linear one we used in this work to remedy this bias. Fig.~\ref{fig:tone-threshold} shows the distribution of the cut-off frequency thresholds that were found in Section~\ref{sec:character}, as well as a plot of the median values of the errors in the tilt dimension, transformed to a frequency using each dataset's respective pitch-gain gradient.

In particular, Fig.~\ref{fig:tone-medians} indicates that the participants, on average, searched for the target until they could no longer detect a difference between the tone they were played and the \SI{512}{\hertz} on-target tone they were searching for. This is shown by the vast majority of the error data being located below the 75\% cut-off threshold frequency of \SI{12.9}{\hertz} (0.43 semitones around \SI{512}{\hertz}). Furthermore, it can be seen that the \emph{hi} dataset comes the closest to the cut-off frequency. This could explain why it produces the strongest correlation between the targets' true perceived position, since the \emph{hi} pitch gradient is the most sensitive to changes in the tilt angle, it allowed the participants to get closer to the true tilt by playing a more easily distinguishable tone.

Given the small sample size, there is limited meaningful statistical analysis we can do on the data collected from the participants with visual impairments. However, it could be seen from the results in Table~\ref{tab:vi-results} that these participants displayed the same behaviour in our experiments, with a clear bias toward the lower angles (i.e.\ the floor) and not-insignificant variability between the three settings in the tilt dimension. Similarly, the pan dimension remains more stable throughout the three settings. The participants also confirmed that they preferred the \emph{hi} setting, since it was more responsive and gave them a clearer idea of the direction they needed to point to.

These results show that a varying pitch tone can convey the tilt angle of a target to a human using bone-conducting headphones with accuracy levels similar to that in the literature~\cite{bujacz2011sonification, katz2011spatial, zotkin2004rendering}. They also highlight a clear and significant performance advantage between the \emph{med}\textbackslash\emph{hi} and \emph{lo} settings, but there is not enough evidence to suggest a significant difference in error performance between the \emph{med} and \emph{hi} settings. However, the \emph{hi} setting produce results closest to the target tilt.

\subsection{Time to Target}

Fig.~\ref{fig:fitts} shows the box-plots of the target search time as a function of the targets' \emph{IDs}. Here, the bin interval is the smallest effective width, calculated from Equation~\ref{eq:fitts-performance}, between the three gradient settings. We used the relation from Equation~\ref{eq:fitts-base} and fitted a logarithmic regression line for each participant. The medians of the $a$ and $b$ parameters, from Equation~\ref{eq:fitts-base}, for all the subjects' regressions were used to plot the resulting lines of best fit shown in Figs.~\ref{fig:fitts-lo} - \ref{fig:fitts-hi}.

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=120 20 120 20, width=0.95\textwidth]{figures/fitts_lo_sighted.png}
    \caption{\emph{Lo} setting. }
    \label{fig:fitts-lo}
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=120 20 120 20, width=0.95\textwidth]{figures/fitts_med_sighted.png}
    \caption{\emph{Med} setting. }
    \label{fig:fitts-med}
  \end{subfigure}

  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=120 20 120 20, width=0.95\textwidth]{figures/fitts_hi_sighted.png}
    \caption{\emph{Hi} setting. }
    \label{fig:fitts-hi}
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[clip, trim=90 20 130 20, width=0.95\textwidth]{figures/fitts_performance_sighted.png}
    \caption{Boxplots of the indices of performance.}
    \label{fig:fitts-performance}
  \end{subfigure}
  \caption{The plots showing Fitts's Law relation between the targets' index of difficulty and the time it took the participants to find the target. The results are summarised in a set of boxplots.}
  \label{fig:fitts}
\end{figure}

From these figures we can see that the data are consistent with Fitts's Law where the logarithmic line of best fit closely approximates the median values of the binned data for all three pitch gradient settings, with each setting giving Pearson correlation scores of 0.9, 0.91 and 0.93 for the \emph{lo}, \emph{med} and \emph{hi} settings respectively ($p < 0.001$ for all 3 settings). This result enabled us to compute the indices of performance, \emph{IP}, given by Equation~\ref{eq:fitts-performance}, for all of the subjects and are shown in Fig.~\ref{fig:fitts-performance}.

A Friedman test on the distributions reveal that there is a significant difference between the 3 settings ($p=0.003<\alpha$) and a set of Wilcoxon tests, with a Bonferroni correction applied to $\alpha$ ($\alpha_c=0.016$) , shows that there is only a significant difference between the \emph{lo} and \emph{hi} settings ($p=0.002<\alpha_c$). There is insufficient evidence to suggest a difference between the other settings (\emph{lo} - \emph{med} $\mapsto p=0.16>\alpha_c$, \emph{med} - \emph{hi} $\mapsto p=0.13>\alpha_c$). Based on the distributions in Fig.~\ref{fig:fitts-performance} and the statistical analysis, we can conclude that the \emph{hi} setting produces better results with a higher \emph{IP}. However, it is not clear where the \emph{med} settings falls in terms of \emph{IP} in relation to the other 2 settings. The statistical results are summarised in Table~\ref{tab:fitts-results}.%One might reasonably expect that a time-accuracy trade-off would occur between the 3 settings, i.e.\

\begin{table}
  \centering
  \caption{A table summarising the statistical results for the Friedman and Wilcoxon tests.}
  \label{tab:fitts-results}
  \begin{tabular}{ccc}
    \toprule
    & $\alpha$ & $p$ \\\hline
    Friedman & 0.05 & 0.003 \\ 
    \emph{lo - med} & 0.016 & 0.16 \\ 
    \emph{lo - hi}  & 0.016 & 0.002 \\ 
    \emph{med - hi} & 0.016 & 0.13 \\
    \bottomrule
  \end{tabular}
\end{table}

%To compare the 3 settings, we apply a Bonferroni correction $\alpha$ ($\alpha_c=0.016$) and perform a set of Wilcoxon tests to compare \emph{lo} and \emph{hi} ($T_1$), \emph{lo} and \emph{med} ($T_2$) and \emph{med} and \emph{hi} ($T_3$). We found that $T_1$ achieved significance ($p=0.012<\alpha_c$), indicating that the time-to-target performances of the \emph{lo} and \emph{hi} settings are significantly different enough to conclude that the \emph{lo} setting produces the superior \emph{IP} of the two settings. However, $T_2$ and $T_3$ did not achieve significance ($p=0.8>\alpha_c$ and $p=0.05>\alpha_c$ respectively), indicating that there is not sufficient evidence to rank the 3 settings from best to worst \emph{IP}. These results are summarised in Table MEME.

%Applying a Bonferroni correction to $\alpha$ ($\alpha_c=0.016$) and performing post-hoc analyses on the 3 settings with the Wilcoxon test comparing the \emph{lo} and \emph{hi} settings achieves significance after applying a Bonferroni correction for 3 tests to $\alpha$ ($p=0.012$), but the other comparisons do not achieve significance ($p=0.8$ for the \emph{lo} - \emph{med} ($T_2$) comparison, and $p=0.05$ for the \emph{med} - \emph{hi} comparison ($T_3$)). These results are summarised in Table MEME.

%A possible explanation for the observed behaviour is that the more distinguishable changes in the audio pitch with the \emph{hi} configuration better informs the user when they are on target, leading to a more accurate estimate, but also increases the time it takes to point in the right direction. Conversely, the \emph{lo} and \emph{med} gradients make it more difficult for the user to know when they are on target, leading to a shorter search time, but at the cost of lower accuracy. This is confirmed by the results obtained in Section~\ref{sec:tilt-results} and the Wilcoxon test results.

The results collected from the participants with partial eyesight follow the same trends observed in the blindfolded participants, giving \emph{IP}s of 0.58, 1.3 and 0.35 for the \emph{lo}, \emph{med} and \emph{hi} gradient settings respectively.

\subsection{Participant with Visual Impairments' Feedback}

After and during the experiments involving the participants with visual impairments, we had the opportunity to collect their feedback on the current system implementation and suggestions for future improvements.

In general, they were satisfied with the current implementation and had little difficulty using it. Furthermore, the prohibitive cost, complexity and cumbersomeness of other existing systems discouraged our subjects from purchasing and using them, so they were quite enthusiastic about our goal of developing a mobile or tablet-based indoor navigation system.

One aspect of the audio interface that requires improvement is the tone used during the experiments was not very pleasant and led to auditory fatigue after a long period of use. We are aware of this issue and we are already investigating more natural, `pleasant' and rich sounds to replace the basic sinusoidal wave that was used in the experiments. One possibility is to use musical instruments (e.g.\ MIDI sound files) to play notes and scales~\cite{brewster1998using}.

Concerning the bone-conducting headsets, only one participant had reservations about this choice, citing cost concerns. None of the participants had any technical issues in using the headset or misunderstanding audio cues. They all agreed that this is a valid choice to avoid cutting a person with visual impairments off from environmental sounds. Furthermore, they suggested to add some voice component to the system to inform the user of important events (e.g. \emph{`Target has been found'}, \emph{`You are veering off course'}, etc.) or to simply confirm and reassure the user that they are still on course.

%The final major suggestion was to add some form of on-target confirmation, either voice, vibration or some other audio cue. For the purposes of this experiment, we purposefully opted to not inform the participant when they were on target, since we are interested in the target acquisition accuracy. However, going forward we intend on adding an on-target notification in the form of an additional tone overlaid over the main tone.

\section{Conclusion and Future Work}
\label{sec:conclusion}

In this paper, we presented a spatial audio interface to direct a user with visual impairments to point a camera toward a target. We also discussed a set of experiments to determine its effectiveness and performance, as well as some subjective feedback collected from participants with partial eyesight.

We found that a spatial audio tone with a varying pitch can be used to convey the pan and tilt angles of a target using a set of bone-conducting headphones. The angular errors made by the participants are in line with those found in previous studies using similar audio interfaces. We also found that varying the pitch-gain gradient of our interface influences the accuracy of the system in the tilt dimension, as well as the time to target, without affecting the performance in the pan dimension. The steeper, \emph{hi}, pitch-gain was found to produce the best results in this respect. Furthermore, we discovered a logarithmic relationship between the index of difficulty of a target and the time taken by a participant to find it, confirming that the results with our interface adhere to Fitts's Law. However, there is a compromise to be made between speed and accuracy, with the \emph{hi} pitch-gain gradient directing the user to the target in the longest time.

Feedback from the participants with visual impairments was mostly positive and they agreed with the choice of bone-conduction headphones that do not inhibit normal hearing. However, they noted that the sine wave audio signal induced some audio fatigue, something noted by the other participants as well, and suggested suggested that more full-bodied, natural sounds be used instead. Using vocal feedback in conjunction with the current audio signal was also suggested.

Future research will focus on integrating voice and vibration feedback cues into the system. We are also investigating solutions to automatically refine the parameters of the HMI and better match the individual user's navigation habits and capability, thereby increasing navigation performance and user satisfaction.

\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}

\end{document}

### 2019-05-13 article.tex
Fixed formatting for new template. Starting great purge

@@
 \usepackage{multirow}
+\usepackage{todonotes}
+\usepackage[capitalise]{cleveref}
 
@@
 % Metadata Information
-\acmJournal{TAP}
+%\acmConference{SAP}
 %\acmVolume{9}
@@
 
-To this end, we are developing a mobile device-based navigation system using a Google Project Tango device\footnote{https://developers.google.com/tango}, pictured in Fig.~\ref{fig:tango-headphone}, that caters to the perception limitations of people with limited vision by using a non-visual interface.
+To this end, we are developing a mobile device-based navigation system using a Google Project Tango device\footnote{https://developers.google.com/tango}, pictured in \cref{fig:tango-headphone}, that caters to the perception limitations of people with limited vision by using a non-visual interface.
 This system will ultimately allow users with visual impairments to reach a target location in the final leg of their journey, i.e.\ the so-called `last 10 yards' problem~\cite{google2016blind,bellotto2013}.
@@
 
+%\begin{figure}
+  %\centering
+  %\begin{subfigure}[t]{0.45\textwidth}
 \begin{figure}
   \centering
-  \begin{subfigure}[t]{0.45\textwidth}
-    \centering
-    \includegraphics[width=0.85\textwidth]{figures/tango_headphone.png}
+  \includegraphics[width=0.4\textwidth]{figures/tango_headphone.png}
   \caption{The Tango device and bone-conducting headset used by the participants. }
   \label{fig:tango-headphone}
-  \end{subfigure}\hfill
-  \begin{subfigure}[t]{0.45\textwidth}
+\end{figure}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}[t]{0.45\textwidth}
+\begin{figure}
   \centering
-    \includegraphics[width=0.7\textwidth]{figures/camera_coordinate.pdf}
+  \includegraphics[width=0.4\textwidth]{figures/camera_coordinate.pdf}
   \caption{A diagram showing the Tango's frame of reference and the target's pan ($\phi$) and tilt ($\theta$) angles.}
   \label{fig:cam-coords}
-  \end{subfigure}
-  \caption{The hardware used during the experiment, as well as a diagram showing the Tango device's coordinate system. }
 \end{figure}
+  %\end{subfigure}
+  %\caption{The hardware used during the experiment, as well as a diagram showing the Tango device's coordinate system. }
+%\end{figure}
 
@@
 For the pointing task, we presented blindfolded and partially sighted participants with a set of virtual targets, one after another, and asked them to simply point a camera to where they thought the targets were.
-The targets' pan and tilt angles w.r.t.\ the Tango's vertical plane, shown in Fig.~\ref{fig:cam-coords}, were given to the participants through a spatial tone with varying pitch played via a set of bone-conducting headphones.
+The targets' pan and tilt angles w.r.t.\ the Tango's vertical plane, shown in \cref{fig:cam-coords}, were given to the participants through a spatial tone with varying pitch played via a set of bone-conducting headphones.
 We use the latter to not interfere with the user's normal hearing function, which people with visual impairments typically rely on.
@@
 Attempting to deliver a system that allows people with visual impairments to independently navigate and accomplish everyday tasks is not new; in fact, there are multiple commercial systems and research prototypes already available on the market.
-One approach that has been investigated is to outfit the existing white walking cane with various sensors, such as sonar, radar, motor encoders, etc.~\cite{ulrich1997, marion2008batcane} to warn the user of upcoming obstacles, instead of relying on haptic feedback from the impact between the cane and the obstacle.
+One approach that has been investigated is to outfit the existing white walking cane with various sensors,
+such as sonar, radar, motor encoders, etc.~\cite{ulrich1997, marion2008batcane} to warn the user of upcoming obstacles, instead of relying on haptic feedback from the impact between the cane and the obstacle.
 Another approach is to outfit a walking cane to act as a radio-frequency identification (RFID) antenna that can read a set of RFID tags placed at strategic locations around the environment at key spots or along a path~\cite{faria2010electronic, willis2005}.
@@
 %####################################################
-REVIEW SECTION - MAKE SURE TO MENTION DIFFERENCE BETWEEN BLIND AND SIGHTED , sonification of 3d scenes in an electronic travel aid for the blind.
+%REVIEW SECTION - MAKE SURE TO MENTION DIFFERENCE BETWEEN BLIND AND SIGHTED , sonification of 3d scenes in an electronic travel aid for the blind.
 Spatial audio has also been considered to convey the direction of a target.
@@
 
-We use a set of bone-conducting headphones (see Fig.~\ref{fig:tango-headphone}) that are placed externally on the user's head so that the system does not occlude the perception of real-world sounds and does not interfere with a user's normal hearing function.
+We use a set of bone-conducting headphones (see \cref{fig:tango-headphone}) that are placed externally on the user's head so that the system does not occlude the perception of real-world sounds and does not interfere with a user's normal hearing function.
 In the future, our system will use multiple feedback modes to provide the user with navigation and obstacle avoidance instructions.
@@
 
-A diagram of the experimental system pipeline is shown in Fig.~\ref{fig:pipeline}.
+A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}.
 Here, the arrows indicate the direction of the flow of information.
@@
   \centering
-  \includegraphics[clip=true, trim=50 120 80 50, width=0.55\textwidth]{figures/pipeline.pdf}
+  \includegraphics[clip=true, trim=50 120 80 50, width=0.4\textwidth]{figures/pipeline.pdf}
   \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }
@@
 For the series of experiments performed in this work, only the audio feedback mode was used to interface with the user.
-The audio component is responsible for conveying the 2D position of a target on the vertical plane w.r.t.\ the Tango's coordinate system, showed in Fig.~\ref{fig:cam-coords}, in terms of pan and tilt angles.
+The audio component is responsible for conveying the 2D position of a target on the vertical plane w.r.t.\ the Tango's coordinate system, showed in \cref{fig:cam-coords}, in terms of pan and tilt angles.
 Distance to the target can be rendered by adjusting the audio signal's amplitude as a function of the distance.
@@
 
-The pan angle describes the angle which the user needs to rotate the camera vector around the vertical $z$-axis in Fig.~\ref{fig:cam-coords}, i.e.\ how far the target is to the left or right of the user.
+The pan angle describes the angle which the user needs to rotate the camera vector around the vertical $z$-axis in \cref{fig:cam-coords}, i.e.\ how far the target is to the left or right of the user.
 We use an HRTF to add a spatial element to the audio tone that the system plays to the user, making the tone sound like it is coming from the direction of the target.
@@
 
-The system adjusts the tone's pitch to convey the target's tilt angle w.r.t.\ the camera's current pointing vector, $C$, as shown in Fig.~\ref{fig:cam-coords}.
+The system adjusts the tone's pitch to convey the target's tilt angle w.r.t.\ the camera's current pointing vector, $C$, as shown in \cref{fig:cam-coords}. 
 Here, a high pitch means the target is above the camera vector (i.e.\ the user should look up) and a low pitch means the target is below the camera vector (the user should look down).
@@
 Here, $y_m$ is a cut-off frequency, $x_m$ its corresponding angle and $m$ the gradient for the setting, calculated as $m = \frac{\Delta y}{\Delta x}$.
-The pitch gain functions are shown in Fig.~\ref{fig:pitch-gain}.
+The pitch gain functions are shown in \cref{fig:pitch-gain}.
 
@@
   \centering
-  \includegraphics[width=0.55\textwidth]{figures/pitch_gain_functions.png}
+  \includegraphics[width=0.4\textwidth]{figures/pitch_gain_functions.png}
   \caption{The pitch gain functions for the 3 different gain settings. }
@@
 
-For the experiments we used two groups of participants, with one including 42 sighted and blindfolded participants and the other 11 legally blind volunteers with varying degrees of vision impairment.
-We refer to these 2 groups as G1 and G2.
-%(see Fig.~\ref{fig:participants} for pictures of two participants during the experiments)
-The participants of each group performed a series of experiments using our system with a pair of bone-conducting headphones.
-The participants were recruited on a volunteer-basis and consisted of a diverse group of undergraduate students, professionals and retirees with ages ranging between 17 and 95 years (18 male, 35 female).
-Some of the participants were using hearing aids.
-However, this was not an issue, since we used bone-conducting headsets which bypass the outer ear structure and the hearing aids.
-
-The participants took part in three experiments.
-The first two were performed to determine each participant's hearing characteristics and provide some context to the results generated during the target-search experiment.
-These characterisation experiments also indicate any pre-existing biases the participant-base might have in their hearing behaviour for our third, target search experiment.
+For the experiments we used two groups of participants, with one including 42 sighted and blindfolded participants and the other 3 legally blind volunteers with varying degrees of vision impairment. 
+They performed a series of experiments using our system with a pair of bone-conducting headphones.
+The participants were recruited on a volunteer-basis and consisted of a diverse group of undergraduate students and professionals with ages ranging between 17 and 40 years (13 male, 32 female).
+The participants also reported having no significant hearing issues or any other disability that could affect the experiment.
+The participants participated in three experiments.
+The first two experiments were performed to determine each participant's hearing characteristics and provide some context to the results generated during the target-search experiment.
+These characterisation experiments will also indicate pre-existing biases our participant-base might have in the modes or dimensions we performed our third experiment on: the target search.
 
@@
 
-The distance between a participant and the target is not considered here and the 3D targets are therefore generated at a constant distance of \SI{2}{\metre} from the participant.
+The distance between the participant and the target is not considered here and the 3D targets are therefore generated at a constant distance of \SI{2}{\metre} from the participant.
 Throughout the experiments, various parameters of the target and the participant are recorded and streamed in real-time to a laptop computer via a WiFi connection.
-Prior to the target search experiment, participants from G1 were given a few minutes without a blindfold to familiarise themselves with the system and the audio tone's behaviour as the target's position changes.
-This was done verbally with the participants from G2 to inform them of the pitch they were aiming for that indicated that they were on-target.
+Prior to the target search experiment, the blindfolded participant group was given a few minutes without a blindfold to familiarise themselves with the system and confirm the target's location with their own eyes.
+This was done verbally with the participants with limited vision.
 
@@
 The participant then had to select the direction the sound came from.
-The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly difficult to distinguish between the left and right direction of the sound.
+The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly difficult to localise.
 
-For this progressive increase in difficulty, a 2-up, 1-down step procedure is used~\cite{wetherill1965sequential,levitt1971transformed}, meaning that for every 2 correct answers, the distance to the centre-front halves, making the lateral direction harder to determine.
-Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre-front.
-We also set  different step sequences: one starting at a large angular distance (\SI{45}{\degree}) from the participant's centre-front and the other at the minimum angular distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' step respectively.
-The terminating condition for the experiment is when the hard and easy step sequences converge to within 2 steps of one another (i.e.\ the difference between the hard and easy sequences are 4 times larger or smaller than one another) for 3 consecutive guesses.
-This gives an angular distance band which indicates each participant's ability to localise the sound source's lateral position.
-Each participant performed this experiment three times.
+For this progressive increase in difficulty, a 2-up, 1-down step process is used~\cite{wetherill1965sequential,levitt1971transformed}, meaning that for every 2 correct answers, the distance to the centre halves, making the lateral direction harder to determine.
+Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre.
+We also use 2 different step sequences, one starting at a large distance (\SI{45}{\degree}) from the user and the other at the minimum distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' step respectively.
+The terminating condition for the experiment is when the 2 step sequences converge to within 2 step ranges of one another for 3 consecutive guesses.
+This gives a distance band within which the participant is capable of localising the sound source. Each participant performed this experiment three times.
 
@@
 
-Next we determined each participant's ability to differentiate an audio tone's pitch, i.e.\ how well they can tell if a tone is high or low pitched.
-We played 2 tones after another to each participant, with the second tone being higher or lower-pitched than the first tone.
-The participants then had to indicate whether they thought the second tone as higher or lower-pitched than the first.
+Here we determined a participant's ability to differentiate pitch, i.e.\ how well they can tell if a tone is high or low pitched.
+We played 2 tones to the participants in succession with the second tone being higher or lower-pitched than the first.
+The participants were then asked to select whether they interpreted the second tone as higher or lower-pitched than the first.
 
-The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first.
-This tone difference depends on how well the participant can tell the tones apart.
+The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first one.
+The tone difference depends on how well the participant can tell the tones apart.
 Like the spatial awareness experiment, a 2-up, 1-down step process is used: for every 2 consecutive correct answers, the pitch difference between the tones is halved, and the difference is doubled for every incorrect answer.
@@
 
-The final experiment is the main one and will answer the question we are most interested in: how well does a spatial tone with varying pitch direct a person to look in a specific direction, and how do the parameters of this tone affect a person's performance in this task?
+The final experiment is the main one and will answer the question we are most interested in: how well does a spatial tone with varying pitch direct a user to look in a specific direction and how do the parameters of this tone affect the user's performance in this task?
 
-For this experiment, the participants given a Tango device running an app purpose-written for this experiment.
-When started, a set of virtual targets were presented one at a time to each participant on the Tango device.
-Then, depending on the direction the participant was currently pointing the camera relative to the target's position, the Tango generated and played an audio tone via bone-conducting headphones to indicate the pan and tilt angle adjustment required to point the camera to the target.
+For this experiment, the participants were blindfolded where necessary and given a Tango device running an app purpose-written for this experiment.
+When started, a set of virtual targets were presented one at a time to the participant on the Tango device.
+Then, depending on the direction the participant was currently pointing the camera relative to the target's position, the Tango generated and played a tone via the bone-conducting headphones to indicate the pan and tilt angle adjustment required to point the camera to the target.
 %These instructions are spatialised tones with varying pitch: an HRTF indicates the pan direction (left or right) and the pitch indicates whether the participant should be looking up (high pitch) or down (low pitch) to find the target.
 
-Once a participant pointed the Tango's camera toward the target, the system generated a neutral tone with a pitch of \SI{512}{\hertz}, which we used as the `on-target' pitch for all of our experiments.
-A participant then had to manually confirm the direction they believed the target was after hearing the tone's pitch change to the \SI{512}{\hertz}, on-target tone, and tap the screen to confirm the location.
-At this point a new search target was presented and the process was repeated.
+Once the participant pointed the camera toward the target, the system generated a neutral tone with a pitch of \SI{512}{\hertz}, which we used as the `on-target' pitch for all of our experiments.
+The participants then had to manually confirm the direction they believe the target was after hearing the on-target tone and tap the screen.
+At this point a new search target was presented and the search-process was repeated.
 To minimise any speed/accuracy trade-off bias in the results, we asked the participants to search for the targets without placing particular emphasis on accuracy or time.
 
-A total of 28 targets were presented to each participant per experiment run.
+28 targets were presented to each participant per run.
 The positions of these targets were randomly generated and equally spread across the 4 quadrants on the vertical plane to prevent a clustering of targets at the same location.
-After every experiment run, the parameters controlling the tone's behaviour were adjusted.
+After every run of the experiment, the parameters controlling the tone's behaviour was adjusted.
 In this case, the rate of change of the tone's pitch was adjusted to make the pitch increase at a lower or higher rate as a function of the tilt angle between the target and the participant's current pointing direction.
-This was done to determine whether, for example, a more rapid increase in pitch would help the participant find the target faster or more accurately. 
-The order in which the settings were set for each participant was randomised in order to minimise any learning effect the participant population might display between experiments.
+This was done to see whether, for example, a more rapid increase in pitch would help the participant find the target faster or more accurately.
+The order in which the settings were set for each participant was randomised in order to minimise any learning effect the participant population might display between each experiment.
 
@@
 
-We use 2 different metrics to compare the 3 different pitch gradient settings, namely target acquisition accuracy and search time.
-The accuracy is given as the difference between the location the Tango's camera was pointing at the time a participant selected a target's location and the target's actual position.
+We use two different metrics to compare the three different pitch gradient settings: the acquisition accuracy and search time.
+The accuracy is given as the difference between the Tango's orientation at the time the participant confirmed they were on target, and the target's actual orientation.
 We separate the results of the tilt and pan dimensions in order to see how the different pitch gradients affect a participant's pointing accuracy.
 
-We also compare the performance of the 3 pitch gradient settings in terms of the time it took each participant to find a target.
+We also compare the performance of the three pitch gradient settings in terms of the time it takes each participant to find a target.
 However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
 Instead, we use Fitts's Law~\cite{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\cite{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty (the ratio between the distance to the target and its width).
-It also provides us with an additional metric called the `index of performance' that we can use to compare the results between the 3 configurations. 
-Here we briefly summarise the equations and quantities involved in this metric. 
+It also provides a so-called `index of performance' that we can use as a metric to compare the results between the three configurations.
+
+Here we briefly summarise the equations and quantities involved in our metric.
 Fitts's Law is given by
@@
 \noindent
-where $t$ is the time it takes to find a target, $a$ and $b$ are constants determined through regression and $ID$ is a target's index of difficulty, given as logarithmic function of the ratio between the distance to the target and the target's width.
-In this case, the targets have no width since they are points in space, and we use MacKenzie's modified form for $ID$, given by
+where $t$ is the time it takes to find a target, $a$ and $b$ are constants determined through regression and $ID$ is a description of the difficulty of the target, given as logarithmic function of the ratio between the distance to the target and the target's width.
+In our case, the targets have no width, since they are points in space, and we therefore use MacKenzie's modified form for $ID$, given by
 
@@
 \noindent
-where $\sigma$ is the standard deviation of the error data, taken as the angle between a participant's target selection and the target's actual position. 
-Fitts's index of performance, $IP$, can then be calculated with
+where $\sigma$ is the standard deviation of the error data, taken as the angle between the participant's target selection and target's actual angular position.
+Fitts's index of performance, $IP$, can then be calculated using
 
@@
 
-Fig.~\ref{fig:location-guesses} shows the results for the spatial awareness experiment in the pan direction where each participant determined the location of the sound they were played.
+\cref{fig:location-guesses} shows the results for the spatial awareness experiment in the pan direction where the participants had to determine the location of the sound they were played.
 
@@
   \centering
-  \includegraphics[clip, trim=100 20 150 100, width=0.5\textwidth]{figures/location_guesses_sighted.png}
+  \includegraphics[clip, trim=100 20 150 100, width=0.4\textwidth]{figures/location_guesses.png}
   \caption{Histograms of the spatial awareness experiment in the pan dimension showing the proportion of correct/incorrect guesses per bin interval. }
@@
 
-MEME INSERT BLIND FIGURE
-
-With a relatively low number of erroneous guesses, we see that the participants were accurate in guessing the location of the sound source.
+With the relatively low number of erroneous guesses, we see that the participants were accurate in guessing the location of the sound source.
 This is further supported by the large number of samples at the minimum difference of \textasciitilde\SI{3}{\cm}, indicating that the participants reached this level more frequently and consistently.
@@
 
-The results recorded during the pitch discrimination experiment are shown in Fig.~\ref{fig:tone-guesses}, where a bar plot is used to show the number of correct guesses for each tone difference level.
+The results recorded during the pitch discrimination experiment are shown in \cref{fig:tone-guesses}, where a bar plot is used to show the number of correct guesses for each tone difference level.
 The latter is given in terms of the relative semitone difference between the tones which are obtained using the following relation:
@@
 
-From Fig.~\ref{fig:tone-guesses-sighted}, we can see that the guesses are normally spread around a 0 semitone difference for the blindfolded participants in G1, with roughly an equal number of samples with positive and negative difference values.
+From \cref{fig:tone-guesses}, we can see that the guesses are normally spread around a 0 semitone difference.
 As expected, a larger proportion of incorrect guesses occur around the smaller differences with the majority of samples for correct and incorrect guesses being recorded in the $[-0.25, 0.25]$ semitone difference level.
-However, the results from the participants from G2 in Fig.~\ref{fig:tone-guesses-blind} are less evenly spread and more concentrated around the 0 semitone difference level, with a skewing of wrong guesses values towards the positive side, possibly indicating a perception bias amongst our pool of participants with vision impairments.
-However, one possible reason for this bias may simply be a lack of data, and we may see that more samples from larger group of participants with vision impairments in G2 would provide a more normal spread, similar to the plot in Fig.~\ref{fig:tone-guesses-sighted}.
+Assuming these differences are normally distributed, we fitted a cumulative distribution function (CDF) over each participant's set of results for their correct guesses and used the CDF's parameters to determine the semitone difference threshold, where the participant could no longer reliably tell two tones apart, for each participant.
+See \cref{fig:cdf-semitone} for an example showing the actual CDF of a participant and its approximated normal CDF\@.
+We set this threshold at 75\% of the correct guesses, since this represents a significant majority of samples.
+We found that the median threshold is approximately 0.43 semitones for the sighted participants in a range of [$9.2\times10^-4$, 3.12] semitones.
+We use the median given the skewness of the distribution.
+The plot showing the participants' threshold distribution can be seen in \cref{fig:tone-threshold}.
 
-Assuming these differences are normally distributed, we fitted a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
-We then used the CDF's parameters to determine the semitone difference where a participant could could no longer reliably tell tones apart.
-%See Fig.~\ref{fig:cdf-semitone} for an example showing the actual CDF of a participant and its approximated normal CDF\@. 
-We set this threshold to a difference level that includes 75\% of the correct guesses.
-We found that the median threshold is approximately 0.28 semitones for G1 and 0.22 semitones for G2.
-We used the absolute values of the difference data and therefore used the median values of the data an ANOVA of the 2 threshold sets show that there is no significant difference between the 2 groups ($p=0.99$).
-The plot showing the participants' threshold distribution can be seen in Fig.~\ref{fig:tone-threshold}.
-
+%\begin{figure}
+  %\centering
+  %\begin{subfigure}[t]{0.5\textwidth}
 \begin{figure}
   \centering
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[clip, trim=80 0 150 100, width=0.95\textwidth]{figures/tone_guesses_sighted.png}
-    \caption{Results for G1. }
-    \label{fig:tone-guesses-sighted}
-  \end{subfigure}%
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[clip, trim=120 0 120 70, width=0.95\textwidth]{figures/tone_guesses_blind.png}
-    \caption{Results for G2. }
-    \label{fig:cdf-semitone-blind}
-  \end{subfigure}
-  %\begin{subfigure}[t]{0.5\textwidth}
-    %\centering
-    %\includegraphics[clip, trim=120 0 120 70, width=0.95\textwidth]{figures/cdf_tone_guesses.png}
-    %\caption{Cumulative distribution of the number of correct guesses for one participant. }
-    %\label{fig:cdf-semitone}
-  %\end{subfigure}
-  \caption{Histograms of the tone limit experiment showing the proportion of correct/incorrect guesses per bin interval. }
+  \includegraphics[clip, trim=80 0 150 100, width=0.4\textwidth]{figures/tone_guesses.png}
+  \caption{Results of the tone limit experiment. }
   \label{fig:tone-guesses}
@@
 \begin{figure}
+  %\end{subfigure}%
+  %\begin{subfigure}[t]{0.5\textwidth}
   \centering
-  \begin{subfigure}[t]{0.5\textwidth}
+  \includegraphics[clip, trim=120 0 120 70, width=0.4\textwidth]{figures/cdf_tone_guesses.png}
+  \caption{Cumulative distribution of the number of correct guesses for one participant. }
+  \label{fig:cdf-semitone}
+\end{figure}
+  %\end{subfigure}
+  %\caption{Histograms of the tone limit experiment showing the proportion of correct/incorrect guesses per bin interval. }
+%\end{figure}
+
+%\begin{figure}
+  %\centering
+  %\begin{subfigure}[t]{0.5\textwidth}
+\begin{figure}
   \centering
-    \includegraphics[clip, trim=80 20 120 0, width=0.95\textwidth]{figures/tone_threshold_sighted.png}
-    \caption{Results for G2. }
+  \includegraphics[clip, trim=80 20 120 0, width=0.4\textwidth]{figures/tone_threshold.png}
+  \caption{A distribution of the 75\% cut-off frequencies. }
   \label{fig:tone-threshold}
-  \end{subfigure}\hfill
-  \begin{subfigure}[t]{0.5\textwidth}
+\end{figure}
+\begin{figure}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}[t]{0.5\textwidth}
   \centering
-    \includegraphics[clip, trim=80 20 120 0, width=0.95\textwidth]{figures/tone_threshold_blind.png}
-    \caption{Results for G2. }
-    \label{fig:tone-threshold}
-  \end{subfigure}\hfill
-  %\begin{subfigure}[t]{0.5\textwidth}
-    %\centering
-    %\includegraphics[clip, trim=80 20 120 0, width=0.95\textwidth]{figures/tone_medians_sighted.png}
-    %\caption{A distribution of the median cut-off frequency thresholds along with the median 75\% cut-off threshold. }
-    %\label{fig:tone-medians}
+  \includegraphics[clip, trim=80 20 120 0, width=0.4\textwidth]{figures/tone_medians.png}
+  \caption{A distribution of the median cut-off frequency thresholds along with the median 75\% cut-off threshold. }
+  \label{fig:tone-medians}
   %\end{subfigure}
+\end{figure}
   %\caption{Distribution plots showing the cut-off frequencies for the sample group. }
-  \caption{A distribution of the 75\% cut-off frequencies. }
-\end{figure}
+%\end{figure}
 
@@
 
-The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in Figs.~\ref{fig:err-results-lo} to~\ref{fig:err-results-hi}, where the angular errors in the pan and tilt directions are plotted against each other for both participant groups.
-A set of box-plots of the pan errors' medians and standard deviations for each setting are also given in Figs.~\ref{fig:err-boxplots-medians} and~\ref{fig:err-boxplots-stds} and the results for both groups are summarised in Table~\ref{tab:results}.
+The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \crefrange{fig:err-results-lo}{fig:err-results-hi}, where the angular errors in the pan and tilt directions are plotted against each other.
+A set of box-plots of the pan errors' median and standard deviations are also given in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} for each of the \emph{lo}, \emph{med} and \emph{hi} configurations.
+The results are summarised in Table~\ref{tab:results}.
 
+%\begin{figure}
+  %\centering
+  %\begin{subfigure}[t]{0.5\textwidth}
 \begin{figure}
   \centering
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_lo_sighted.png}
-    \caption{Results for G1. }
-  \end{subfigure}%
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_lo_blind.png}
-    \caption{Results for G2. }
-  \end{subfigure}
+  \includegraphics[clip, trim=450 0 450 110, width=0.4\textwidth]{figures/err_lo.png}
   \caption{\emph{Lo} setting. }
@@
 \begin{figure}
+  %\end{subfigure}%
+  %\begin{subfigure}[t]{0.5\textwidth}
   \centering
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_med_sighted.png}
-    \caption{Results for G1. }
-  \end{subfigure}%
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_med_blind.png}
-    \caption{Results for G2. }
-  \end{subfigure}
+  \includegraphics[clip, trim=450 0 450 110, width=0.4\textwidth]{figures/err_med.png}
   \caption{\emph{Med} setting. }
@@
 \end{figure}
+  %\end{subfigure}%
+
 \begin{figure}
+  %\begin{subfigure}[t]{0.45\textwidth}
   \centering
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_hi_sighted.png}
-    \caption{Results for G1. }
-  \end{subfigure}%
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[clip, trim=450 0 450 110, width=0.95\textwidth]{figures/err_hi_blind.png}
-    \caption{Results for G2. }
-  \end{subfigure}
+  \includegraphics[clip, trim=450 0 450 60, width=0.4\textwidth]{figures/err_hi.png}
   \caption{\emph{Hi} setting. }
@@
 \end{figure}
+  %\end{subfigure}%
+  %\caption{Plots showing the distribution of angular errors in the pan and tilt dimensions for the 3 different pitch gradient settings and summarised in a set of boxplots. }
+%\label{fig:err}
+%\end{figure}
 
+%\begin{figure}
+  %\centering
+  %\begin{subfigure}[t]{0.5\textwidth}
 \begin{figure}
   \centering
-  \begin{subfigure}[t]{0.45\textwidth}
-    \centering
-    \includegraphics[clip, trim=30 -70 100 0, width=0.95\textwidth]{figures/err_boxplot_medians_sighted.png}
-    \caption{Results for G1.}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.45\textwidth}
-    \centering
-    \includegraphics[clip, trim=30 -70 100 0, width=0.95\textwidth]{figures/err_boxplot_medians_blind.png}
-    \caption{Results for G2. }
-  \end{subfigure}
-  \caption{Boxplots of the medians for the pan and tilt error results from the target search experiment.}
-  \label{fig:err-boxplots-medians}
+  \includegraphics[clip, trim=20 -70 100 100, width=0.4\textwidth]{figures/err_boxplot_medians.png}
+  \caption{Error median.}
+  \label{fig:err-boxplot-median}
 \end{figure}
-
+  %\end{subfigure}%
+  %\begin{subfigure}[t]{0.5\textwidth}
 \begin{figure}
   \centering
-  \begin{subfigure}[t]{0.45\textwidth}
-    \centering
-    \includegraphics[clip, trim=80 -70 100 0, width=0.95\textwidth]{figures/err_boxplot_std_sighted.png}
-    \caption{Results for G1.}%
-  \end{subfigure}
-  \begin{subfigure}[t]{0.45\textwidth}
-    \centering
-    \includegraphics[clip, trim=80 -70 100 0, width=0.95\textwidth]{figures/err_boxplot_std_blind.png}
-    \caption{Results for G2.}
-  \end{subfigure}
-  \caption{Boxplots of the standard deviations for the pan and tilt error results from the target search experiment.}
-  \label{fig:err-boxplots-stds}
+  \includegraphics[clip, trim=80 -70 100 0, width=0.4\textwidth]{figures/err_boxplot_std.png}
+  \caption{Error standard deviations.}
+  \label{fig:err-boxplot-std}
 \end{figure}
+  %\end{subfigure}
+  %\caption{Boxplots of pan and tilt error results from the target search experiment.}
+  %\label{fig:err-boxplots}
+%\end{figure}
 
@@
   \label{tab:results}
-  \begin{tabular}{cclcccc}
-    \toprule
-    \multicolumn{3}{c}{} & $\mu_{abs}$ & $\mu$ & $\sigma$ & $R$ \\\midrule
-    \multirow{6}{*}{G1}  & & \emph{lo}  & 0.23 & -0.02 & 0.32 & 0.75 \\
-	 & Pan [rad] & \emph{med} & 0.21 & -0.01 & 0.28 & 0.77 \\
-	 & & \emph{hi}  & 0.22 & -0.05 & 0.31 & 0.75 \\\cmidrule{3-7}
-	 & & \emph{lo}  & 0.40 & -0.14 & 0.46 & 0.38 \\
-	 & Tilt [rad] & \emph{med} & 0.32 & -0.12 & 0.36 & 0.48 \\
-	 & & \emph{hi}  & 0.34 & -0.16 & 0.39 & 0.55 \\\midrule
-    \multirow{6}{*}{G2} & & \emph{lo}  & 0.42 & -0.01 & 0.48 & N/A \\
-	 & Pan [rad] & \emph{med} & 0.42 & 0.07 & 0.49 & 0.14 \\
-	 & & \emph{hi}  & 0.40 & 0.05 & 0.48 & 0.13 \\\cmidrule{3-7}
-	 & & \emph{lo}  & 0.52 & -0.50 & 0.38 & 0.14 \\
-	 & Tilt [rad] & \emph{med} & 0.44 & -0.41 & 0.34 & 0.32 \\
-	 & & \emph{hi}  & 0.41 & -0.38 & 0.33 & 0.36 \\
-    \bottomrule
+  \begin{tabular}{|c|l|c|c|c|c|}
+    \hline
+    \multicolumn{2}{|c|}{} & $\mu_{abs}$ & $\mu$ & $\sigma$ & $R$ \\\hline\hline
+    & \emph{lo}  & 0.23 & -0.02 & 0.32 & 0.75 \\\cline{2-6}
+    Pan & \emph{med} & 0.21 & -0.01 & 0.28 & 0.77 \\\cline{2-6}
+    & \emph{hi}  & 0.22 & -0.05 & 0.31 & 0.75 \\\hline\hline
+    & \emph{lo}  & 0.40 & -0.14 & 0.46 & 0.38 \\\cline{2-6}
+    Tilt & \emph{med} & 0.32 & -0.12 & 0.36 & 0.48 \\\cline{2-6}
+    & \emph{hi}  & 0.34 & -0.16 & 0.39 & 0.55 \\\hline
   \end{tabular}
@@
 
-The results in Figs.~\ref{fig:err-results-lo} to~\ref{fig:err-results-hi} for both groups suggest that the data in the pan dimension are approximately normally distributed around \SI{0}{\degree}, at least visually.
-However, results from the Shapiro-Wilkes test that fall below the critical threshold, $\alpha=0.05$, and inspection of the quantile-quantile (Q-Q) plots do not give enough confidence to consider the data as normally distributed and we therefore analyse the data using non-parametric techniques.
+\crefrange{fig:err-results-lo}{fig:err-results-hi} and the median and mean points from the box-plots in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} show that the data in the pan dimension is approximately normally distributed around zero.
+However, $p$-scores below the critical 0.05 level from the Shapiro-Wilkes test and inspection of the quantile-quantile (Q-Q) plots do not give enough confidence to consider the data as normally distributed and we therefore analyse the data through non-parametric techniques.
 
-%####################################################################################################################
-%####################################################################################################################
-%####################################################################################################################
-%####################################################################################################################
-%####################################################################################################################
+There is a strong linear correlation between the participants' guesses and the targets' true pan angles, shown by the high Spearman correlation scores of approximately 0.75 ($p \ll 0.05$) for all of the datasets, with the \emph{med} configuration displaying the marginally best result of 0.77.
+The three settings have similar average errors and standard deviations, with the \emph{med} configuration again producing the marginally best results with the smallest average error and standard deviation.
+However, the differences are small (approximately 6\%) and are not significant enough (Friedman test $p \gg 0.05$) to conclude that the pitch gradient has an effect on the performance in the pan dimension.
 
-For the participants in G1, there is a strong linear correlation between the participants' guesses and the targets' true pan angles, shown by the high Spearman correlation scores of approximately 0.75 ($p < 0.001$) for all of the datasets, with the \emph{med} configuration displaying the marginally best result of 0.77.
-The three settings have similar average errors and standard deviations around \SI{0}{\radian}, with the \emph{med} setting again producing the marginally best results with the smallest average error and standard deviation.
-However, the differences are small (approximately 6\%) and are not significant enough (Friedman test $p=0.3>\alpha$) to conclude that the pitch gradient has an effect on the performance in the pan dimension.
-With very low Spearman, or statistically insignificant, scores, the data for G2 show that there is a very weak positive relationship between the targets' pan positions and the participants' guesses. 
-The pan angle error is still centred around \SI{0}{\radian}, but displays a wider spread with a larger standard deviation and absolute mean than the errors in G1. 
-These statistical results are listed in Table~\ref{tab:err-results}.
-
-\begin{table}
-  \centering
-  \caption{A table summarising Friedman ($T_F$) and Wilcoxon ($T_W$) test results applied to the 3 different settings in the pan and tilt dimensions. }
-  \label{tab:err-results}
-  \begin{tabular}{ccccc}
-    \toprule
-    & & & $\alpha$ & $p$ \\\midrule
-    \multirow{5}{*}{G1} & Pan & $T_F$ & 0.05 & 0.3 \\\cmidrule{3-5}
-	 & \multirow{4}{*}{Tilt} & $T_F$ & 0.05 & 0.002 \\ 
-	 & & $T_{W, lo - med}$ & 0.016 & $<0.001$ \\ 
-	 & & $T_{W, lo - hi}$  & 0.016 & $<0.001$ \\ 
-	 & & $T_{W, med - hi}$ & 0.016 & 0.42 \\\midrule 
-    \multirow{2}{*}{G2} & Pan & $T_F$ & 0.05 & 0.5 \\\cmidrule{3-5}
-	 & Tilt & $T_F$ & 0.05 & 0.3 \\ 
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-%The data collected from the participants with partial eyesight follow a similar trend to that of the blindfolded participants: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all three settings.
+The data collected from the participants with partial eyesight follow a similar trend to that of the blindfolded participants: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all three settings.
 These results are summarised in Table~\ref{tab:vi-results}.
@@
 
-%\begin{table}
-  %\centering
-  %\caption{A table summarising the target search results of the participants with partial eyesight (P1 - P3).
+\begin{table}
+  \centering
+  \caption{A table summarising the target search results of the participants with partial eyesight (P1 - P3).
 The results include the average error ($\mu$) and standard deviation ($\sigma$), given in radians in the pan and tilt dimensions.}
-  %\label{tab:vi-results}
-  %\begin{tabular}{cccccccc}
-    %\toprule
-    %\multicolumn{2}{c}{} & \multicolumn{2}{c}{\emph{lo}} & \multicolumn{2}{c}{\emph{med}} & \multicolumn{2}{c}{\emph{hi}} \\
-    %\multicolumn{2}{c}{} & $\mu_l$ & $\sigma_l$ & $\mu_m$ & $\sigma_m$ & $\mu_h$ & $\sigma_h$ \\\midrule
-    %& P1 & 0.25 & 0.44 & 0.21 & 0.45 & 0.29 & 0.40 \\ 
-    %Pan [rad] & P2 & 0.18 & 0.85 & 0.05 & 0.49 & -0.08 & 0.32 \\ 
-    %& P3 & -0.10 & 0.67 & -0.08 & 0.61 & -0.08 & 0.50 \\ \midrule
-    %& P1 & -0.17 & 0.21 & -0.10 & 0.2 & -0.25 & 0.21 \\ 
-    %Tilt [rad] & P2 & -0.87 & 0.26 & -0.05 & 0.21 & -0.15 & 0.18 \\ 
-    %& P3 & -0.57 & 0.31 & -0.57 & 0.45 & -0.38 & 0.39 \\ 
-    %\bottomrule
-  %\end{tabular}
-%\end{table}
+  \label{tab:vi-results}
+  \begin{tabular}{|c|c|cc|cc|cc|}
+    \hline
+    \multicolumn{2}{|c|}{} & \multicolumn{2}{c|}{\emph{lo}} & \multicolumn{2}{c|}{\emph{med}} & \multicolumn{2}{c|}{\emph{hi}} \\
+    \multicolumn{2}{|c|}{} & $\mu_l$ & $\sigma_l$ & $\mu_m$ & $\sigma_m$ & $\mu_h$ & $\sigma_h$ \\\hline\hline
+    & P1 & 0.25 & 0.44 & 0.21 & 0.45 & 0.29 & 0.40 \\ \cline{2-8}
+    Pan & P2 & 0.18 & 0.85 & 0.05 & 0.49 & -0.08 & 0.32 \\ \cline{2-8}
+    & P3 & -0.10 & 0.67 & -0.08 & 0.61 & -0.08 & 0.50 \\ \hline\hline
+    & P1 & -0.17 & 0.21 & -0.10 & 0.2 & -0.25 & 0.21 \\ \cline{2-8}
+    Tilt & P2 & -0.87 & 0.26 & -0.05 & 0.21 & -0.15 & 0.18 \\ \cline{2-8}
+    & P3 & -0.57 & 0.31 & -0.57 & 0.45 & -0.38 & 0.39 \\ \hline
+  \end{tabular}
+\end{table}
 
-%Based on previous research~\cite{zwiers2001spatial}, these results were somewhat expected.
+Based on previous research~\cite{zwiers2001spatial}, these results were somewhat expected.
 In addition, they also confirm that a participant's target search capability in the pan dimension is robust to the changing pitch for the target's tilt angle which is a useful result in support of the effectiveness of our audio interface.
@@
 
-The ordinates in Figs.~\ref{fig:err-results-lo} to~\ref{fig:err-results-hi} also show the results for the target search experiment in the tilt direction.
-The box-plots in in Fig.~\ref{fig:err-boxplots-median} and~\ref{fig:err-boxplots-std} also show the median difference between the participants' guesses and the targets' true tilt positions. 
-All of the results are summarised in Table~\ref{tab:err-results}. 
-The data here were found to be non-normally normally distributed following inspections of the Q-Q plots and $p$-scores from the Shapiro-Wilkes test and are analysed accordingly.
+Besides the pan, the ordinates in \crefrange{fig:err-results-lo}{fig:err-results-hi} also show the results recorded during the target search experiment for the tilt direction.
+A set of box-plots are given in \cref{fig:err-boxplot-median} to show the average tilt error between the participants' guesses and the targets' true positions.
+All of the results are summarised in Table~\ref{tab:results}. 
+The data here are also considered not normally distributed following inspections of the Q-Q plots and Shapiro-Wilkes test results and are analysed accordingly.
 
-The results for the participants in G1 show that there is a reasonably significant correlation between the participants' guesses and the actual tilt angle locations of the targets, shown by moderate Spearman correlation scores of approximately 0.38 for \emph{lo}, 0.48 for \emph{med} and the \emph{hi} gradient giving the strongest R-score of the three with a score of 0.55 ($p < 0.001$ for all 3 settings).
+We found that there is reasonably significant correlation between the participants' guesses and the actual locations of the targets, shown by moderate Spearman correlation scores of approximately 0.38 for \emph{lo}, 0.48 for \emph{med} and the \emph{hi} gradient giving the strongest R-scores of the three with a score of 0.55 ($p \ll 0.05$ for all 3 settings).
 This indicates that the varying pitch is working as expected and the participants are generally interpreting the cues correctly.
-
-MEME UPDATE RESULTS FOR G2
 
@@
 This is in line with the correlation scores, with the \emph{lo} gradient giving a worse result than the \emph{med} and \emph{hi} gradients and the \emph{hi} gradient giving the best results overall, with its high correlation score and relatively low absolute angular errors and standard deviation.
-This translates to an average position error of around \SI{25}{\centi\meter} at the \SI{2}{\meter} distance the targets were presented during the experiment.
 
-We use the Friedman test on the medians of the data to find the statistical significance of the differences between the datasets.
-We use the median values here since the data are not normally distributed and there is significant noise within the data which may contaminate the mean values.
-Setting the critical threshold to $\alpha=0.05$, we find that there is indeed a significant difference between the three settings with $p=0.002$.
-Applying a Bonferroni correction to $\alpha$ for the 3 conditions ($\alpha_c=\frac{\alpha}{3}=0.016$) and running a Wilcoxon signed rank test shows that both the \emph{med} and \emph{hi} settings are significantly different than the \emph{lo} setting ($p=0.001<\alpha_c$ for both settings), but that the \emph{med} and \emph{hi} settings do not produce significantly different results from one another ($p=0.42>\alpha_c$).
+We use the Friedman test~\cite{friedman1937use} on the medians of the data to find the statistical significance of the differences between the datasets.
+We use the median values here since the data are not normally spread and there is significant noise within the data which may contaminate the mean values.
+This results in a $p$-value of 0.002, which falls below the commonly-used critical threshold of 0.05, implying that there is a statistically significant difference between the three settings.
+A post-hoc analysis with a Wilcoxon signed rank test and a critical threshold with a Bonferroni correction applied for the 3 settings ($\alpha=0.016$) shows that both the \emph{med} and \emph{hi} settings are significantly different than the \emph{lo} setting ($p=0.0014$ for both settings), but that the \emph{med} and \emph{hi} settings do not produce significantly different results from one another ($p=0.42$).
 This is supported by the earlier observations made on the average and standard deviations of the error data which indicate that the \emph{lo} setting gives the highest average errors, while the \emph{med} and \emph{hi} settings produce similar error levels.
 
-From Fig.~\ref{fig:err-boxplots} it can be seen that the data show a significant skewing to the negative side, indicating a potential bias amongst the experiment's participant-base that must be taken into account.
+From \cref{fig:err-boxplot-median} it can also be seen that the data show a significant skewing to the negative side, indicating a potential bias amongst the experiment's participant-base that must be taken into account.
 From the results, it is not completely clear what causes this negative bias in the pitch dimension.
@@
 Future improvements to our audio interface should consider a non-linear increase in pitch as a function of tilt angle instead of the linear one we used in this work to remedy this bias.
-Fig.~\ref{fig:tone-threshold} shows the distribution of the cut-off frequency thresholds that were found in Section~\ref{sec:character}, as well as a plot of the median values of the errors in the tilt dimension, transformed to a frequency using each dataset's respective pitch-gain gradient.
+\cref{fig:tone-threshold} shows the distribution of the cut-off frequency thresholds that were found in Section~\ref{sec:character}, as well as a plot of the median values of the errors in the tilt dimension, transformed to a frequency using each dataset's respective pitch-gain gradient.
 
-In particular, Fig.~\ref{fig:tone-medians} indicates that the participants, on average, searched for the target until they could no longer detect a difference between the tone they were played and the \SI{512}{\hertz} on-target tone they were searching for.
+In particular, \cref{fig:tone-medians} indicates that the participants, on average, searched for the target until they could no longer detect a difference between the tone they were played and the \SI{512}{\hertz} on-target tone they were searching for.
 This is shown by the vast majority of the error data being located below the 75\% cut-off threshold frequency of \SI{12.9}{\hertz} (0.43 semitones around \SI{512}{\hertz}).
@@
 These results show that a varying pitch tone can convey the tilt angle of a target to a human using bone-conducting headphones with accuracy levels similar to that in the literature~\cite{bujacz2011sonification, katz2011spatial, zotkin2004rendering}.
-They also highlight a clear and significant performance advantage between the \emph{med}\textbackslash\emph{hi} and \emph{lo} settings, but there is not enough evidence to suggest a significant difference in error performance between the \emph{med} and \emph{hi} settings.
-However, the \emph{hi} setting produce results closest to the target tilt.
+They also highlight a clear and significant difference between the three different pitch gain gradients, with the \emph{hi} pitch-gain marginally outperforming the \emph{med} gain setting and producing the results closest to the true tilt.
 
@@
 
-Fig.~\ref{fig:fitts} shows the box-plots of the target search time as a function of the targets' \emph{IDs}.
+\crefrange{fig:fitts-lo}{fig:fitts-hi} shows the box-plots of the target-search time as a function of the \emph{ID} of the targets.
 Here, the bin interval is the smallest effective width, calculated from Equation~\ref{eq:fitts-performance}, between the three gradient settings.
 We used the relation from Equation~\ref{eq:fitts-base} and fitted a logarithmic regression line for each participant.
-The medians of the $a$ and $b$ parameters, from Equation~\ref{eq:fitts-base}, for all the subjects' regressions were used to plot the resulting lines of best fit shown in Figs.~\ref{fig:fitts-lo} - \ref{fig:fitts-hi}.
+The medians of the $a$ and $b$ parameters, from Equation~\ref{eq:fitts-base}, for all the subjects' regressions were used to plot the resulting lines of best fit, shown in \crefrange{fig:fitts-lo}{fig:fitts-hi}.
 
+%\begin{figure}
+  %\centering
+  %\begin{subfigure}[t]{0.5\textwidth}
 \begin{figure}
   \centering
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[clip, trim=120 20 120 20, width=0.95\textwidth]{figures/fitts_lo_sighted.png}
+  \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_lo.png}
   \caption{\emph{Lo} setting. }
   \label{fig:fitts-lo}
-  \end{subfigure}%
-  \begin{subfigure}[t]{0.5\textwidth}
+\end{figure}
+  %\end{subfigure}%
+  %\begin{subfigure}[t]{0.5\textwidth}
+\begin{figure}
   \centering
-    \includegraphics[clip, trim=120 20 120 20, width=0.95\textwidth]{figures/fitts_med_sighted.png}
+  \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_med.png}
   \caption{\emph{Med} setting. }
   \label{fig:fitts-med}
-  \end{subfigure}
+\end{figure}
+  %\end{subfigure}
 
-  \begin{subfigure}[t]{0.5\textwidth}
+  %\begin{subfigure}[t]{0.5\textwidth}
+\begin{figure}
   \centering
-    \includegraphics[clip, trim=120 20 120 20, width=0.95\textwidth]{figures/fitts_hi_sighted.png}
+  \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_hi.png}
   \caption{\emph{Hi} setting. }
   \label{fig:fitts-hi}
-  \end{subfigure}%
-  \begin{subfigure}[t]{0.5\textwidth}
+\end{figure}
+  %\end{subfigure}%
+  %\begin{subfigure}[t]{0.5\textwidth}
+\begin{figure}
   \centering
-    \includegraphics[clip, trim=90 20 130 20, width=0.95\textwidth]{figures/fitts_performance_sighted.png}
+  \includegraphics[clip, trim=90 20 130 20, width=0.4\textwidth]{figures/fitts_performance.png}
   \caption{Boxplots of the indices of performance.}
   \label{fig:fitts-performance}
-  \end{subfigure}
-  \caption{The plots showing Fitts's Law relation between the targets' index of difficulty and the time it took the participants to find the target. The results are summarised in a set of boxplots.}
-  \label{fig:fitts}
 \end{figure}
+  %\end{subfigure}
+  %\caption{The plots showing Fitts's Law relation between the targets' index of difficulty and the time it took the participants to find the target. The results are summarised in a set of boxplots.}
+  %\label{fig:fitts}
+%\end{figure}
 
-From these figures we can see that the data are consistent with Fitts's Law where the logarithmic line of best fit closely approximates the median values of the binned data for all three pitch gradient settings, with each setting giving Pearson correlation scores of 0.9, 0.91 and 0.93 for the \emph{lo}, \emph{med} and \emph{hi} settings respectively ($p < 0.001$ for all 3 settings).
-This result enabled us to compute the indices of performance, \emph{IP}, given by Equation~\ref{eq:fitts-performance}, for all of the subjects and are shown in Fig.~\ref{fig:fitts-performance}.
+From these figures we can see that the data are consistent with Fitts's Law where the logarithmic line of best fit very closely approximates the median values of the binned data for all three pitch gradient settings, with each settings giving Pearson scores of 0.95, 0.87 and 0.93 for the \emph{lo}, \emph{med} and \emph{hi} settings respectively ($p < 0.05$ for all settings).
+This result enabled us to compute the index of performance, $IP$, given by Equation~\ref{eq:fitts-performance}, for all of the subjects.
+These results were used to plot \cref{fig:fitts-performance}, which shows that the \emph{lo} and \emph{med} configurations give similar results, but slightly different spreads, while the \emph{hi} gives a lower $IP$.
+The Friedman score for the three settings gives a $p$-value of 0.017, comfortably achieving statistical significance with a threshold of $\alpha=0.05$.
+The Wilcoxon test comparing the \emph{lo} and \emph{hi} settings achieves significance after applying a Bonferroni correction ($\alpha=0.016$), but the other comparisons do not achieve significance.
 
-A Friedman test on the distributions reveal that there is a significant difference between the 3 settings ($p=0.003<\alpha$) and a set of Wilcoxon tests, with a Bonferroni correction applied to $\alpha$ ($\alpha_c=0.016$) , shows that there is only a significant difference between the \emph{lo} and \emph{hi} settings ($p=0.002<\alpha_c$).
-There is insufficient evidence to suggest a difference between the other settings (\emph{lo} - \emph{med} $\mapsto p=0.16>\alpha_c$, \emph{med} - \emph{hi} $\mapsto p=0.13>\alpha_c$).
-Based on the distributions in Fig.~\ref{fig:fitts-performance} and the statistical analysis, we can conclude that the \emph{hi} setting produces better results with a higher \emph{IP}.
-However, it is not clear where the \emph{med} settings falls in terms of \emph{IP} in relation to the other 2 settings.
-The statistical results are summarised in Table~\ref{tab:fitts-results}.%One might reasonably expect that a time-accuracy trade-off would occur between the 3 settings, i.e.\
-
-\begin{table}
-  \centering
-  \caption{A table summarising the statistical results for the Friedman and Wilcoxon tests.}
-  \label{tab:fitts-results}
-  \begin{tabular}{ccc}
-    \toprule
-    & $\alpha$ & $p$ \\\hline
-    Friedman & 0.05 & 0.003 \\ 
-    \emph{lo - med} & 0.016 & 0.16 \\ 
-    \emph{lo - hi}  & 0.016 & 0.002 \\ 
-    \emph{med - hi} & 0.016 & 0.13 \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-%To compare the 3 settings, we apply a Bonferroni correction $\alpha$ ($\alpha_c=0.016$) and perform a set of Wilcoxon tests to compare \emph{lo} and \emph{hi} ($T_1$), \emph{lo} and \emph{med} ($T_2$) and \emph{med} and \emph{hi} ($T_3$).
-We found that $T_1$ achieved significance ($p=0.012<\alpha_c$), indicating that the time-to-target performances of the \emph{lo} and \emph{hi} settings are significantly different enough to conclude that the \emph{lo} setting produces the superior \emph{IP} of the two settings.
-However, $T_2$ and $T_3$ did not achieve significance ($p=0.8>\alpha_c$ and $p=0.05>\alpha_c$ respectively), indicating that there is not sufficient evidence to rank the 3 settings from best to worst \emph{IP}.
-These results are summarised in Table MEME.
-
-%Applying a Bonferroni correction to $\alpha$ ($\alpha_c=0.016$) and performing post-hoc analyses on the 3 settings with the Wilcoxon test comparing the \emph{lo} and \emph{hi} settings achieves significance after applying a Bonferroni correction for 3 tests to $\alpha$ ($p=0.012$), but the other comparisons do not achieve significance ($p=0.8$ for the \emph{lo} - \emph{med} ($T_2$) comparison, and $p=0.05$ for the \emph{med} - \emph{hi} comparison ($T_3$)).
-These results are summarised in Table MEME.
-
-%A possible explanation for the observed behaviour is that the more distinguishable changes in the audio pitch with the \emph{hi} configuration better informs the user when they are on target, leading to a more accurate estimate, but also increases the time it takes to point in the right direction.
+A possible explanation for the observed behaviour is that the more distinguishable changes in the audio pitch with the \emph{hi} configuration better informs the user when they are on target, leading to a more accurate estimate, but also increases the time it takes to point in the right direction.
 Conversely, the \emph{lo} and \emph{med} gradients make it more difficult for the user to know when they are on target, leading to a shorter search time, but at the cost of lower accuracy.
@@
 
-The results collected from the participants with partial eyesight follow the same trends observed in the blindfolded participants, giving \emph{IP}s of 0.58, 1.3 and 0.35 for the \emph{lo}, \emph{med} and \emph{hi} gradient settings respectively.
+The results collected from the participants with partial eyesight follow the same trends observed in the blindfolded participants, giving $IPs$ of 0.58, 1.3 and 0.35 for the \emph{lo}, \emph{med} and \emph{hi} gradient settings respectively.
 

### 2019-05-13 article.tex
Removed characterisation experiments

@@
 \begin{abstract}
-	Our aim is to build a portable active navigation system for the visually impaired that uses active perception techniques and a combination of feedback modes to identify a scene and guide the user to his/her destination.
-	In this paper, we investigate the effectiveness of a spatial audio tone with a varying pitch component, played through bone-conducting headphones, in conveying the pan and tilt angles of a target to the user in a pointing task.
-	We also wish to see how changes to the rate of change of the pitch affects the user's performance.
-	We conducted a set of experiments with blindfolded and visually impaired users and found that the varying pitch component gives an average error of approximately \SI{20}{\degree} when searching for a target; in line with previous results from other authors.
-	Furthermore, we were able to demonstrate that the audio interface adheres to Fitts's Law and used it as a metric to determine which pitch setting produces the best results.
+	Our aim is to build a portable active navigation system for the visually impaired that uses active perception techniques and a combination of feedback modes to identify a scene and guide a user to their destination.
+	Such a system requires a non-visual feedback interface and in this paper we investigate the effectiveness of a spatial audio tone with a varying pitch component, played through bone-conducting headphones, in conveying the pan and tilt angles of a target to the user in a pointing task.
+	The goal is to determine how changes to the rate of change of the pitch affects a user's performance.
+	For this, wee conducted a set of experiments with blindfolded and visually impaired users and found that the varying pitch component gives an average error of approximately \SI{20}{\degree} when searching for a target; in line with previous results from other authors.
+	Furthermore, we are able to demonstrate that the audio interface adheres to Fitts's Law and used it as a metric to determine which pitch setting produces the optimal results.
 	We discovered a trade-off between the speed and accuracy in the pointing task, which are maximised when the tone's pitch is adjusted to a low and high rate of change respectively. 
@@
 Improvements in modern computing have made it possible for new and innovative solutions for these problems to come to the fore.
-In particular, researchers in the field of active vision have have made much progress in allowing a machine to autonomously manipulate a camera to gain more information about an environment to complete mapping and object and face tracking tasks, for example~\cite{bajcsy2018revisiting}.
+In particular, researchers in the field of active vision have have made much progress in enabling machines to autonomously manipulate cameras to gain more information about an environment to complete mapping and object and face tracking tasks, for example~\cite{bajcsy2018revisiting}.
 There is, however, a significant research question about whether techniques from active machine vision can be applied to humans, i.e.\ can a machine identify a point of interest in a scene and direct a human, instead of an electronic servo, to focus a camera on that point?
-If this can be done, it would be beneficial to people with visual impairments and will allow them to search for an arbitrary point of interest or identify an unknown scene.
+If this can be done, it would be beneficial to people with visual impairments and will augment their ability to search for an arbitrary point of interest or identify an unknown scene.
 
@@
 This system will ultimately allow users with visual impairments to reach a target location in the final leg of their journey, i.e.\ the so-called `last 10 yards' problem~\cite{google2016blind,bellotto2013}.
-The ideas here can also be extended and applied to existing macronavigation tools, such as Google Maps.
+The ideas here can also be extended and applied to mainstream navigation tools, such as Google Maps.
 A Tango-enabled device comes pre-equipped with powerful image-processing, localisation and depth-perception capabilities and is built on top of a standard Android platform, providing access to the entire set of input/output options that this operating system has to offer.
@@
   \includegraphics[width=0.4\textwidth]{figures/tango_headphone.png}
-  \caption{The Tango device and bone-conducting headset used by the participants. }
-  \label{fig:tango-headphone}
+  \caption{The Tango device and bone-conducting headset used by the participants. }\label{fig:tango-headphone}
 \end{figure}
@@
   %\begin{subfigure}[t]{0.45\textwidth}
-\begin{figure}
-  \centering
-  \includegraphics[width=0.4\textwidth]{figures/camera_coordinate.pdf}
-  \caption{A diagram showing the Tango's frame of reference and the target's pan ($\phi$) and tilt ($\theta$) angles.}
-  \label{fig:cam-coords}
-\end{figure}
   %\end{subfigure}
@@
 In this paper we focus on the audio feedback mode and discuss how it is used in our system.
-We present experiments we performed to determine its effectiveness at directing a user to complete a pointing task and how its parameter values affect a user's target-search performance.
-For the pointing task, we presented blindfolded and partially sighted participants with a set of virtual targets, one after another, and asked them to simply point a camera to where they thought the targets were.
-The targets' pan and tilt angles w.r.t.\ the Tango's vertical plane, shown in \cref{fig:cam-coords}, were given to the participants through a spatial tone with varying pitch played via a set of bone-conducting headphones.
+We present experiments we performed to determine its effectiveness at directing a user to complete a pointing task and how its parameters affect users' target-search performance.
+For the pointing task, we presented blindfolded and partially sighted participants with a set of virtual targets, one after another, and asked them to point a camera to where they thought the targets were.
+The targets' pan and tilt angles ($\phi$ and $\theta$ respectively) w.r.t.\ the Tango's vertical plane, shown in \cref{fig:cam-coords}, were given to the participants through a spatial tone with varying pitch played via a set of bone-conducting headphones.
 We use the latter to not interfere with the user's normal hearing function, which people with visual impairments typically rely on.
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/camera_coordinate.pdf}
+  \caption{A diagram showing the Tango's frame of reference and the target's pan ($\phi$) and tilt ($\theta$) angles.}\label{fig:cam-coords}
+\end{figure}
+
 Unfortunately, there is a gap in the literature regarding the use of a such an audio interface for pointing tasks with regards to a mobile device.
 It is also unclear whether popular metrics, such as Fitts's Law~\cite{fitts1954information}, can be applied in this case.
-Fitts's Law is a predictive model in the field of psychomotor research and often used in the human-machine interfacing field that relates the time it takes a user to direct a pointing device toward a target as a function of the difficulty of finding the target (i.e.\ the ratio between the distance to the target and its size).
+Fitts's Law is a predictive model in the field of psychomotor research, often used in the human-machine interfacing field, that relates the time it takes a user to direct a pointing device toward a target as a function of the difficulty of finding the target (i.e.\ the ratio between the distance to the target and its size).
 If a Fitts relationship is found, it can be used as a metric to anticipate whether future adjustments to the pitch's rate of change will have a positive effect on target-search performance.
@@
 
-The remainder of this paper is organised as follows: Section~\ref{sec:lit-review} gives an overview of existing navigation systems and audio interfaces for people living with visual impairments.
-Section~\ref{sec:portable-navigation} discusses the navigation device's hardware and interface setup and describes how the pan and tilt angles are conveyed to the user.
-The experiments that were conducted are explained in Section~\ref{sec:experiments} and the results are presented and discussed in Section~\ref{sec:results}.
-Finally, Section~\ref{sec:conclusion} concludes this paper with a summary of the findings and comments on our future work.
+The remainder of this paper is organised as follows: \cref{sec:lit-review} gives an overview of existing navigation systems and audio interfaces for people living with visual impairments.
+\cref{sec:portable-navigation} discusses the navigation device's hardware and interface setup and describes how $\phi$ and $\theta$ are conveyed to the user.
+The experiments that were conducted are explained in \cref{sec:experiments} and the results are presented and discussed in \cref{sec:results}. 
+Finally, \cref{sec:conclusion} concludes this paper with a summary of the findings and comments on our future work.
 
-\section{Previous Work}
-\label{sec:lit-review}
+\section{Previous Work}\label{sec:lit-review}
 
+\todo{chop up this section. Make anonymous}
 Attempting to deliver a system that allows people with visual impairments to independently navigate and accomplish everyday tasks is not new; in fact, there are multiple commercial systems and research prototypes already available on the market.
@@
 
-%####################################################
-%REVIEW SECTION - MAKE SURE TO MENTION DIFFERENCE BETWEEN BLIND AND SIGHTED , sonification of 3d scenes in an electronic travel aid for the blind.
 Spatial audio has also been considered to convey the direction of a target.
@@
 However, to our knowledge no extensive work or experiments have been done to determine how well users respond to tilt adjustment instructions using a tone with \emph{varying pitch}, in particular when using bone-conducting headphones.
-%########################################################
 
@@
 
-\section{Portable Navigation System}
-\label{sec:portable-navigation}
+\section{Portable Navigation System}\label{sec:portable-navigation}
 
@@
 
-The system we intend to ultimately deliver is a portable navigation device that is capable of guiding a user with visual impairments on the last leg of their journey, e.g.\ to a specific aisle and shelf in a shop.
+We intend to ultimately deliver a portable navigation device that is capable of guiding a user with visual impairments on the last leg of their journey, e.g.\ to a specific aisle and shelf in a shop.
 To do this, we will use a combination of different feedback modes to facilitate two-way communication between the user and the device.
 A large amount of data need to be translated from a visual form into a format that is useful to people with limited or no vision.
-We therefore plan to use a combination of voice, audio and vibration cues to translate the visual navigation data as effectively as possible and overcome the bandwidth limitation of the human ear.
+We therefore plan to use a combination of voice, audio and vibration cues to translate visual navigation data as effectively as possible and overcome the bandwidth limitation of the human ear.
 
-The system is based on a concept proposed in~\cite{bellotto2013, lock2017portable}, which uses a Google Tango device.
+%The system is based on a concept proposed in~\cite{bellotto2013, lock2017portable}, which uses a Google Tango device.
 This is an Android-based cellphone or tablet device that comes equipped with an RGB-D camera to sense colour and depth.
-It combines an inertial measurement unit with powerful and robust landmark recognition and image processing algorithms to localise itself.
+It combines an inertial measurement unit with powerful and robust landmark recognition and image processing algorithms to localise itself in real-time.
 An added benefit of this platform is its familiar, compact form-factor which will help overcome the hurdle of user-acceptance and usability.
 
-We use a set of bone-conducting headphones (see \cref{fig:tango-headphone}) that are placed externally on the user's head so that the system does not occlude the perception of real-world sounds and does not interfere with a user's normal hearing function.
-In the future, our system will use multiple feedback modes to provide the user with navigation and obstacle avoidance instructions.
+We use a set of bone-conducting headphones (see \cref{fig:tango-headphone}) that are placed externally on a user's head so that the system does not occlude the perception of real-world sounds and does not interfere with a user's normal hearing function.
+In the future, we will use multiple feedback modes to provide the user with navigation and obstacle avoidance instructions.
 However, for this paper, we only considered the spatialised audio mode and its variation in pitch in order to determine its effectiveness in conveying a target's pan and tilt angles.
@@
   \includegraphics[clip=true, trim=50 120 80 50, width=0.4\textwidth]{figures/pipeline.pdf}
-  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }
-\label{fig:pipeline}
+  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }\label{fig:pipeline}
 \end{figure}
@@
 The audio component is responsible for conveying the 2D position of a target on the vertical plane w.r.t.\ the Tango's coordinate system, showed in \cref{fig:cam-coords}, in terms of pan and tilt angles.
-Distance to the target can be rendered by adjusting the audio signal's amplitude as a function of the distance.
-However, in this work, this was not implemented.
-The audio signal is a sinusoidal sound wave that is continuously played (refreshed at $\sim$\SI{10}{\hertz}) to the user through bone-conducting headphones.
+In future system iterations, the distance to a target can be rendered by adjusting the audio signal's amplitude as a function of the distance.
+The audio signal is a continuous $\sim$\SI{10}{\hertz} sinusoidal sound wave that is played to the user through bone-conducting headphones.
 We select a sinusoidal wave because it is relatively simple to manipulate and analyse.
@@
 
-The audio is spatialised in the pan dimension using an HRTF provided by the OpenAL sound library\footnote{http://openal.org}, while the tilt angle is conveyed by varying the pitch of the audio tone.
-We use this approach because the external set of bone-conducting headphones plays the sound through the user's cheekbones instead of their outer ears, bypassing the ears' pennae that provide humans their ability to localise elevated sound sources~\cite{roffler1968factors, algazi2001elevation}.
+The audio is spatialised in the pan dimension using the OpenAL\footnote{http://openal.org} sound library's HRTF, while the tilt angle is conveyed by varying the audio tone's pitch.
+We use this approach because the external set of bone-conducting headphones plays the sound through a user's cheekbones instead of their outer ears, bypassing the ears' pennae that provide humans their ability to localise elevated sound sources~\cite{roffler1968factors, algazi2001elevation}.
 This makes an HRTF less effective in conveying the target's tilt angle and therefore needs to be conveyed using another method; a varying pitch tone in this case.
-The difference between the target's angular position and the angular orientation of the Tango device are used to generate the audio signals.
+The difference between the target's angular position and the device's angular orientation are used to generate the audio signals.
 
@@
 
-The pan angle describes the angle which the user needs to rotate the camera vector around the vertical $z$-axis in \cref{fig:cam-coords}, i.e.\ how far the target is to the left or right of the user.
-We use an HRTF to add a spatial element to the audio tone that the system plays to the user, making the tone sound like it is coming from the direction of the target.
-Humans determine the pan direction by subconsciously analysing the time difference between a sound reaching both of your ears.
+The pan angle ($\phi$) describes the angle which the user needs to rotate the camera vector around the $z$-axis in \cref{fig:cam-coords}, i.e.\ how far the target is to the left or right of the user.
+We use an HRTF to add a spatial element to the audio tone that is played to the user, making the tone sound like it is coming from the direction of the target.
+Humans determine a sound source's pan direction by subconsciously analysing the time difference between a sound reaching both of your ears.
 For example, if you hear a sound in your left ear first, you interpret the sound as coming from your left.
-The greater the so-called inter-aural time difference~\cite{wightman1992dominant}, the greater the perceived angular distance to the sound source.
+The greater the so-called inter-aural time difference, the greater the perceived angular distance to the sound source~\cite{wightman1992dominant}.
 
-We implement OpenAL's default HRTF, based on the MIT's KEMAR dataset\footnote{http://sound.media.mit.edu/resources/KEMAR.html}, to generate a sinusoidal sound wave based on the difference between the user and target's positions.
+We implement OpenAL's default HRTF, based on the MIT's KEMAR dataset\footnote{sound.media.mit.edu/resources/KEMAR.html}, to generate a sinusoidal sound wave based on the difference between the user and target's positions.
 The library takes position values as input and outputs a tone based on the angle between the two position vectors.
@@
 
-The system adjusts the tone's pitch to convey the target's tilt angle w.r.t.\ the camera's current pointing vector, $C$, as shown in \cref{fig:cam-coords}. 
+The system adjusts the tone's pitch ($f$) to convey the target's tilt angle ($\theta$) w.r.t.\ the camera's current pointing vector, $C$, as shown in \cref{fig:cam-coords}. 
 Here, a high pitch means the target is above the camera vector (i.e.\ the user should look up) and a low pitch means the target is below the camera vector (the user should look down).
@@
 
-We wish to determine how the gradient of the pitch gain function affects a user's performance.
-For example, does an increased gain rate in the pitch as a function of the tilt angle lead to an increased target acquisition rate?
-For this we select three different pitch gain gradients, referred to here as low (\emph{lo}), medium (\emph{med}) and high (\emph{hi}) gain presets.
-To find these gradients, we set the maximum and minimum limits for the tilt angle and the maximum and minimum frequencies for the pitch.
+We wish to determine how the gradient of the pitch gain as a function of $\theta$ (i.e.\ $m = \frac{df}{d\theta}$) affects a user's performance.
+For example, does steeper $\frac{df}{d\theta}$ lead to an increased target acquisition rate?
+For this we select three different pitch settings, referred to henceforth as $m_l$, $m_m$ and $m_h$ for the smallest, middle and highest gain gradients respectively. 
+To find these gradients, we set the maximum and minimum limits for $\theta$ and the maximum and minimum frequencies for $f$.
 Furthermore, for the sake of consistency, each gradient setting is set to generate the same pitch when the user is pointing the camera towards the target.
 
-After practical tests with the Tango and headphones, we set the neutral, on-target tone to a frequency of \SI{512}{\hertz} for its audibility.
-For the \emph{lo} setting, we set the maximum and minimum pitches to be one octave higher and lower than the neutral tone, giving limits of \SI{1024}{\hertz} and \SI{256}{\hertz} respectively.
-The \emph{med} preset is set to two octaves higher and lower than the neutral tone (\SI{2048}{\hertz} and \SI{128}{\hertz}) and the \emph{hi} to three octaves higher and lower (\SI{4096}{\hertz} and \SI{64}{\hertz}).
+After practical tests with the Tango and headphones, we set the neutral, on-target tone to $f_{512} =$ \SI{512}{\hertz} for its audibility.
+For $m_l$, we set $f_{max}$ and $f_{min}$ to one octave higher and lower than the neutral tone, giving limits of \SI{1024}{\hertz} and \SI{256}{\hertz} respectively.
+For $m_m$, the $f_{max}$ and $f_{min}$ are set to two octaves higher and lower than the neutral tone (\SI{2048}{\hertz} and \SI{128}{\hertz}) and $m_h$ to three octaves higher and lower (\SI{4096}{\hertz} and \SI{64}{\hertz}).
 We selected these limits for practical reasons, given the fact that the bone conducting headphones we use have low volume gain at very high and low frequencies, making it difficult to hear. 
+The values of $m_l, m_m, m_h$ are visualised in \cref{fig:pitch-gain}.
+$f$ is given by \cref{eq:pitch-eq}, where $c$ can be found using the current pitch setting's pitch and angle limits.
 
-The frequency is selected using Equation~\ref{eq:pitch-eq}, where $\theta$ is the tilt angle and $m$ and $c$ are parameters calculated using a linear equation (seen in Equation~\ref{eq:linear}) and the cut-off frequency values.
-Here, $y_m$ is a cut-off frequency, $x_m$ its corresponding angle and $m$ the gradient for the setting, calculated as $m = \frac{\Delta y}{\Delta x}$.
-The pitch gain functions are shown in \cref{fig:pitch-gain}.
-
-\begin{equation}
-  \label{eq:pitch-eq}
+\begin{equation}\label{eq:pitch-eq}
   f = 2^{-m \theta + c}
-\end{equation}
-
-\begin{equation}
-  \label{eq:linear}
-  y - y_m = m(x - x_m)
 \end{equation}
@@
   \includegraphics[width=0.4\textwidth]{figures/pitch_gain_functions.png}
-  \caption{The pitch gain functions for the 3 different gain settings. }
-  \label{fig:pitch-gain}
+  \caption{The pitch gain functions for the 3 different gain settings. }\label{fig:pitch-gain}
 \end{figure}
@@
 The \SI{0}{\radian} position is directly in front of the user.
-We set the range of angles the system can convey to $[-\frac{\pi}{2}; \frac{\pi}{2}]$; anything outside this range implies that the target is behind the user, and was therefore not considered in this series of experiments.
+We set the range of angles the system can convey to $[-\frac{\pi}{2}; \frac{\pi}{2}]$; anything outside this range implies that the target is behind the user and was not considered in this series of experiments.
 
-\section{Experiments}
-\label{sec:experiments}
+\section{Experiments}\label{sec:experiments}
 
-We performed a set of experiments with our audio interface to determine how effective it is at directing a user to adjust the pan and tilt angles of a camera for point it to a target.
-Furthermore, we also carried out a set of pre-screening experiments to determine each participant's hearing characteristics.
-The participants were given time before the experiments commenced to familiarise themselves with the device and the tones it emits, as well as what the `on-target' tone sounds like.
+We performed a set of experiments with our audio interface to determine its effectiveness at directing a user to adjust a camera's $\phi$ and $\theta$ to point it to a target.
+%Furthermore, we also carried out a set of pre-screening experiments to determine each participant's hearing characteristics.
+The results from the experiments allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimise the behaviour of the feedback modes in our portable navigation aid.
+
+The participants were given time before the experiments commenced to familiarise themselves with the device and the tones it emits, as well as what the $f_{512}$ `on-target' tone sounds like.
 We also tested the system with 3 legally blind participants and compared their data to the blindfolded dataset.
-Furthermore, these tests provided us with subjective feedback on the system that can be used to improve future iterations of the system.
-The results from the experiments we performed allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimise the behaviour of the feedback modes in our portable navigation aid.
+These tests in particular provided us with subjective feedback on the system that can be used to improve future iterations.
 
@@
 They performed a series of experiments using our system with a pair of bone-conducting headphones.
-The participants were recruited on a volunteer-basis and consisted of a diverse group of undergraduate students and professionals with ages ranging between 17 and 40 years (13 male, 32 female).
-The participants also reported having no significant hearing issues or any other disability that could affect the experiment.
-The participants participated in three experiments.
-The first two experiments were performed to determine each participant's hearing characteristics and provide some context to the results generated during the target-search experiment.
-These characterisation experiments will also indicate pre-existing biases our participant-base might have in the modes or dimensions we performed our third experiment on: the target search.
+The participants were recruited on a volunteer-basis and consisted of a diverse group of undergraduate students and professionals with ages ranging between 17 and 40 years (13 male, 32 female) and did not not have significant hearing issues or any other disability that could affect the experiment.
+
+%The participants participated in three experiments.
+%The first two experiments were performed to determine each participant's hearing characteristics and provide some context to the results generated during the target-search experiment.
+%These characterisation experiments will also indicate pre-existing biases our participant-base might have in the modes or dimensions we performed our third experiment on: the target search.
 
@@
 
-The distance between the participant and the target is not considered here and the 3D targets are therefore generated at a constant distance of \SI{2}{\metre} from the participant.
+We are only evaluating the interface in the pan and tilt dimensions and the 3D targets are therefore generated at a constant distance of \SI{2}{\metre} from the participant.
 Throughout the experiments, various parameters of the target and the participant are recorded and streamed in real-time to a laptop computer via a WiFi connection.
@@
 
-\subsection{Participant Characterisation}
+%\subsection{Participant Characterisation}
 
-\subsubsection{Spatial Awareness}
+%\subsubsection{Spatial Awareness}
 
-In this experiment, we evaluated a participant's ability to determine the lateral direction a sound is coming from.
-To do this, we played a continuous \SI{512}{\hertz} sinusoidal tone to the participant through the headphones and applied an HRTF to spatialise and place its source to the participant's left or right.
-The participant then had to select the direction the sound came from.
-The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly difficult to localise.
+%In this experiment, we evaluated a participant's ability to determine the lateral direction a sound is coming from.
+%To do this, we played a continuous \SI{512}{\hertz} sinusoidal tone to the participant through the headphones and applied an HRTF to spatialise and place its source to the participant's left or right.
+%The participant then had to select the direction the sound came from.
+%The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly difficult to localise.
 
-For this progressive increase in difficulty, a 2-up, 1-down step process is used~\cite{wetherill1965sequential,levitt1971transformed}, meaning that for every 2 correct answers, the distance to the centre halves, making the lateral direction harder to determine.
-Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre.
-We also use 2 different step sequences, one starting at a large distance (\SI{45}{\degree}) from the user and the other at the minimum distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' step respectively.
-The terminating condition for the experiment is when the 2 step sequences converge to within 2 step ranges of one another for 3 consecutive guesses.
-This gives a distance band within which the participant is capable of localising the sound source. Each participant performed this experiment three times.
+%For this progressive increase in difficulty, a 2-up, 1-down step process is used~\cite{wetherill1965sequential,levitt1971transformed}, meaning that for every 2 correct answers, the distance to the centre halves, making the lateral direction harder to determine.
+%Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre.
+%We also use 2 different step sequences, one starting at a large distance (\SI{45}{\degree}) from the user and the other at the minimum distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' step respectively.
+%The terminating condition for the experiment is when the 2 step sequences converge to within 2 step ranges of one another for 3 consecutive guesses.
+%This gives a distance band within which the participant is capable of localising the sound source. Each participant performed this experiment three times.
 
-\subsubsection{Pitch Discrimination}
+%\subsubsection{Pitch Discrimination}
 
-Here we determined a participant's ability to differentiate pitch, i.e.\ how well they can tell if a tone is high or low pitched.
-We played 2 tones to the participants in succession with the second tone being higher or lower-pitched than the first.
-The participants were then asked to select whether they interpreted the second tone as higher or lower-pitched than the first.
+%Here we determined a participant's ability to differentiate pitch, i.e.\ how well they can tell if a tone is high or low pitched.
+%We played 2 tones to the participants in succession with the second tone being higher or lower-pitched than the first.
+%The participants were then asked to select whether they interpreted the second tone as higher or lower-pitched than the first.
 
-The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first one.
-The tone difference depends on how well the participant can tell the tones apart.
-Like the spatial awareness experiment, a 2-up, 1-down step process is used: for every 2 consecutive correct answers, the pitch difference between the tones is halved, and the difference is doubled for every incorrect answer.
-Two step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
-The termination condition is when the two step sequences are within one octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2^1$) for 3 consecutive answers.
-Each participant performed this experiment twice.
+%The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first one.
+%The tone difference depends on how well the participant can tell the tones apart.
+%Like the spatial awareness experiment, a 2-up, 1-down step process is used: for every 2 consecutive correct answers, the pitch difference between the tones is halved, and the difference is doubled for every incorrect answer.
+%Two step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
+%The termination condition is when the two step sequences are within one octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2^1$) for 3 consecutive answers.
+%Each participant performed this experiment twice.
 
-\subsection{Target Search}
+%\subsection{Target Search}
 
-\subsubsection{Task Description}
+\subsection{Task Description}
 
@@
 
-\subsubsection{Metrics}
+\subsection{Metrics}
 
@@
 
-\subsection{Participant Characterisation}
-\label{sec:character}
+%\subsection{Participant Characterisation}
+%\label{sec:character}
 
-\cref{fig:location-guesses} shows the results for the spatial awareness experiment in the pan direction where the participants had to determine the location of the sound they were played.
-
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=100 20 150 100, width=0.4\textwidth]{figures/location_guesses.png}
-  \caption{Histograms of the spatial awareness experiment in the pan dimension showing the proportion of correct/incorrect guesses per bin interval. }
-  \label{fig:location-guesses}
-\end{figure}
-
-With the relatively low number of erroneous guesses, we see that the participants were accurate in guessing the location of the sound source.
-This is further supported by the large number of samples at the minimum difference of \textasciitilde\SI{3}{\cm}, indicating that the participants reached this level more frequently and consistently.
-We can therefore conclude that the participants had little difficulty determining the pan angle of a sound source.
-These results are in line with what we expected and they are supported by literature which indicates that humans are very adept at localising a sound source, and this ability was apparent for the HRTF-generated pan locations.
-
-The results recorded during the pitch discrimination experiment are shown in \cref{fig:tone-guesses}, where a bar plot is used to show the number of correct guesses for each tone difference level.
-The latter is given in terms of the relative semitone difference between the tones which are obtained using the following relation:
-
-\begin{equation}
-\label{eq:semitone-difference}
-  \Delta f = 12\log_2\frac{f_0}{f_1}.
-\end{equation}
-
-From \cref{fig:tone-guesses}, we can see that the guesses are normally spread around a 0 semitone difference.
-As expected, a larger proportion of incorrect guesses occur around the smaller differences with the majority of samples for correct and incorrect guesses being recorded in the $[-0.25, 0.25]$ semitone difference level.
-Assuming these differences are normally distributed, we fitted a cumulative distribution function (CDF) over each participant's set of results for their correct guesses and used the CDF's parameters to determine the semitone difference threshold, where the participant could no longer reliably tell two tones apart, for each participant.
-See \cref{fig:cdf-semitone} for an example showing the actual CDF of a participant and its approximated normal CDF\@.
-We set this threshold at 75\% of the correct guesses, since this represents a significant majority of samples.
-We found that the median threshold is approximately 0.43 semitones for the sighted participants in a range of [$9.2\times10^-4$, 3.12] semitones.
-We use the median given the skewness of the distribution.
-The plot showing the participants' threshold distribution can be seen in \cref{fig:tone-threshold}.
+%\cref{fig:location-guesses} shows the results for the spatial awareness experiment in the pan direction where the participants had to determine the location of the sound they were played.
 
@@
   %\centering
-  %\begin{subfigure}[t]{0.5\textwidth}
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=80 0 150 100, width=0.4\textwidth]{figures/tone_guesses.png}
-  \caption{Results of the tone limit experiment. }
-  \label{fig:tone-guesses}
-\end{figure}
+  %\includegraphics[clip, trim=100 20 150 100, width=0.4\textwidth]{figures/location_guesses.png}
+  %\caption{Histograms of the spatial awareness experiment in the pan dimension showing the proportion of correct/incorrect guesses per bin interval. }
+  %\label{fig:location-guesses}
+%\end{figure}
 
-\begin{figure}
-  %\end{subfigure}%
-  %\begin{subfigure}[t]{0.5\textwidth}
-  \centering
-  \includegraphics[clip, trim=120 0 120 70, width=0.4\textwidth]{figures/cdf_tone_guesses.png}
-  \caption{Cumulative distribution of the number of correct guesses for one participant. }
-  \label{fig:cdf-semitone}
-\end{figure}
-  %\end{subfigure}
-  %\caption{Histograms of the tone limit experiment showing the proportion of correct/incorrect guesses per bin interval. }
+%With the relatively low number of erroneous guesses, we see that the participants were accurate in guessing the location of the sound source.
+%This is further supported by the large number of samples at the minimum difference of \textasciitilde\SI{3}{\cm}, indicating that the participants reached this level more frequently and consistently.
+%We can therefore conclude that the participants had little difficulty determining the pan angle of a sound source.
+%These results are in line with what we expected and they are supported by literature which indicates that humans are very adept at localising a sound source, and this ability was apparent for the HRTF-generated pan locations.
+
+%The results recorded during the pitch discrimination experiment are shown in \cref{fig:tone-guesses}, where a bar plot is used to show the number of correct guesses for each tone difference level.
+%The latter is given in terms of the relative semitone difference between the tones which are obtained using the following relation:
+
+%\begin{equation}
+%\label{eq:semitone-difference}
+  %\Delta f = 12\log_2\frac{f_0}{f_1}.
+%\end{equation}
+
+%From \cref{fig:tone-guesses}, we can see that the guesses are normally spread around a 0 semitone difference.
+%As expected, a larger proportion of incorrect guesses occur around the smaller differences with the majority of samples for correct and incorrect guesses being recorded in the $[-0.25, 0.25]$ semitone difference level.
+%Assuming these differences are normally distributed, we fitted a cumulative distribution function (CDF) over each participant's set of results for their correct guesses and used the CDF's parameters to determine the semitone difference threshold, where the participant could no longer reliably tell two tones apart, for each participant.
+%See \cref{fig:cdf-semitone} for an example showing the actual CDF of a participant and its approximated normal CDF\@.
+%We set this threshold at 75\% of the correct guesses, since this represents a significant majority of samples.
+%We found that the median threshold is approximately 0.43 semitones for the sighted participants in a range of [$9.2\times10^-4$, 3.12] semitones.
+%We use the median given the skewness of the distribution.
+%The plot showing the participants' threshold distribution can be seen in \cref{fig:tone-threshold}.
+
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=80 0 150 100, width=0.4\textwidth]{figures/tone_guesses.png}
+  %\caption{Results of the tone limit experiment. }
+  %\label{fig:tone-guesses}
 %\end{figure}
@@
   %\centering
-  %\begin{subfigure}[t]{0.5\textwidth}
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=80 20 120 0, width=0.4\textwidth]{figures/tone_threshold.png}
-  \caption{A distribution of the 75\% cut-off frequencies. }
-  \label{fig:tone-threshold}
-\end{figure}
-\begin{figure}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}[t]{0.5\textwidth}
-  \centering
-  \includegraphics[clip, trim=80 20 120 0, width=0.4\textwidth]{figures/tone_medians.png}
-  \caption{A distribution of the median cut-off frequency thresholds along with the median 75\% cut-off threshold. }
-  \label{fig:tone-medians}
-  %\end{subfigure}
-\end{figure}
-  %\caption{Distribution plots showing the cut-off frequencies for the sample group. }
+  %\includegraphics[clip, trim=120 0 120 70, width=0.4\textwidth]{figures/cdf_tone_guesses.png}
+  %\caption{Cumulative distribution of the number of correct guesses for one participant. }
+  %\label{fig:cdf-semitone}
 %\end{figure}
 
-\subsection{Target Search}
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=80 20 120 0, width=0.4\textwidth]{figures/tone_threshold.png}
+  %\caption{A distribution of the 75\% cut-off frequencies. }
+  %\label{fig:tone-threshold}
+%\end{figure}
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=80 20 120 0, width=0.4\textwidth]{figures/tone_medians.png}
+  %\caption{A distribution of the median cut-off frequency thresholds along with the median 75\% cut-off threshold. }
+  %\label{fig:tone-medians}
+%\end{figure}
 
-\subsubsection{Panning Results}
+%\subsection{Target Search}
+
+\subsection{Panning Results}
 
@@
 
-%\begin{figure}
-  %\centering
-  %\begin{subfigure}[t]{0.5\textwidth}
 \begin{figure}
@@
 \begin{figure}
-  %\end{subfigure}%
-  %\begin{subfigure}[t]{0.5\textwidth}
   \centering
@@
 \end{figure}
-  %\end{subfigure}%
 
 \begin{figure}
-  %\begin{subfigure}[t]{0.45\textwidth}
   \centering
@@
 \end{figure}
-  %\end{subfigure}%
-  %\caption{Plots showing the distribution of angular errors in the pan and tilt dimensions for the 3 different pitch gradient settings and summarised in a set of boxplots. }
-%\label{fig:err}
-%\end{figure}
 
-%\begin{figure}
-  %\centering
-  %\begin{subfigure}[t]{0.5\textwidth}
 \begin{figure}
@@
 \end{figure}
-  %\end{subfigure}%
-  %\begin{subfigure}[t]{0.5\textwidth}
+
 \begin{figure}
@@
 \end{figure}
-  %\end{subfigure}
-  %\caption{Boxplots of pan and tilt error results from the target search experiment.}
-  %\label{fig:err-boxplots}
-%\end{figure}
 
@@
 
-\subsubsection{Tilt Results}
-\label{sec:tilt-results}
+\subsection{Tilt Results}\label{sec:tilt-results}
 
@@
 Future improvements to our audio interface should consider a non-linear increase in pitch as a function of tilt angle instead of the linear one we used in this work to remedy this bias.
-\cref{fig:tone-threshold} shows the distribution of the cut-off frequency thresholds that were found in Section~\ref{sec:character}, as well as a plot of the median values of the errors in the tilt dimension, transformed to a frequency using each dataset's respective pitch-gain gradient.
+%\cref{fig:tone-threshold} shows the distribution of the cut-off frequency thresholds that were found in Section~\ref{sec:character}, as well as a plot of the median values of the errors in the tilt dimension, transformed to a frequency using each dataset's respective pitch-gain gradient.
 
-In particular, \cref{fig:tone-medians} indicates that the participants, on average, searched for the target until they could no longer detect a difference between the tone they were played and the \SI{512}{\hertz} on-target tone they were searching for.
-This is shown by the vast majority of the error data being located below the 75\% cut-off threshold frequency of \SI{12.9}{\hertz} (0.43 semitones around \SI{512}{\hertz}).
-Furthermore, it can be seen that the \emph{hi} dataset comes the closest to the cut-off frequency.
-This could explain why it produces the strongest correlation between the targets' true perceived position, since the \emph{hi} pitch gradient is the most sensitive to changes in the tilt angle, it allowed the participants to get closer to the true tilt by playing a more easily distinguishable tone.
+%In particular, \cref{fig:tone-medians} indicates that the participants, on average, searched for the target until they could no longer detect a difference between the tone they were played and the \SI{512}{\hertz} on-target tone they were searching for.
+%This is shown by the vast majority of the error data being located below the 75\% cut-off threshold frequency of \SI{12.9}{\hertz} (0.43 semitones around \SI{512}{\hertz}).
+%Furthermore, it can be seen that the \emph{hi} dataset comes the closest to the cut-off frequency.
+%This could explain why it produces the strongest correlation between the targets' true perceived position, since the \emph{hi} pitch gradient is the most sensitive to changes in the tilt angle, it allowed the participants to get closer to the true tilt by playing a more easily distinguishable tone.
 
@@
   \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_lo.png}
-  \caption{\emph{Lo} setting. }
-  \label{fig:fitts-lo}
+  \caption{\emph{Lo} setting. }\label{fig:fitts-lo}
 \end{figure}
-  %\end{subfigure}%
-  %\begin{subfigure}[t]{0.5\textwidth}
+
 \begin{figure}
@@
 \end{figure}
-  %\end{subfigure}
 
-  %\begin{subfigure}[t]{0.5\textwidth}
 \begin{figure}
@@
 \end{figure}
-  %\end{subfigure}
-  %\caption{The plots showing Fitts's Law relation between the targets' index of difficulty and the time it took the participants to find the target. The results are summarised in a set of boxplots.}
-  %\label{fig:fitts}
-%\end{figure}
 
@@
 
-\section{Conclusion and Future Work}
-\label{sec:conclusion}
+\section{Conclusion and Future Work}\label{sec:conclusion}
 

### 2019-05-14 article.tex

@@
 \usepackage{graphicx}
-\usepackage{caption}
-\usepackage{subcaption}
 \usepackage{multirow}
@@
 
-%\begin{figure}
-  %\centering
-  %\begin{subfigure}[t]{0.45\textwidth}
 \begin{figure}
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/tango_headphone.png}
+  \includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}
   \caption{The Tango device and bone-conducting headset used by the participants. }\label{fig:tango-headphone}
 \end{figure}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}[t]{0.45\textwidth}
-  %\end{subfigure}
-  %\caption{The hardware used during the experiment, as well as a diagram showing the Tango device's coordinate system. }
-%\end{figure}
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/camera_coordinate.pdf}
+  \includegraphics[width=0.4\columnwidth]{figures/camera_coordinate.pdf}
   \caption{A diagram showing the Tango's frame of reference and the target's pan ($\phi$) and tilt ($\theta$) angles.}\label{fig:cam-coords}
@@
 
-%The system is based on a concept proposed in~\cite{bellotto2013, lock2017portable}, which uses a Google Tango device.
+\begin{anonsuppress}
+The system is based on a concept proposed in~\cite{bellotto2013, lock2017portable}, which uses a Google Tango device.
+\end{anonsuppress}
 This is an Android-based cellphone or tablet device that comes equipped with an RGB-D camera to sense colour and depth.
@@
   \centering
-  \includegraphics[clip=true, trim=50 120 80 50, width=0.4\textwidth]{figures/pipeline.pdf}
+  \includegraphics[clip=true, trim=0 120 80 50, width=1.0\columnwidth]{figures/pipeline.pdf}
   \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }\label{fig:pipeline}
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/pitch_gain_functions.png}
+  \includegraphics[width=1.0\columnwidth]{figures/pitch_gain_functions.png}
   \caption{The pitch gain functions for the 3 different gain settings. }\label{fig:pitch-gain}
@@
   \centering
-  \includegraphics[clip, trim=450 0 450 110, width=0.4\textwidth]{figures/err_lo.png}
-  \caption{\emph{Lo} setting. }
-  \label{fig:err-results-lo}
-\end{figure}
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=450 0 450 110, width=0.4\textwidth]{figures/err_med.png}
-  \caption{\emph{Med} setting. }
-  \label{fig:err-results-med}
+  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_lo.png}
+  %\includegraphics[width=1.0\columnwidth]{figures/err_lo.png}
+  \caption{\emph{Lo} setting. }\label{fig:err-results-lo}
 \end{figure}
@@
   \centering
-  \includegraphics[clip, trim=450 0 450 60, width=0.4\textwidth]{figures/err_hi.png}
-  \caption{\emph{Hi} setting. }
-  \label{fig:err-results-hi}
+  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_med.png}
+  %\includegraphics[width=1.0\columnwidth]{figures/err_med.png}
+  \caption{\emph{Med} setting. }\label{fig:err-results-med}
 \end{figure}
@@
   \centering
-  \includegraphics[clip, trim=20 -70 100 100, width=0.4\textwidth]{figures/err_boxplot_medians.png}
-  \caption{Error median.}
-  \label{fig:err-boxplot-median}
+  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_hi.png}
+  %\includegraphics[width=1.0\columnwidth]{figures/err_hi.png}
+  \caption{\emph{Hi} setting. }\label{fig:err-results-hi}
 \end{figure}
@@
   \centering
-  \includegraphics[clip, trim=80 -70 100 0, width=0.4\textwidth]{figures/err_boxplot_std.png}
-  \caption{Error standard deviations.}
-  \label{fig:err-boxplot-std}
+  \includegraphics[clip, trim=20 -70 100 100, width=0.8\columnwidth]{figures/err_boxplot_medians.png}
+  \caption{Error median.}\label{fig:err-boxplot-median}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[clip, trim=80 -70 100 0, width=0.8\columnwidth]{figures/err_boxplot_std.png}
+  \caption{Error standard deviations.}\label{fig:err-boxplot-std}
 \end{figure}
@@
   \caption{A table of the pan and tilt angular error results for the target search experiment.
-The results include the absolute average error ($\mu_{abs}$), average error ($\mu$) and standard deviations ($\sigma$) given in radians, as well as the Spearman ($R$) correlation scores.}
-  \label{tab:results}
-  \begin{tabular}{|c|l|c|c|c|c|}
-    \hline
-    \multicolumn{2}{|c|}{} & $\mu_{abs}$ & $\mu$ & $\sigma$ & $R$ \\\hline\hline
-    & \emph{lo}  & 0.23 & -0.02 & 0.32 & 0.75 \\\cline{2-6}
-    Pan & \emph{med} & 0.21 & -0.01 & 0.28 & 0.77 \\\cline{2-6}
-    & \emph{hi}  & 0.22 & -0.05 & 0.31 & 0.75 \\\hline\hline
-    & \emph{lo}  & 0.40 & -0.14 & 0.46 & 0.38 \\\cline{2-6}
-    Tilt & \emph{med} & 0.32 & -0.12 & 0.36 & 0.48 \\\cline{2-6}
-    & \emph{hi}  & 0.34 & -0.16 & 0.39 & 0.55 \\\hline
+The results include the absolute average error ($\mu_{abs}$), average error ($\mu$) and standard deviations ($\sigma$) given in radians, as well as the Spearman ($R$) correlation scores.}\label{tab:results}
+  \begin{tabular}{llcccc}
+    \toprule
+    \multicolumn{2}{c}{} & $\mu_{abs}$ & $\mu$ & $\sigma$ & $R$ \\\midrule
+    & \emph{lo}  & 0.23 & -0.02 & 0.32 & 0.75 \\%\cmidrule{2-6}
+    Pan & \emph{med} & 0.21 & -0.01 & 0.28 & 0.77 \\%\cmidrule{2-6}
+    & \emph{hi}  & 0.22 & -0.05 & 0.31 & 0.75 \\\midrule
+    & \emph{lo}  & 0.40 & -0.14 & 0.46 & 0.38 \\%\cmidrule{2-6}
+    Tilt & \emph{med} & 0.32 & -0.12 & 0.36 & 0.48 \\%\cmidrule{2-6}
+    & \emph{hi}  & 0.34 & -0.16 & 0.39 & 0.55 \\
+    \bottomrule
   \end{tabular}
@@
   \caption{A table summarising the target search results of the participants with partial eyesight (P1 - P3).
-The results include the average error ($\mu$) and standard deviation ($\sigma$), given in radians in the pan and tilt dimensions.}
-  \label{tab:vi-results}
-  \begin{tabular}{|c|c|cc|cc|cc|}
-    \hline
-    \multicolumn{2}{|c|}{} & \multicolumn{2}{c|}{\emph{lo}} & \multicolumn{2}{c|}{\emph{med}} & \multicolumn{2}{c|}{\emph{hi}} \\
-    \multicolumn{2}{|c|}{} & $\mu_l$ & $\sigma_l$ & $\mu_m$ & $\sigma_m$ & $\mu_h$ & $\sigma_h$ \\\hline\hline
-    & P1 & 0.25 & 0.44 & 0.21 & 0.45 & 0.29 & 0.40 \\ \cline{2-8}
-    Pan & P2 & 0.18 & 0.85 & 0.05 & 0.49 & -0.08 & 0.32 \\ \cline{2-8}
-    & P3 & -0.10 & 0.67 & -0.08 & 0.61 & -0.08 & 0.50 \\ \hline\hline
-    & P1 & -0.17 & 0.21 & -0.10 & 0.2 & -0.25 & 0.21 \\ \cline{2-8}
-    Tilt & P2 & -0.87 & 0.26 & -0.05 & 0.21 & -0.15 & 0.18 \\ \cline{2-8}
-    & P3 & -0.57 & 0.31 & -0.57 & 0.45 & -0.38 & 0.39 \\ \hline
+The results include the average error ($\mu$) and standard deviation ($\sigma$), given in radians in the pan and tilt dimensions.}\label{tab:vi-results}
+  \begin{tabular}{llcccccc}
+    \toprule
+    \multicolumn{2}{c}{} & \multicolumn{2}{c}{\emph{lo}} & \multicolumn{2}{c}{\emph{med}} & \multicolumn{2}{c}{\emph{hi}} \\
+    \multicolumn{2}{c}{} & $\mu_l$ & $\sigma_l$ & $\mu_m$ & $\sigma_m$ & $\mu_h$ & $\sigma_h$ \\\midrule
+         & P1 &  0.25 & 0.44 &  0.21 & 0.45 &  0.29 & 0.40 \\% \cline{2-8}
+    Pan  & P2 &  0.18 & 0.85 &  0.05 & 0.49 & -0.08 & 0.32 \\% \cline{2-8}
+         & P3 & -0.10 & 0.67 & -0.08 & 0.61 & -0.08 & 0.50 \\ \midrule
+         & P1 & -0.17 & 0.21 & -0.10 & 0.2  & -0.25 & 0.21 \\% \cline{2-8}
+    Tilt & P2 & -0.87 & 0.26 & -0.05 & 0.21 & -0.15 & 0.18 \\% \cline{2-8}
+         & P3 & -0.57 & 0.31 & -0.57 & 0.45 & -0.38 & 0.39 \\% \hline
+    \bottomrule
   \end{tabular}

### 2019-05-14 article.tex
Various minor edits, added new reference, added todos to consider removing Fitts stuff and shortening lit review section

@@
-\documentclass[sigconf, review=true, screen=true, anonymous=true]{acmart}
+\documentclass[sigconf, screen=true, anonymous=true]{acmart}
 
@@
 \usepackage{multirow}
+\usepackage[capitalise]{cleveref}
+
+% For editing
+\usepackage{ulem}
 \usepackage{todonotes}
-\usepackage[capitalise]{cleveref}
 
@@
 % Metadata Information
-%\acmConference{SAP}
+\acmConference{SAP}{September 2019}{Barcelona}
 %\acmVolume{9}
@@
 % Paper history
-\received{March 2018}
+\received{May 2019}
 
@@
 
-\keywords{Human-machine interface, vision impairment, navigation aid, spatialised sound, Fitts's Law, pointing task}
+\keywords{Human-machine interface, vision impairment, spatialised sound, Fitts's Law, pointing task}
 
@@
 Improvements in modern computing have made it possible for new and innovative solutions for these problems to come to the fore.
-In particular, researchers in the field of active vision have have made much progress in enabling machines to autonomously manipulate cameras to gain more information about an environment to complete mapping and object and face tracking tasks, for example~\cite{bajcsy2018revisiting}.
-There is, however, a significant research question about whether techniques from active machine vision can be applied to humans, i.e.\ can a machine identify a point of interest in a scene and direct a human, instead of an electronic servo, to focus a camera on that point?
-If this can be done, it would be beneficial to people with visual impairments and will augment their ability to search for an arbitrary point of interest or identify an unknown scene.
+In particular, researchers in the active vision field have have made much progress in enabling machines to autonomously manipulate cameras to gather information about an environment for mapping and object and face tracking tasks~\cite{bajcsy2018revisiting}.
+There is, however, a significant research question about whether techniques from active machine vision can be applied to humans, i.e.\ can a machine identify a point of interest in a scene and direct a human, instead of an electronic servo, to focus on that point?
+If this can be done, it would be beneficial to people with visual impairments and will augment their ability to search for an arbitrary point or object of interest and identify an unknown scene.
 
-To this end, we are developing a mobile device-based navigation system using a Google Project Tango device\footnote{https://developers.google.com/tango}, pictured in \cref{fig:tango-headphone}, that caters to the perception limitations of people with limited vision by using a non-visual interface.
+To this end, we are developing a mobile navigation system using a Google Project Tango tablet device\footnote{https://developers.google.com/tango}, pictured in \cref{fig:tango-headphone}, that caters to the perception limitations of people with limited vision by using a non-visual interface.
 This system will ultimately allow users with visual impairments to reach a target location in the final leg of their journey, i.e.\ the so-called `last 10 yards' problem~\cite{google2016blind,bellotto2013}.
@@
   \includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}
-  \caption{The Tango device and bone-conducting headset used by the participants. }\label{fig:tango-headphone}
+  \caption{The Tango device and bone-conducting headset the system is based on. }\label{fig:tango-headphone}
 \end{figure}
@@
 For the pointing task, we presented blindfolded and partially sighted participants with a set of virtual targets, one after another, and asked them to point a camera to where they thought the targets were.
-The targets' pan and tilt angles ($\phi$ and $\theta$ respectively) w.r.t.\ the Tango's vertical plane, shown in \cref{fig:cam-coords}, were given to the participants through a spatial tone with varying pitch played via a set of bone-conducting headphones.
+The targets' pan and tilt angles w.r.t.\ the device's vertical plane, shown in \cref{fig:cam-coords}, were given to the participants through a spatial tone with varying pitch played via a set of bone-conducting headphones.
 We use the latter to not interfere with the user's normal hearing function, which people with visual impairments typically rely on.
@@
 Therefore, we opted for a tone with varying pitch to convey the angle adjustment required to point the camera in a particular direction.
+A similar audio interface was successfully implemented and evaluated in~\cite{durette2008visuo}, but in this case we are providing guidance instructions for both pan and tilt dimensions and using a non-constant pitch.
+\todo{can maybe cut out Fitts stuff}\uline{It is also unclear whether popular metrics, such as Fitts's Law~\cite{fitts1954information}, can be applied in this case.
+Fitts's Law is a predictive model in the field of psychomotor research, often used in the human-machine interfacing field, that relates the time it takes a user to direct a pointing device toward a target as a function of the difficulty of finding the target (i.e.\ the ratio between the distance to the target and its size).
+If a Fitts relationship is found, it can be used as a metric to anticipate whether future adjustments to the pitch's rate of change will have a positive effect on target-search performance.}
 
@@
   \includegraphics[width=0.4\columnwidth]{figures/camera_coordinate.pdf}
-  \caption{A diagram showing the Tango's frame of reference and the target's pan ($\phi$) and tilt ($\theta$) angles.}\label{fig:cam-coords}
+  \caption{A diagram showing the device's frame of reference and the target's pan and tilt angles.}\label{fig:cam-coords}
 \end{figure}
-
-Unfortunately, there is a gap in the literature regarding the use of a such an audio interface for pointing tasks with regards to a mobile device.
-It is also unclear whether popular metrics, such as Fitts's Law~\cite{fitts1954information}, can be applied in this case.
-Fitts's Law is a predictive model in the field of psychomotor research, often used in the human-machine interfacing field, that relates the time it takes a user to direct a pointing device toward a target as a function of the difficulty of finding the target (i.e.\ the ratio between the distance to the target and its size).
-If a Fitts relationship is found, it can be used as a metric to anticipate whether future adjustments to the pitch's rate of change will have a positive effect on target-search performance.
 
@@
 
-Researchers have previously used Fitts's Law~\cite{fitts1954information}, and more recently MacKenzie's modified version of it~\cite{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
+\todo{cut?}\uline{Researchers have previously used Fitts's Law~\cite{fitts1954information}, and more recently MacKenzie's modified version of it~\cite{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
 Fitts's Law was originally proposed for visual target search tasks.
@@
 These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\cite{wu2010fitts}.
-However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.
+However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.}
 
@@
 
-We intend to ultimately deliver a portable navigation device that is capable of guiding a user with visual impairments on the last leg of their journey, e.g.\ to a specific aisle and shelf in a shop.
-To do this, we will use a combination of different feedback modes to facilitate two-way communication between the user and the device.
+Our ultimate goal is to deliver a navigation system that is capable of guiding a user with visual impairments on the last leg of their journey, e.g.\ to a specific aisle and shelf in a shop, using only a mobile phone.
 A large amount of data need to be translated from a visual form into a format that is useful to people with limited or no vision.
+%To do this, we will use a combination of different feedback modes to facilitate two-way communication between the user and the device.
 We therefore plan to use a combination of voice, audio and vibration cues to translate visual navigation data as effectively as possible and overcome the bandwidth limitation of the human ear.
@@
 \end{anonsuppress}
-This is an Android-based cellphone or tablet device that comes equipped with an RGB-D camera to sense colour and depth.
+The system is based on a Google Tango tablet, an Android-based device that comes equipped with an RGB-D cameras to sense colour and depth.
 It combines an inertial measurement unit with powerful and robust landmark recognition and image processing algorithms to localise itself in real-time.
@@
 
-A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}.
+\todo{Needed?}A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}.
 Here, the arrows indicate the direction of the flow of information.
@@
 The audio signal is a continuous $\sim$\SI{10}{\hertz} sinusoidal sound wave that is played to the user through bone-conducting headphones.
-We select a sinusoidal wave because it is relatively simple to manipulate and analyse.
-A richer and more natural tone will be implemented at a later stage of the project.
+We select a sinusoidal wave because it is relatively simple to manipulate and analyse, which will be replaced by a richer, more natural tone at a later stage of the project.
 
@@
 
-The pan angle ($\phi$) describes the angle which the user needs to rotate the camera vector around the $z$-axis in \cref{fig:cam-coords}, i.e.\ how far the target is to the left or right of the user.
-We use an HRTF to add a spatial element to the audio tone that is played to the user, making the tone sound like it is coming from the direction of the target.
-Humans determine a sound source's pan direction by subconsciously analysing the time difference between a sound reaching both of your ears.
-For example, if you hear a sound in your left ear first, you interpret the sound as coming from your left.
-The greater the so-called inter-aural time difference, the greater the perceived angular distance to the sound source~\cite{wightman1992dominant}.
+The pan angle ($\phi$) describes the angle which the user needs to rotate the camera vector, $C$, around the $z$-axis shown in \cref{fig:cam-coords}, i.e.\ how far the target is to the left or right of the user.
+We use an HRTF to add a spatial element to the audio tone that is played to the user, placing the sound source at the target's location. 
+Humans determine a sound source's pan direction by subconsciously analysing the inter-aural time difference (IID) between a sound reaching both of your ears: the greater the IID, the greater the perceived angular distance to the sound source~\cite{wightman1992dominant}.
+%For example, if you hear a sound in your left ear first, you interpret the sound as coming from your left.
 
@@
 
-The system adjusts the tone's pitch ($f$) to convey the target's tilt angle ($\theta$) w.r.t.\ the camera's current pointing vector, $C$, as shown in \cref{fig:cam-coords}. 
-Here, a high pitch means the target is above the camera vector (i.e.\ the user should look up) and a low pitch means the target is below the camera vector (the user should look down).
+The system adjusts the tone's pitch ($f$) to convey the target's tilt angle ($\theta$) w.r.t.\ $C$, as shown in \cref{fig:cam-coords}. 
+Here, a high pitch means the target is above $C$ (i.e.\ the user should look up) and a low pitch means the target is below $C$ (the user should look down).
 This high/low association scheme is chosen because humans naturally associate high-pitched sounds with higher objects and lower-pitched noises with lower objects~\cite{pratt1930spatial, blauert1997spatial}.
@@
 
-We wish to determine how the gradient of the pitch gain as a function of $\theta$ (i.e.\ $m = \frac{df}{d\theta}$) affects a user's performance.
-For example, does steeper $\frac{df}{d\theta}$ lead to an increased target acquisition rate?
+We wish to determine how the gradient of the pitch gain as a function of $\theta$ (i.e.\ $m = \frac{df}{d\theta}$) affects a user's performance, e.g.\ does steeper $\frac{df}{d\theta}$ lead to an increased target acquisition rate?
 For this we select three different pitch settings, referred to henceforth as $m_l$, $m_m$ and $m_h$ for the smallest, middle and highest gain gradients respectively. 
-To find these gradients, we set the maximum and minimum limits for $\theta$ and the maximum and minimum frequencies for $f$.
-Furthermore, for the sake of consistency, each gradient setting is set to generate the same pitch when the user is pointing the camera towards the target.
+To find these gradients, we set the maximum and minimum limits for $\theta$ and the maximum and minimum frequencies for $f$ for each respective setting.
+Furthermore, for the sake of consistency and between the different settings, each gradient generates the same pitch when $C$ is level with the target's tilt.
 
-After practical tests with the Tango and headphones, we set the neutral, on-target tone to $f_{512} =$ \SI{512}{\hertz} for its audibility.
-For $m_l$, we set $f_{max}$ and $f_{min}$ to one octave higher and lower than the neutral tone, giving limits of \SI{1024}{\hertz} and \SI{256}{\hertz} respectively.
-For $m_m$, the $f_{max}$ and $f_{min}$ are set to two octaves higher and lower than the neutral tone (\SI{2048}{\hertz} and \SI{128}{\hertz}) and $m_h$ to three octaves higher and lower (\SI{4096}{\hertz} and \SI{64}{\hertz}).
+After practical tests with the device and headphones, we set the neutral, on-target tone to $f_{512} =$ \SI{512}{\hertz} for its audibility.
+For $m_l$, we set $f_{max}$ and $f_{min}$ to one octave higher and lower than $f_{512}$, giving limits of \SI{1024}{\hertz} and \SI{256}{\hertz} respectively.
+For $m_m$, the $f_{max}$ and $f_{min}$ are set to two octaves higher and lower than $f_{512}$ (\SI{2048}{\hertz} and \SI{128}{\hertz}) and $m_h$ to three octaves higher and lower (\SI{4096}{\hertz} and \SI{64}{\hertz}).
 We selected these limits for practical reasons, given the fact that the bone conducting headphones we use have low volume gain at very high and low frequencies, making it difficult to hear. 
 The values of $m_l, m_m, m_h$ are visualised in \cref{fig:pitch-gain}.
-$f$ is given by \cref{eq:pitch-eq}, where $c$ can be found using the current pitch setting's pitch and angle limits.
-
-\begin{equation}\label{eq:pitch-eq}
-  f = 2^{-m \theta + c}
-\end{equation}
 
@@
 
+We set the range of angles the system can convey to $[-\frac{\pi}{2}; \frac{\pi}{2}]$; anything outside this range implies that the target is behind the user and was not considered in this series of experiments.
 The \SI{0}{\radian} position is directly in front of the user.
-We set the range of angles the system can convey to $[-\frac{\pi}{2}; \frac{\pi}{2}]$; anything outside this range implies that the target is behind the user and was not considered in this series of experiments.
+With these limits, $f$ can be determined with $f(\theta) = 2^{-m\theta + c}$, where $m$ is the given gradient setting and $c$ can be found using the current setting's pitch and angle limits.
 
@@
 
-The participants were given time before the experiments commenced to familiarise themselves with the device and the tones it emits, as well as what the $f_{512}$ `on-target' tone sounds like.
+The participants were given time before the experiments to familiarise themselves with the device and the tones it emits, as well as what the $f_{512}$ `on-target' tone sounds like.
 We also tested the system with 3 legally blind participants and compared their data to the blindfolded dataset.
-These tests in particular provided us with subjective feedback on the system that can be used to improve future iterations.
+These latter experiments in particular provided us with valuable subjective feedback that can be used to improve future iterations.
 
@@
 
-For the experiments we used two groups of participants, with one including 42 sighted and blindfolded participants and the other 3 legally blind volunteers with varying degrees of vision impairment. 
-They performed a series of experiments using our system with a pair of bone-conducting headphones.
-The participants were recruited on a volunteer-basis and consisted of a diverse group of undergraduate students and professionals with ages ranging between 17 and 40 years (13 male, 32 female) and did not not have significant hearing issues or any other disability that could affect the experiment.
+For the experiments we used two groups of participants, with one ($G1$) including 42 sighted and blindfolded participants and the other ($G2$) 3 legally blind volunteers with varying degrees of vision impairment.
+They performed a series of experiments using our system with a pair of `AfterShockz Sport3' bone-conducting headphones.
+The participants were recruited on a volunteer-basis and consisted of a diverse group of undergraduate students and professionals with ages ranging between 17 and 40 years ($\mu=22\pm3.5$ years, 13 male, 32 female) and did not not have significant hearing issues or any other disability that could affect the experiment.
 
@@
 We are only evaluating the interface in the pan and tilt dimensions and the 3D targets are therefore generated at a constant distance of \SI{2}{\metre} from the participant.
-Throughout the experiments, various parameters of the target and the participant are recorded and streamed in real-time to a laptop computer via a WiFi connection.
-Prior to the target search experiment, the blindfolded participant group was given a few minutes without a blindfold to familiarise themselves with the system and confirm the target's location with their own eyes.
-This was done verbally with the participants with limited vision.
+Throughout the experiments, various parameters of the targets and participants were recorded and streamed in real-time to a laptop computer via a WiFi connection.
+%Prior to the target search experiment, the blindfolded participant group was given a few minutes without a blindfold to familiarise themselves with the system and confirm the target's location with their own eyes.
+%This was done verbally with the participants with limited vision.
 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{bib}
+%\bibliography{bib}
 

### 2019-05-14 article.tex
More formatting, fixes to setting notation and equations

@@
 The remainder of this paper is organised as follows: \cref{sec:lit-review} gives an overview of existing navigation systems and audio interfaces for people living with visual impairments.
-\cref{sec:portable-navigation} discusses the navigation device's hardware and interface setup and describes how $\phi$ and $\theta$ are conveyed to the user.
+\cref{sec:portable-navigation} discusses the navigation device's hardware and interface setup and describes how the target's position is conveyed to the user.
 The experiments that were conducted are explained in \cref{sec:experiments} and the results are presented and discussed in \cref{sec:results}. 
@@
 We wish to determine how the gradient of the pitch gain as a function of $\theta$ (i.e.\ $m = \frac{df}{d\theta}$) affects a user's performance, e.g.\ does steeper $\frac{df}{d\theta}$ lead to an increased target acquisition rate?
-For this we select three different pitch settings, referred to henceforth as $m_l$, $m_m$ and $m_h$ for the smallest, middle and highest gain gradients respectively. 
+For this we select 3 different pitch settings, referred to henceforth as $m_l$, $m_m$ and $m_h$ for the smallest, middle and highest gain gradients respectively. 
 To find these gradients, we set the maximum and minimum limits for $\theta$ and the maximum and minimum frequencies for $f$ for each respective setting.
@@
 After practical tests with the device and headphones, we set the neutral, on-target tone to $f_{512} =$ \SI{512}{\hertz} for its audibility.
-For $m_l$, we set $f_{max}$ and $f_{min}$ to one octave higher and lower than $f_{512}$, giving limits of \SI{1024}{\hertz} and \SI{256}{\hertz} respectively.
-For $m_m$, the $f_{max}$ and $f_{min}$ are set to two octaves higher and lower than $f_{512}$ (\SI{2048}{\hertz} and \SI{128}{\hertz}) and $m_h$ to three octaves higher and lower (\SI{4096}{\hertz} and \SI{64}{\hertz}).
+For $m_l$, we set $f_{max}$ and $f_{min}$ to 1 octave higher and lower than $f_{512}$, giving limits of \SI{1024}{\hertz} and \SI{256}{\hertz} respectively.
+For $m_m$, the $f_{max}$ and $f_{min}$ are set to 2 octaves higher and lower than $f_{512}$ (\SI{2048}{\hertz} and \SI{128}{\hertz}) and $m_h$ to 3 octaves higher and lower (\SI{4096}{\hertz} and \SI{64}{\hertz}).
 We selected these limits for practical reasons, given the fact that the bone conducting headphones we use have low volume gain at very high and low frequencies, making it difficult to hear. 
@@
 The \SI{0}{\radian} position is directly in front of the user.
-With these limits, $f$ can be determined with $f(\theta) = 2^{-m\theta + c}$, where $m$ is the given gradient setting and $c$ can be found using the current setting's pitch and angle limits.
+With these limits, $f$ can be determined with \cref{eq:frequency}, where $m$ is the given setting's gradient, $\frac{df}{d\theta}$, and $c$ can be found using the current setting's pitch and angle limits.
+
+\begin{equation}\label{eq:frequency}
+  f(\theta) = 2^{-m\theta + c}
+\end{equation}
 
@@
 
-The final experiment is the main one and will answer the question we are most interested in: how well does a spatial tone with varying pitch direct a user to look in a specific direction and how do the parameters of this tone affect the user's performance in this task?
+%The final experiment is the main one and will answer the question we are most interested in: how well does a spatial tone with varying pitch direct a user to look in a specific direction and how do the parameters of this tone affect the user's performance in this task?
 
-For this experiment, the participants were blindfolded where necessary and given a Tango device running an app purpose-written for this experiment.
-When started, a set of virtual targets were presented one at a time to the participant on the Tango device.
+For the experiment, the participants were blindfolded where necessary and given a Tango device running an app purpose-written for this experiment.
+When started, a set of virtual targets were presented one at a time to the participant on the device.
 Then, depending on the direction the participant was currently pointing the camera relative to the target's position, the Tango generated and played a tone via the bone-conducting headphones to indicate the pan and tilt angle adjustment required to point the camera to the target.
@@
 
-Once the participant pointed the camera toward the target, the system generated a neutral tone with a pitch of \SI{512}{\hertz}, which we used as the `on-target' pitch for all of our experiments.
-The participants then had to manually confirm the direction they believe the target was after hearing the on-target tone and tap the screen.
-At this point a new search target was presented and the search-process was repeated.
-To minimise any speed/accuracy trade-off bias in the results, we asked the participants to search for the targets without placing particular emphasis on accuracy or time.
-
+Once the participant pointed the camera toward where they thought the target was located, they had to tap the screen to confirm the target's perceived location at which point a new target was presented and the search-process was repeated.
 28 targets were presented to each participant per run.
 The positions of these targets were randomly generated and equally spread across the 4 quadrants on the vertical plane to prevent a clustering of targets at the same location.
-After every run of the experiment, the parameters controlling the tone's behaviour was adjusted.
-In this case, the rate of change of the tone's pitch was adjusted to make the pitch increase at a lower or higher rate as a function of the tilt angle between the target and the participant's current pointing direction.
+After every experiment run, the gradient ($m$ in \cref{eq:frequency}) was adjusted to make the pitch increase at a lower or higher rate.
 This was done to see whether, for example, a more rapid increase in pitch would help the participant find the target faster or more accurately.
+
+To minimise any speed/accuracy trade-off bias in the results, we asked the participants to search for the targets without placing particular emphasis on accuracy or time. 
 The order in which the settings were set for each participant was randomised in order to minimise any learning effect the participant population might display between each experiment.
@@
 
-We use two different metrics to compare the three different pitch gradient settings: the acquisition accuracy and search time.
-The accuracy is given as the difference between the Tango's orientation at the time the participant confirmed they were on target, and the target's actual orientation.
-We separate the results of the tilt and pan dimensions in order to see how the different pitch gradients affect a participant's pointing accuracy.
+We use two different metrics to compare the 3 different pitch gradient settings: the acquisition accuracy and search time.
+The accuracy is given as the difference between the device's orientation at the time the participant confirmed they were on target, and the target's actual angular position.
+We separate the results of the tilt and pan dimensions in order to determine how the different pitch settings affect pointing accuracy.
 
-We also compare the performance of the three pitch gradient settings in terms of the time it takes each participant to find a target.
+\todo{Needed?}We also compare the performance of the 3 pitch gradient settings in terms of the time it takes each participant to find a target.
 However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
 Instead, we use Fitts's Law~\cite{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\cite{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty (the ratio between the distance to the target and its width).
-It also provides a so-called `index of performance' that we can use as a metric to compare the results between the three configurations.
+It also provides a so-called `index of performance' that we can use as a metric to compare the results between the 3 configurations.
 
@@
 
-The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \crefrange{fig:err-results-lo}{fig:err-results-hi}, where the angular errors in the pan and tilt directions are plotted against each other.
-A set of box-plots of the pan errors' median and standard deviations are also given in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} for each of the \emph{lo}, \emph{med} and \emph{hi} configurations.
+The results from the target search experiment for the participants in $G1$ in the pan dimension are given on the abscissa of the 2D histograms in \crefrange{fig:err-results-lo}{fig:err-results-hi}, where the angular errors in the pan and tilt directions are plotted against each other.
+A set of box-plots of the pan errors' median and standard deviations are also given in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} for each of the $m_l, m_m$ and $m_h$ setting. 
 The results are summarised in Table~\ref{tab:results}.
@@
   %\includegraphics[width=1.0\columnwidth]{figures/err_lo.png}
-  \caption{\emph{Lo} setting. }\label{fig:err-results-lo}
+  \caption{Angular error data for $G1$ and the $m_l$ setting. }\label{fig:err-results-lo}
 \end{figure}
@@
   %\includegraphics[width=1.0\columnwidth]{figures/err_med.png}
-  \caption{\emph{Med} setting. }\label{fig:err-results-med}
+  \caption{Angular error data for $G1$ and the $m_m$ setting. }\label{fig:err-results-med}
 \end{figure}
@@
   %\includegraphics[width=1.0\columnwidth]{figures/err_hi.png}
-  \caption{\emph{Hi} setting. }\label{fig:err-results-hi}
+  \caption{Angular error data for $G1$ and the $m_h$ setting. }\label{fig:err-results-hi}
 \end{figure}
@@
   \includegraphics[clip, trim=20 -70 100 100, width=0.8\columnwidth]{figures/err_boxplot_medians.png}
-  \caption{Error median.}\label{fig:err-boxplot-median}
+  \caption{Error medians for $G1$.}\label{fig:err-boxplot-median}
 \end{figure}
@@
   \includegraphics[clip, trim=80 -70 100 0, width=0.8\columnwidth]{figures/err_boxplot_std.png}
-  \caption{Error standard deviations.}\label{fig:err-boxplot-std}
+  \caption{Error standard deviations for $G1$.}\label{fig:err-boxplot-std}
 \end{figure}
@@
   \centering
-  \caption{A table of the pan and tilt angular error results for the target search experiment.
+  \caption{A table of the pan and tilt angular error results collected from $G1$.
 The results include the absolute average error ($\mu_{abs}$), average error ($\mu$) and standard deviations ($\sigma$) given in radians, as well as the Spearman ($R$) correlation scores.}\label{tab:results}
@@
     \multicolumn{2}{c}{} & $\mu_{abs}$ & $\mu$ & $\sigma$ & $R$ \\\midrule
-    & \emph{lo}  & 0.23 & -0.02 & 0.32 & 0.75 \\%\cmidrule{2-6}
-    Pan & \emph{med} & 0.21 & -0.01 & 0.28 & 0.77 \\%\cmidrule{2-6}
-    & \emph{hi}  & 0.22 & -0.05 & 0.31 & 0.75 \\\midrule
-    & \emph{lo}  & 0.40 & -0.14 & 0.46 & 0.38 \\%\cmidrule{2-6}
-    Tilt & \emph{med} & 0.32 & -0.12 & 0.36 & 0.48 \\%\cmidrule{2-6}
-    & \emph{hi}  & 0.34 & -0.16 & 0.39 & 0.55 \\
+         & $m_l$ & 0.23 & -0.02 & 0.32 & 0.75 \\%\cmidrule{2-6}
+    Pan  & $m_m$ & 0.21 & -0.01 & 0.28 & 0.77 \\%\cmidrule{2-6}
+         & $m_h$ & 0.22 & -0.05 & 0.31 & 0.75 \\\midrule
+         & $m_l$ & 0.40 & -0.14 & 0.46 & 0.38 \\%\cmidrule{2-6}
+    Tilt & $m_m$ & 0.32 & -0.12 & 0.36 & 0.48 \\%\cmidrule{2-6}
+         & $m_h$ & 0.34 & -0.16 & 0.39 & 0.55 \\
     \bottomrule
@@
 
-There is a strong linear correlation between the participants' guesses and the targets' true pan angles, shown by the high Spearman correlation scores of approximately 0.75 ($p \ll 0.05$) for all of the datasets, with the \emph{med} configuration displaying the marginally best result of 0.77.
-The three settings have similar average errors and standard deviations, with the \emph{med} configuration again producing the marginally best results with the smallest average error and standard deviation.
-However, the differences are small (approximately 6\%) and are not significant enough (Friedman test $p \gg 0.05$) to conclude that the pitch gradient has an effect on the performance in the pan dimension.
+For the data collected from $G1$, there is a strong linear correlation between the participants' guesses and the targets' true pan angles, shown by the high Spearman correlation scores of approximately 0.75 ($p < 0.01$) for all of the datasets, with the $m_m$ setting displaying the marginally best result of 0.77.
+The 3 settings have similar average errors and standard deviations, with the $m_m$ setting again producing the marginally best results with the smallest average error and standard deviation.
+However, the differences are relatively small (approximately 6\%) and are not significant enough (Friedman test $p \gg 0.05$) to conclude that the pitch gradient has an effect on the target acquisition accuracy performance in the pan dimension.
 
-The data collected from the participants with partial eyesight follow a similar trend to that of the blindfolded participants: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all three settings.
+The data collected from $G2$ follow a similar trend to that of $G1$: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all 3 settings.
 These results are summarised in Table~\ref{tab:vi-results}.
@@
 However, these results are in line with results from previous work~\cite{zwiers2001spatial}, indicating that the groups with partial and normal eyesight respond with similar levels of accuracy to spatialised sound when presented with simple tasks.
+In addition, they also confirm that a participant's target search capability in the pan dimension is robust to the changing pitch for the target's tilt angle which is a useful result in support of the effectiveness of our audio interface.
 
@@
   \centering
-  \caption{A table summarising the target search results of the participants with partial eyesight (P1 - P3).
+  \caption{A table summarising the target search results of the participants in $G2$ (P1 - P3).
 The results include the average error ($\mu$) and standard deviation ($\sigma$), given in radians in the pan and tilt dimensions.}\label{tab:vi-results}
@@
     \toprule
-    \multicolumn{2}{c}{} & \multicolumn{2}{c}{\emph{lo}} & \multicolumn{2}{c}{\emph{med}} & \multicolumn{2}{c}{\emph{hi}} \\
+    \multicolumn{2}{c}{} & \multicolumn{2}{c}{$m_l$} & \multicolumn{2}{c}{$m_m$} & \multicolumn{2}{c}{$m_h$} \\
     \multicolumn{2}{c}{} & $\mu_l$ & $\sigma_l$ & $\mu_m$ & $\sigma_m$ & $\mu_h$ & $\sigma_h$ \\\midrule
@@
 
-Based on previous research~\cite{zwiers2001spatial}, these results were somewhat expected.
-In addition, they also confirm that a participant's target search capability in the pan dimension is robust to the changing pitch for the target's tilt angle which is a useful result in support of the effectiveness of our audio interface.
+%Based on previous research~\cite{zwiers2001spatial}, these results were somewhat expected.
 
@@
 
-Besides the pan, the ordinates in \crefrange{fig:err-results-lo}{fig:err-results-hi} also show the results recorded during the target search experiment for the tilt direction.
-A set of box-plots are given in \cref{fig:err-boxplot-median} to show the average tilt error between the participants' guesses and the targets' true positions.
-All of the results are summarised in Table~\ref{tab:results}. 
+The ordinates in \crefrange{fig:err-results-lo}{fig:err-results-hi} also show the results recorded during the experiment with $G1$ in the tilt direction.
+A set of box-plots are given in \cref{fig:err-boxplot-median} to show the average tilt error between the participants in $G1$'s guesses and the targets' true positions.
+All of the results are summarised in \cref{tab:results}. 
 The data here are also considered not normally distributed following inspections of the Q-Q plots and Shapiro-Wilkes test results and are analysed accordingly.
 
-We found that there is reasonably significant correlation between the participants' guesses and the actual locations of the targets, shown by moderate Spearman correlation scores of approximately 0.38 for \emph{lo}, 0.48 for \emph{med} and the \emph{hi} gradient giving the strongest R-scores of the three with a score of 0.55 ($p \ll 0.05$ for all 3 settings).
+We found that there is reasonably significant correlation between the participants' guesses and the actual locations of the targets, shown by moderate Spearman correlation scores of approximately 0.38 for \emph{lo}, 0.48 for \emph{med} and the \emph{hi} gradient giving the strongest R-scores of the 3 with a score of 0.55 ($p < 0.01$ for all 3 settings).
 This indicates that the varying pitch is working as expected and the participants are generally interpreting the cues correctly.
 
-The average errors of the datasets are relatively close to one another, with the \emph{lo} gradient giving the largest absolute error and standard deviation at \SI{0.40}{\radian} and \SI{0.46}{\radian}.
-The \emph{med} and \emph{hi} have similar absolute errors of \SI{0.32}{\radian} and \SI{0.34}{\radian} respectively.
-This is in line with the correlation scores, with the \emph{lo} gradient giving a worse result than the \emph{med} and \emph{hi} gradients and the \emph{hi} gradient giving the best results overall, with its high correlation score and relatively low absolute angular errors and standard deviation.
+The average errors of the datasets are relatively close to one another, with the $m_l$ setting producing the largest absolute error and standard deviation at \SI{0.40}{\radian} and \SI{0.46}{\radian}.
+The $m_m$ and $m_h$ settings have similar absolute errors of \SI{0.32}{\radian} and \SI{0.34}{\radian} respectively.
+This is in line with the correlation scores, with $m_l$ giving a worst result and $m_h$ giving the best results overall, with highest correlation score and relatively low absolute angular errors and standard deviation, marginally beating $m_m$.
 
-We use the Friedman test~\cite{friedman1937use} on the medians of the data to find the statistical significance of the differences between the datasets.
+We use the Friedman test on the medians of the data to better understand the difference differences between the datasets.
 We use the median values here since the data are not normally spread and there is significant noise within the data which may contaminate the mean values.
-This results in a $p$-value of 0.002, which falls below the commonly-used critical threshold of 0.05, implying that there is a statistically significant difference between the three settings.
-A post-hoc analysis with a Wilcoxon signed rank test and a critical threshold with a Bonferroni correction applied for the 3 settings ($\alpha=0.016$) shows that both the \emph{med} and \emph{hi} settings are significantly different than the \emph{lo} setting ($p=0.0014$ for both settings), but that the \emph{med} and \emph{hi} settings do not produce significantly different results from one another ($p=0.42$).
-This is supported by the earlier observations made on the average and standard deviations of the error data which indicate that the \emph{lo} setting gives the highest average errors, while the \emph{med} and \emph{hi} settings produce similar error levels.
+The Friedman test indicates a statistically significant difference between the 3 settings ($p < 0.01$).
+A post-hoc analysis with a Wilcoxon signed rank test and a critical threshold with a Bonferroni correction applied for the 3 settings ($\alpha=0.016=\frac{0.04}{3}$) shows that both the $m_m$ and $m_h$ settings are significantly different than the $m_l$ setting ($p=0.0014$ for both settings), but that the $m_m$ and $m_h$ settings do not produce significantly different results from one another ($p=0.42$).
+This indicates there is an inflection point where increasing $\frac{df}{d\theta}$ produces diminishing returns.
+%This is supported by the earlier observations made on the average and standard deviations of the error data which indicate that the $m_l$ setting gives the highest average errors, while $m_m$ and $m_h$ produce similar error levels.
 
@@
 
-Given the small sample size, there is limited meaningful statistical analysis we can do on the data collected from the participants with visual impairments.
-However, it could be seen from the results in Table~\ref{tab:vi-results} that these participants displayed the same behaviour in our experiments, with a clear bias toward the lower angles (i.e.\ the floor) and not-insignificant variability between the three settings in the tilt dimension.
-Similarly, the pan dimension remains more stable throughout the three settings.
-The participants also confirmed that they preferred the \emph{hi} setting, since it was more responsive and gave them a clearer idea of the direction they needed to point to.
+Given the small sample size in $G2$, there is limited meaningful statistical analysis we can do on the data collected from the participants with visual impairments.
+However, it could be seen from the results in \cref{tab:vi-results} that these participants displayed the same behaviour in our experiments with a clear bias toward the lower angles (i.e.\ the floor) and not-insignificant variability between the 3 settings.
+%Similarly, the pan dimension remains more stable throughout the 3 settings.
+The participants also confirmed that they preferred the increased response rate of the \emph{hi} setting, reporting that it gave them a clearer idea of the direction they needed to point to.
 
-These results show that a varying pitch tone can convey the tilt angle of a target to a human using bone-conducting headphones with accuracy levels similar to that in the literature~\cite{bujacz2011sonification, katz2011spatial, zotkin2004rendering}.
-They also highlight a clear and significant difference between the three different pitch gain gradients, with the \emph{hi} pitch-gain marginally outperforming the \emph{med} gain setting and producing the results closest to the true tilt.
+The results collected from $G1$ and $G2$ show that a varying pitch tone can convey the tilt angle of a target to a human using bone-conducting headphones with accuracy levels similar to that in literature~\cite{bujacz2011sonification, katz2011spatial, zotkin2004rendering}.
+They also highlight a clear and significant difference between the 3 different pitch gain gradients, with the $m_l$ setting giving the lowest acquisition accuracy, while $m_m$ and $m_h$ give similar accuracy levels closest to the true tilt.
 
@@
 \crefrange{fig:fitts-lo}{fig:fitts-hi} shows the box-plots of the target-search time as a function of the \emph{ID} of the targets.
-Here, the bin interval is the smallest effective width, calculated from Equation~\ref{eq:fitts-performance}, between the three gradient settings.
-We used the relation from Equation~\ref{eq:fitts-base} and fitted a logarithmic regression line for each participant.
-The medians of the $a$ and $b$ parameters, from Equation~\ref{eq:fitts-base}, for all the subjects' regressions were used to plot the resulting lines of best fit, shown in \crefrange{fig:fitts-lo}{fig:fitts-hi}.
+Here, the bin interval is the smallest effective width, calculated from \cref{eq:fitts-performance}, between the 3 gradient settings.
+We used the relation from \cref{eq:fitts-base} and fitted a logarithmic regression line for each participant.
+The medians of the $a$ and $b$ parameters, from \cref{eq:fitts-base}, for all the subjects' regressions were used to plot the resulting lines of best fit, shown in \crefrange{fig:fitts-lo}{fig:fitts-hi}.
 
@@
   \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_med.png}
-  \caption{\emph{Med} setting. }
-  \label{fig:fitts-med}
+  \caption{\emph{Med} setting. }\label{fig:fitts-med}
 \end{figure}
@@
   \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_hi.png}
-  \caption{\emph{Hi} setting. }
-  \label{fig:fitts-hi}
+  \caption{\emph{Hi} setting. }\label{fig:fitts-hi}
 \end{figure}
@@
   \includegraphics[clip, trim=90 20 130 20, width=0.4\textwidth]{figures/fitts_performance.png}
-  \caption{Boxplots of the indices of performance.}
-  \label{fig:fitts-performance}
+  \caption{Boxplots of the indices of performance.}\label{fig:fitts-performance}
 \end{figure}
 
-From these figures we can see that the data are consistent with Fitts's Law where the logarithmic line of best fit very closely approximates the median values of the binned data for all three pitch gradient settings, with each settings giving Pearson scores of 0.95, 0.87 and 0.93 for the \emph{lo}, \emph{med} and \emph{hi} settings respectively ($p < 0.05$ for all settings).
+From these figures we can see that the data are consistent with Fitts's Law where the logarithmic line of best fit very closely approximates the median values of the binned data for all 3 pitch gradient settings, with each settings giving Pearson scores of 0.95, 0.87 and 0.93 for the \emph{lo}, \emph{med} and \emph{hi} settings respectively ($p < 0.05$ for all settings).
 This result enabled us to compute the index of performance, $IP$, given by Equation~\ref{eq:fitts-performance}, for all of the subjects.
 These results were used to plot \cref{fig:fitts-performance}, which shows that the \emph{lo} and \emph{med} configurations give similar results, but slightly different spreads, while the \emph{hi} gives a lower $IP$.
-The Friedman score for the three settings gives a $p$-value of 0.017, comfortably achieving statistical significance with a threshold of $\alpha=0.05$.
+The Friedman score for the 3 settings gives a $p$-value of 0.017, comfortably achieving statistical significance with a threshold of $\alpha=0.05$.
 The Wilcoxon test comparing the \emph{lo} and \emph{hi} settings achieves significance after applying a Bonferroni correction ($\alpha=0.016$), but the other comparisons do not achieve significance.
@@
 We also found that varying the pitch-gain gradient of our interface influences the accuracy of the system in the tilt dimension, as well as the time to target, without affecting the performance in the pan dimension.
-The steeper, \emph{hi}, pitch-gain was found to produce the best results in this respect.
+The steeper, $m_h$ and $m_m$ pitch-gains were found to produce the best results in this respect.
 Furthermore, we discovered a logarithmic relationship between the index of difficulty of a target and the time taken by a participant to find it, confirming that the results with our interface adhere to Fitts's Law.
-However, there is a compromise to be made between speed and accuracy, with the \emph{hi} pitch-gain gradient directing the user to the target in the longest time.
+However, there is a compromise to be made between speed and accuracy, with the $m_h$ pitch-gain gradient directing the user to the target in the longest time.
 

### 2019-05-14 article.tex
Cut out a bunch of sections with blind people and Fitts law stuff

@@
 	For this, wee conducted a set of experiments with blindfolded and visually impaired users and found that the varying pitch component gives an average error of approximately \SI{20}{\degree} when searching for a target; in line with previous results from other authors.
-	Furthermore, we are able to demonstrate that the audio interface adheres to Fitts's Law and used it as a metric to determine which pitch setting produces the optimal results.
-	We discovered a trade-off between the speed and accuracy in the pointing task, which are maximised when the tone's pitch is adjusted to a low and high rate of change respectively. 
+	%Furthermore, we are able to demonstrate that the audio interface adheres to Fitts's Law and used it as a metric to determine which pitch setting produces the optimal results.
+	%We discovered a trade-off between the speed and accuracy in the pointing task, which are maximised when the tone's pitch is adjusted to a low and high rate of change respectively. 
 \end{abstract}
@@
 A similar audio interface was successfully implemented and evaluated in~\cite{durette2008visuo}, but in this case we are providing guidance instructions for both pan and tilt dimensions and using a non-constant pitch.
-\todo{can maybe cut out Fitts stuff}\uline{It is also unclear whether popular metrics, such as Fitts's Law~\cite{fitts1954information}, can be applied in this case.
-Fitts's Law is a predictive model in the field of psychomotor research, often used in the human-machine interfacing field, that relates the time it takes a user to direct a pointing device toward a target as a function of the difficulty of finding the target (i.e.\ the ratio between the distance to the target and its size).
-If a Fitts relationship is found, it can be used as a metric to anticipate whether future adjustments to the pitch's rate of change will have a positive effect on target-search performance.}
+%\todo{can maybe cut out Fitts stuff}\uline{It is also unclear whether popular metrics, such as Fitts's Law~\cite{fitts1954information}, can be applied in this case.
+%Fitts's Law is a predictive model in the field of psychomotor research, often used in the human-machine interfacing field, that relates the time it takes a user to direct a pointing device toward a target as a function of the difficulty of finding the target (i.e.\ the ratio between the distance to the target and its size).
+%If a Fitts relationship is found, it can be used as a metric to anticipate whether future adjustments to the pitch's rate of change will have a positive effect on target-search performance.}
 
@@
 
-\todo{cut?}\uline{Researchers have previously used Fitts's Law~\cite{fitts1954information}, and more recently MacKenzie's modified version of it~\cite{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
-Fitts's Law was originally proposed for visual target search tasks.
-However, it has been applied in non-visual target search tasks as well.
-For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\cite{ahmaniemi2009augmented}.
-The authors showed that the search time adheres to Fitts's Law.
-However, they also note that it is not a perfect fit, citing the fact that Fitts's Law does not take into account a user's search strategy.
-Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\cite{marentakis2006effects}.
-Here, participants pointed to where they thought the targets were, on their left or right, as they traversed a path.
-Their results show a good relation between target difficulty and search time, providing a strong argument that Fitts's Law can be used to describe the performance of a spatial audio interface.
-These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\cite{wu2010fitts}.
-However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.}
+%\todo{cut?}\uline{Researchers have previously used Fitts's Law~\cite{fitts1954information}, and more recently MacKenzie's modified version of it~\cite{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
+%Fitts's Law was originally proposed for visual target search tasks.
+%However, it has been applied in non-visual target search tasks as well.
+%For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\cite{ahmaniemi2009augmented}.
+%The authors showed that the search time adheres to Fitts's Law.
+%However, they also note that it is not a perfect fit, citing the fact that Fitts's Law does not take into account a user's search strategy.
+%Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\cite{marentakis2006effects}.
+%Here, participants pointed to where they thought the targets were, on their left or right, as they traversed a path.
+%Their results show a good relation between target difficulty and search time, providing a strong argument that Fitts's Law can be used to describe the performance of a spatial audio interface.
+%These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\cite{wu2010fitts}.
+%However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.}
 
@@
 
-\todo{Needed?}We also compare the performance of the 3 pitch gradient settings in terms of the time it takes each participant to find a target.
-However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
-Instead, we use Fitts's Law~\cite{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\cite{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty (the ratio between the distance to the target and its width).
-It also provides a so-called `index of performance' that we can use as a metric to compare the results between the 3 configurations.
+%\todo{Needed?}We also compare the performance of the 3 pitch gradient settings in terms of the time it takes each participant to find a target.
+%However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
+%Instead, we use Fitts's Law~\cite{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\cite{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty (the ratio between the distance to the target and its width).
+%It also provides a so-called `index of performance' that we can use as a metric to compare the results between the 3 configurations.
 
-Here we briefly summarise the equations and quantities involved in our metric.
-Fitts's Law is given by
+%Here we briefly summarise the equations and quantities involved in our metric.
+%Fitts's Law is given by
 
-\begin{equation}
-  \label{eq:fitts-base}
-  t = a + bID,
-\end{equation}
+%\begin{equation}
+  %\label{eq:fitts-base}
+  %t = a + bID,
+%\end{equation}
 
-\noindent
-where $t$ is the time it takes to find a target, $a$ and $b$ are constants determined through regression and $ID$ is a description of the difficulty of the target, given as logarithmic function of the ratio between the distance to the target and the target's width.
-In our case, the targets have no width, since they are points in space, and we therefore use MacKenzie's modified form for $ID$, given by
+%\noindent
+%where $t$ is the time it takes to find a target, $a$ and $b$ are constants determined through regression and $ID$ is a description of the difficulty of the target, given as logarithmic function of the ratio between the distance to the target and the target's width.
+%In our case, the targets have no width, since they are points in space, and we therefore use MacKenzie's modified form for $ID$, given by
 
-\begin{equation}
-  \label{eq:fitts-id}
-  ID = \log_2\left(\frac{\theta}{w_e} + 1\right).
-\end{equation}
+%\begin{equation}
+  %\label{eq:fitts-id}
+  %ID = \log_2\left(\frac{\theta}{w_e} + 1\right).
+%\end{equation}
 
-\noindent
-Here $\theta$ is the angular distance between subsequent target centres and $w_e$ is the targets' effective angular width~\cite{welford1968fundamentals}, given by
+%\noindent
+%Here $\theta$ is the angular distance between subsequent target centres and $w_e$ is the targets' effective angular width~\cite{welford1968fundamentals}, given by
 
-\begin{equation}
-  \label{eq:fitts-we}
-  w_e = \sqrt{2\pi e}\sigma = 4.133\sigma,
-\end{equation}
+%\begin{equation}
+  %\label{eq:fitts-we}
+  %w_e = \sqrt{2\pi e}\sigma = 4.133\sigma,
+%\end{equation}
 
-\noindent
-where $\sigma$ is the standard deviation of the error data, taken as the angle between the participant's target selection and target's actual angular position.
-Fitts's index of performance, $IP$, can then be calculated using
+%\noindent
+%where $\sigma$ is the standard deviation of the error data, taken as the angle between the participant's target selection and target's actual angular position.
+%Fitts's index of performance, $IP$, can then be calculated using
 
-\begin{equation}
-  \label{eq:fitts-performance}
-  IP = \frac{ID}{t},
-\end{equation}
+%\begin{equation}
+  %\label{eq:fitts-performance}
+  %IP = \frac{ID}{t},
+%\end{equation}
 
-\noindent
-where $IP = \frac{1}{t}$ when $\sigma=0$.
+%\noindent
+%where $IP = \frac{1}{t}$ when $\sigma=0$.
 
@@
 
-The data collected from $G2$ follow a similar trend to that of $G1$: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all 3 settings.
-These results are summarised in Table~\ref{tab:vi-results}.
-Unfortunately, not enough samples could be collected to draw any final conclusions.
-However, these results are in line with results from previous work~\cite{zwiers2001spatial}, indicating that the groups with partial and normal eyesight respond with similar levels of accuracy to spatialised sound when presented with simple tasks.
-In addition, they also confirm that a participant's target search capability in the pan dimension is robust to the changing pitch for the target's tilt angle which is a useful result in support of the effectiveness of our audio interface.
+%The data collected from $G2$ follow a similar trend to that of $G1$: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all 3 settings.
+%These results are summarised in Table~\ref{tab:vi-results}.
+%Unfortunately, not enough samples could be collected to draw any final conclusions.
+%However, these results are in line with results from previous work~\cite{zwiers2001spatial}, indicating that the groups with partial and normal eyesight respond with similar levels of accuracy to spatialised sound when presented with simple tasks.
+%In addition, they also confirm that a participant's target search capability in the pan dimension is robust to the changing pitch for the target's tilt angle which is a useful result in support of the effectiveness of our audio interface.
 
-\begin{table}
-  \centering
-  \caption{A table summarising the target search results of the participants in $G2$ (P1 - P3).
+%\begin{table}
+  %\centering
+  %\caption{A table summarising the target search results of the participants in $G2$ (P1 - P3).
 The results include the average error ($\mu$) and standard deviation ($\sigma$), given in radians in the pan and tilt dimensions.}\label{tab:vi-results}
-  \begin{tabular}{llcccccc}
-    \toprule
-    \multicolumn{2}{c}{} & \multicolumn{2}{c}{$m_l$} & \multicolumn{2}{c}{$m_m$} & \multicolumn{2}{c}{$m_h$} \\
-    \multicolumn{2}{c}{} & $\mu_l$ & $\sigma_l$ & $\mu_m$ & $\sigma_m$ & $\mu_h$ & $\sigma_h$ \\\midrule
-         & P1 &  0.25 & 0.44 &  0.21 & 0.45 &  0.29 & 0.40 \\% \cline{2-8}
-    Pan  & P2 &  0.18 & 0.85 &  0.05 & 0.49 & -0.08 & 0.32 \\% \cline{2-8}
-         & P3 & -0.10 & 0.67 & -0.08 & 0.61 & -0.08 & 0.50 \\ \midrule
-         & P1 & -0.17 & 0.21 & -0.10 & 0.2  & -0.25 & 0.21 \\% \cline{2-8}
-    Tilt & P2 & -0.87 & 0.26 & -0.05 & 0.21 & -0.15 & 0.18 \\% \cline{2-8}
-         & P3 & -0.57 & 0.31 & -0.57 & 0.45 & -0.38 & 0.39 \\% \hline
-    \bottomrule
-  \end{tabular}
-\end{table}
+  %\begin{tabular}{llcccccc}
+    %\toprule
+    %\multicolumn{2}{c}{} & \multicolumn{2}{c}{$m_l$} & \multicolumn{2}{c}{$m_m$} & \multicolumn{2}{c}{$m_h$} \\
+    %\multicolumn{2}{c}{} & $\mu_l$ & $\sigma_l$ & $\mu_m$ & $\sigma_m$ & $\mu_h$ & $\sigma_h$ \\\midrule
+         %& P1 &  0.25 & 0.44 &  0.21 & 0.45 &  0.29 & 0.40 \\% \cline{2-8}
+    %Pan  & P2 &  0.18 & 0.85 &  0.05 & 0.49 & -0.08 & 0.32 \\% \cline{2-8}
+         %& P3 & -0.10 & 0.67 & -0.08 & 0.61 & -0.08 & 0.50 \\ \midrule
+         %& P1 & -0.17 & 0.21 & -0.10 & 0.2  & -0.25 & 0.21 \\% \cline{2-8}
+    %Tilt & P2 & -0.87 & 0.26 & -0.05 & 0.21 & -0.15 & 0.18 \\% \cline{2-8}
+         %& P3 & -0.57 & 0.31 & -0.57 & 0.45 & -0.38 & 0.39 \\% \hline
+    %\bottomrule
+  %\end{tabular}
+%\end{table}
 
@@
 
-Given the small sample size in $G2$, there is limited meaningful statistical analysis we can do on the data collected from the participants with visual impairments.
-However, it could be seen from the results in \cref{tab:vi-results} that these participants displayed the same behaviour in our experiments with a clear bias toward the lower angles (i.e.\ the floor) and not-insignificant variability between the 3 settings.
-%Similarly, the pan dimension remains more stable throughout the 3 settings.
-The participants also confirmed that they preferred the increased response rate of the \emph{hi} setting, reporting that it gave them a clearer idea of the direction they needed to point to.
+%Given the small sample size in $G2$, there is limited meaningful statistical analysis we can do on the data collected from the participants with visual impairments.
+%However, it could be seen from the results in \cref{tab:vi-results} that these participants displayed the same behaviour in our experiments with a clear bias toward the lower angles (i.e.\ the floor) and not-insignificant variability between the 3 settings.
+%The participants also confirmed that they preferred the increased response rate of the \emph{hi} setting, reporting that it gave them a clearer idea of the direction they needed to point to.
 
@@
 
-\subsection{Time to Target}
+%\subsection{Time to Target}
 
-\crefrange{fig:fitts-lo}{fig:fitts-hi} shows the box-plots of the target-search time as a function of the \emph{ID} of the targets.
-Here, the bin interval is the smallest effective width, calculated from \cref{eq:fitts-performance}, between the 3 gradient settings.
-We used the relation from \cref{eq:fitts-base} and fitted a logarithmic regression line for each participant.
-The medians of the $a$ and $b$ parameters, from \cref{eq:fitts-base}, for all the subjects' regressions were used to plot the resulting lines of best fit, shown in \crefrange{fig:fitts-lo}{fig:fitts-hi}.
+%\crefrange{fig:fitts-lo}{fig:fitts-hi} shows the box-plots of the target-search time as a function of the \emph{ID} of the targets.
+%Here, the bin interval is the smallest effective width, calculated from \cref{eq:fitts-performance}, between the 3 gradient settings.
+%We used the relation from \cref{eq:fitts-base} and fitted a logarithmic regression line for each participant.
+%The medians of the $a$ and $b$ parameters, from \cref{eq:fitts-base}, for all the subjects' regressions were used to plot the resulting lines of best fit, shown in \crefrange{fig:fitts-lo}{fig:fitts-hi}.
 
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_lo.png}
-  \caption{\emph{Lo} setting. }\label{fig:fitts-lo}
-\end{figure}
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_lo.png}
+  %\caption{\emph{Lo} setting. }\label{fig:fitts-lo}
+%\end{figure}
 
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_med.png}
-  \caption{\emph{Med} setting. }\label{fig:fitts-med}
-\end{figure}
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_med.png}
+  %\caption{\emph{Med} setting. }\label{fig:fitts-med}
+%\end{figure}
 
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_hi.png}
-  \caption{\emph{Hi} setting. }\label{fig:fitts-hi}
-\end{figure}
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_hi.png}
+  %\caption{\emph{Hi} setting. }\label{fig:fitts-hi}
+%\end{figure}
 
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=90 20 130 20, width=0.4\textwidth]{figures/fitts_performance.png}
-  \caption{Boxplots of the indices of performance.}\label{fig:fitts-performance}
-\end{figure}
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=90 20 130 20, width=0.4\textwidth]{figures/fitts_performance.png}
+  %\caption{Boxplots of the indices of performance.}\label{fig:fitts-performance}
+%\end{figure}
 
-From these figures we can see that the data are consistent with Fitts's Law where the logarithmic line of best fit very closely approximates the median values of the binned data for all 3 pitch gradient settings, with each settings giving Pearson scores of 0.95, 0.87 and 0.93 for the \emph{lo}, \emph{med} and \emph{hi} settings respectively ($p < 0.05$ for all settings).
-This result enabled us to compute the index of performance, $IP$, given by Equation~\ref{eq:fitts-performance}, for all of the subjects.
-These results were used to plot \cref{fig:fitts-performance}, which shows that the \emph{lo} and \emph{med} configurations give similar results, but slightly different spreads, while the \emph{hi} gives a lower $IP$.
-The Friedman score for the 3 settings gives a $p$-value of 0.017, comfortably achieving statistical significance with a threshold of $\alpha=0.05$.
-The Wilcoxon test comparing the \emph{lo} and \emph{hi} settings achieves significance after applying a Bonferroni correction ($\alpha=0.016$), but the other comparisons do not achieve significance.
+%From these figures we can see that the data are consistent with Fitts's Law where the logarithmic line of best fit very closely approximates the median values of the binned data for all 3 pitch gradient settings, with each settings giving Pearson scores of 0.95, 0.87 and 0.93 for the \emph{lo}, \emph{med} and \emph{hi} settings respectively ($p < 0.05$ for all settings).
+%This result enabled us to compute the index of performance, $IP$, given by Equation~\ref{eq:fitts-performance}, for all of the subjects.
+%These results were used to plot \cref{fig:fitts-performance}, which shows that the \emph{lo} and \emph{med} configurations give similar results, but slightly different spreads, while the \emph{hi} gives a lower $IP$.
+%The Friedman score for the 3 settings gives a $p$-value of 0.017, comfortably achieving statistical significance with a threshold of $\alpha=0.05$.
+%The Wilcoxon test comparing the \emph{lo} and \emph{hi} settings achieves significance after applying a Bonferroni correction ($\alpha=0.016$), but the other comparisons do not achieve significance.
 
-A possible explanation for the observed behaviour is that the more distinguishable changes in the audio pitch with the \emph{hi} configuration better informs the user when they are on target, leading to a more accurate estimate, but also increases the time it takes to point in the right direction.
-Conversely, the \emph{lo} and \emph{med} gradients make it more difficult for the user to know when they are on target, leading to a shorter search time, but at the cost of lower accuracy.
-This is confirmed by the results obtained in Section~\ref{sec:tilt-results} and the Wilcoxon test results.
+%A possible explanation for the observed behaviour is that the more distinguishable changes in the audio pitch with the \emph{hi} configuration better informs the user when they are on target, leading to a more accurate estimate, but also increases the time it takes to point in the right direction.
+%Conversely, the \emph{lo} and \emph{med} gradients make it more difficult for the user to know when they are on target, leading to a shorter search time, but at the cost of lower accuracy.
+%This is confirmed by the results obtained in Section~\ref{sec:tilt-results} and the Wilcoxon test results.
 
-The results collected from the participants with partial eyesight follow the same trends observed in the blindfolded participants, giving $IPs$ of 0.58, 1.3 and 0.35 for the \emph{lo}, \emph{med} and \emph{hi} gradient settings respectively.
+%The results collected from the participants with partial eyesight follow the same trends observed in the blindfolded participants, giving $IPs$ of 0.58, 1.3 and 0.35 for the \emph{lo}, \emph{med} and \emph{hi} gradient settings respectively.
 
-\subsection{Participant with Visual Impairments' Feedback}
+%\subsection{Participant with Visual Impairments' Feedback}
 
-After and during the experiments involving the participants with visual impairments, we had the opportunity to collect their feedback on the current system implementation and suggestions for future improvements.
+%After and during the experiments involving the participants with visual impairments, we had the opportunity to collect their feedback on the current system implementation and suggestions for future improvements.
 
-In general, they were satisfied with the current implementation and had little difficulty using it.
-Furthermore, the prohibitive cost, complexity and cumbersomeness of other existing systems discouraged our subjects from purchasing and using them, so they were quite enthusiastic about our goal of developing a mobile or tablet-based indoor navigation system.
+%In general, they were satisfied with the current implementation and had little difficulty using it.
+%Furthermore, the prohibitive cost, complexity and cumbersomeness of other existing systems discouraged our subjects from purchasing and using them, so they were quite enthusiastic about our goal of developing a mobile or tablet-based indoor navigation system.
 
-One aspect of the audio interface that requires improvement is the tone used during the experiments was not very pleasant and led to auditory fatigue after a long period of use.
-We are aware of this issue and we are already investigating more natural, `pleasant' and rich sounds to replace the basic sinusoidal wave that was used in the experiments.
-One possibility is to use musical instruments (e.g.\ MIDI sound files) to play notes and scales~\cite{brewster1998using}.
+%One aspect of the audio interface that requires improvement is the tone used during the experiments was not very pleasant and led to auditory fatigue after a long period of use.
+%We are aware of this issue and we are already investigating more natural, `pleasant' and rich sounds to replace the basic sinusoidal wave that was used in the experiments.
+%One possibility is to use musical instruments (e.g.\ MIDI sound files) to play notes and scales~\cite{brewster1998using}.
 
-Concerning the bone-conducting headsets, only one participant had reservations about this choice, citing cost concerns.
-None of the participants had any technical issues in using the headset or misunderstanding audio cues.
-They all agreed that this is a valid choice to avoid cutting a person with visual impairments off from environmental sounds.
-Furthermore, they suggested to add some voice component to the system to inform the user of important events (e.g.
+%Concerning the bone-conducting headsets, only one participant had reservations about this choice, citing cost concerns.
+%None of the participants had any technical issues in using the headset or misunderstanding audio cues.
+%They all agreed that this is a valid choice to avoid cutting a person with visual impairments off from environmental sounds.
+%Furthermore, they suggested to add some voice component to the system to inform the user of important events (e.g.
 \emph{`Target has been found'}, \emph{`You are veering off course'}, etc.) or to simply confirm and reassure the user that they are still on course.

### 2019-05-14 article.tex
Cut out a bunch of sections with blind people and Fitts law stuff

@@
 
-The main contributions of this paper are two-fold:
+This work contributes by providing the first experimental results on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with bone-conducting headsets.
 
-\begin{itemize}
-  \item we provide the first experimental results on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with bone-conducting headsets; 
-  \item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
-\end{itemize}
+%The main contributions of this paper are two-fold: 
+%\begin{itemize}
+  %\item we provide the first experimental results on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with bone-conducting headsets; 
+  %\item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
+%\end{itemize}
 

### 2019-05-14 article.tex
Redid intro, re-added blind tests

--- 2019-05-14 article.tex
@@
 
-\title{An Audio Interface for an Active Perception Navigation Aid for Blind People}
+\title{Audio Interface of an Active Perception Navigation Aid for People with Visual Impairments}
 
@@
 	The goal is to determine how changes to the rate of change of the pitch affects a user's performance.
-	For this, wee conducted a set of experiments with blindfolded and visually impaired users and found that the varying pitch component gives an average error of approximately \SI{20}{\degree} when searching for a target; in line with previous results from other authors.
-	Furthermore, we are able to demonstrate that the audio interface adheres to Fitts's Law and used it as a metric to determine which pitch setting produces the optimal results.
-	We discovered a trade-off between the speed and accuracy in the pointing task, which are maximised when the tone's pitch is adjusted to a low and high rate of change respectively. 
+	For this, we conducted a set of experiments with blindfolded and visually impaired users and found that the varying pitch component gives an average error of approximately \SI{20}{\degree} when searching for a target; in line with previous results from other authors.
 \end{abstract}
@@
 
-\keywords{Human-machine interface, vision impairment, spatialised sound, Fitts's Law, pointing task}
+\keywords{Human-machine interface, vision impairment, spatialised sound, varying pitch, pointing task}
 
@@
 A Tango-enabled device comes pre-equipped with powerful image-processing, localisation and depth-perception capabilities and is built on top of a standard Android platform, providing access to the entire set of input/output options that this operating system has to offer.
-The final system will use multiple feedback modes (vibration, audio and voice) to guide a user toward a target destination while providing information on any oncoming obstacles.
+%The final system will use multiple feedback modes (vibration, audio and voice) to guide a user toward a target destination while providing information on any oncoming obstacles.
 
@@
 
-In this paper we focus on the audio feedback mode and discuss how it is used in our system.
-We present experiments we performed to determine its effectiveness at directing a user to complete a pointing task and how its parameters affect users' target-search performance.
-For the pointing task, we presented blindfolded and partially sighted participants with a set of virtual targets, one after another, and asked them to point a camera to where they thought the targets were.
-The targets' pan and tilt angles w.r.t.\ the device's vertical plane, shown in \cref{fig:cam-coords}, were given to the participants through a spatial tone with varying pitch played via a set of bone-conducting headphones.
-We use the latter to not interfere with the user's normal hearing function, which people with visual impairments typically rely on.
-Because these headphones bypass the external structure of the ear responsible for localising a sound source's elevation, it is necessary to convey the target's tilt angle using another method.
-Therefore, we opted for a tone with varying pitch to convey the angle adjustment required to point the camera in a particular direction.
-A similar audio interface was successfully implemented and evaluated in~\cite{durette2008visuo}, but in this case we are providing guidance instructions for both pan and tilt dimensions and using a non-constant pitch.
-\todo{can maybe cut out Fitts stuff}\uline{It is also unclear whether popular metrics, such as Fitts's Law~\cite{fitts1954information}, can be applied in this case.
-Fitts's Law is a predictive model in the field of psychomotor research, often used in the human-machine interfacing field, that relates the time it takes a user to direct a pointing device toward a target as a function of the difficulty of finding the target (i.e.\ the ratio between the distance to the target and its size).
-If a Fitts relationship is found, it can be used as a metric to anticipate whether future adjustments to the pitch's rate of change will have a positive effect on target-search performance.}
+For this work, we implemented and evaluate an audio guidance mode that will be implemented in the guidance system to provide navigation instructions to the user. 
+To evaluate this guidance mode, we conducted a set of experiments involving a target-search task where the participants were guided to point a camera to a set of virtual targets with the audio instructions.
+The system uses a set of bone-conducting headphones to provide the audio instructions, with the latter being used to avoid interfering with a user's normal hearing function; something people with limited vision typically rely upon.
+However, this type of headphones bypass the external structure of the ear which provide the ability to localise a sound source's elevation.
+We therefore use a tone of varying pitch to convey the target's tilt position w.r.t.\ the camera's pointing vector, $C$, pictured in \cref{fig:cam-coords}.
+The tone is spatialised to provide the target's position in the pan dimension.
+A similar interface can be found in~\cite{durette2008visuo}, where they used a varying pitch component without spatialising the tone. 
+However, they did not investigate this interface's target-finding accuracy.
+Furthermore, we wish to determine how changing the pitch's rate of change will affect target-finding performance. 
+Therefore, this work contributes by determining how accurately a spatialised tone with varying pitch can direct a user towards a target, and how the pitch's rate of change affects this accuracy.
+
+%In this paper we focus on the audio feedback mode and discuss how it is used in our system.
+%We present experiments we performed to determine its effectiveness at directing a user to complete a pointing task and how its parameters affect users' target-search performance.
+%For the pointing task, we presented blindfolded and partially sighted participants with a set of virtual targets, one after another, and asked them to point a camera to where they thought the targets were.
+%The targets' pan and tilt angles w.r.t.\ the device's vertical plane, shown in \cref{fig:cam-coords}, were given to the participants through a spatial tone with varying pitch played via a set of bone-conducting headphones.
+%We use the latter to not interfere with the user's normal hearing function, which people with visual impairments typically rely on.
+%Because these headphones bypass the external structure of the ear responsible for localising a sound source's elevation, it is necessary to convey the target's tilt angle using another method.
+%Therefore, we opted for a tone with varying pitch to convey the angle adjustment required to point the camera in a particular direction.
+%A similar audio interface was successfully implemented and evaluated in~\cite{durette2008visuo}, but in this case we are providing guidance instructions for both pan and tilt dimensions and using a non-constant pitch.
+%This work contributes by providing the first experimental results on how well a tone with varying pitches and rates of change can convey a target's tilt angle when using a mobile device with bone-conducting headsets.
 
@@
 
-The main contributions of this paper are two-fold:
-
-\begin{itemize}
-  \item we provide the first experimental results on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with bone-conducting headsets; 
-  \item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
-\end{itemize}
-
 The remainder of this paper is organised as follows: \cref{sec:lit-review} gives an overview of existing navigation systems and audio interfaces for people living with visual impairments.
 \cref{sec:portable-navigation} discusses the navigation device's hardware and interface setup and describes how the target's position is conveyed to the user.
-The experiments that were conducted are explained in \cref{sec:experiments} and the results are presented and discussed in \cref{sec:results}. 
+The experiment we conducted are explained in \cref{sec:experiments} and the results are presented and discussed in \cref{sec:results}. 
 Finally, \cref{sec:conclusion} concludes this paper with a summary of the findings and comments on our future work.
@@
 Attempting to deliver a system that allows people with visual impairments to independently navigate and accomplish everyday tasks is not new; in fact, there are multiple commercial systems and research prototypes already available on the market.
-One approach that has been investigated is to outfit the existing white walking cane with various sensors,
-such as sonar, radar, motor encoders, etc.~\cite{ulrich1997, marion2008batcane} to warn the user of upcoming obstacles, instead of relying on haptic feedback from the impact between the cane and the obstacle.
+One approach that has been investigated is to outfit the existing white walking cane with various sensors, such as sonar, radar, motor encoders, etc.~\cite{ulrich1997, marion2008batcane} to warn the user of upcoming obstacles, instead of relying on haptic feedback from the impact between the cane and the obstacle.
 Another approach is to outfit a walking cane to act as a radio-frequency identification (RFID) antenna that can read a set of RFID tags placed at strategic locations around the environment at key spots or along a path~\cite{faria2010electronic, willis2005}.
@@
 Other authors found that the minimum difference in the spatial sound's angle for the user to be able to perceive movement is approximately \SI{1.7}{\degree}. 
-During the experiments, an audio speaker was physically manoeuvred to provide the participant with a spatialised sound tone~\cite{ashmead1998spatial}.
+During these experiments, an audio speaker was physically manoeuvred to provide the participant with a spatialised sound tone~\cite{ashmead1998spatial}.
 Researchers have also tried using simulated spatial audio to inform the user from which direction a sound is originating~\cite{holland2002audiogps, kammoun2012navigation, rebillat2009smart, menelas2010audio, wilson2007swan, zotkin2004rendering}.
@@
 There are also experimental results about how well users can find targets presented with spatial sound in the tilt and panning dimensions with normal headphones~\cite{katz2011spatial, zwiers2001spatial}, as well as work that has shown similar levels of localisation performance between normal and bone-conducting headphones in the pan dimension~\cite{macdonald2006spatial}.
-However, to our knowledge no extensive work or experiments have been done to determine how well users respond to tilt adjustment instructions using a tone with \emph{varying pitch}, in particular when using bone-conducting headphones.
-
-\todo{cut?}\uline{Researchers have previously used Fitts's Law~\cite{fitts1954information}, and more recently MacKenzie's modified version of it~\cite{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
-Fitts's Law was originally proposed for visual target search tasks.
-However, it has been applied in non-visual target search tasks as well.
-For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\cite{ahmaniemi2009augmented}.
-The authors showed that the search time adheres to Fitts's Law.
-However, they also note that it is not a perfect fit, citing the fact that Fitts's Law does not take into account a user's search strategy.
-Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\cite{marentakis2006effects}.
-Here, participants pointed to where they thought the targets were, on their left or right, as they traversed a path.
-Their results show a good relation between target difficulty and search time, providing a strong argument that Fitts's Law can be used to describe the performance of a spatial audio interface.
-These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\cite{wu2010fitts}.
-However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.}
+However, to our knowledge no extensive work or experiments have been done to determine how well users respond to tilt adjustment instructions using a tone with \emph{varying pitch}, in particular when using bone-conducting headphones, and how changes to this tone's behaviour affects performance.
 
@@
 A large amount of data need to be translated from a visual form into a format that is useful to people with limited or no vision.
-%To do this, we will use a combination of different feedback modes to facilitate two-way communication between the user and the device.
 We therefore plan to use a combination of voice, audio and vibration cues to translate visual navigation data as effectively as possible and overcome the bandwidth limitation of the human ear.
@@
 
-\todo{Needed?}A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}.
+A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}.
 Here, the arrows indicate the direction of the flow of information.
@@
 Humans determine a sound source's pan direction by subconsciously analysing the inter-aural time difference (IID) between a sound reaching both of your ears: the greater the IID, the greater the perceived angular distance to the sound source~\cite{wightman1992dominant}.
-%For example, if you hear a sound in your left ear first, you interpret the sound as coming from your left.
 
@@
 We performed a set of experiments with our audio interface to determine its effectiveness at directing a user to adjust a camera's $\phi$ and $\theta$ to point it to a target.
-%Furthermore, we also carried out a set of pre-screening experiments to determine each participant's hearing characteristics.
 The results from the experiments allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimise the behaviour of the feedback modes in our portable navigation aid.
@@
 
-\subsection{Experimental Procedure}
-
 For the experiments we used two groups of participants, with one ($G1$) including 42 sighted and blindfolded participants and the other ($G2$) 3 legally blind volunteers with varying degrees of vision impairment.
@@
 
-%The participants participated in three experiments.
-%The first two experiments were performed to determine each participant's hearing characteristics and provide some context to the results generated during the target-search experiment.
-%These characterisation experiments will also indicate pre-existing biases our participant-base might have in the modes or dimensions we performed our third experiment on: the target search.
-
-%\begin{figure}
-  %\centering
-  %\begin{subfigure}[t]{0.45\textwidth}
-    %\centering
-    %\includegraphics[width=0.5\textwidth]{figures/sighted_participant.png}
-    %\caption{A sighted and blindfolded participant. }
-  %\end{subfigure}\hfill
-  %\begin{subfigure}[t]{0.45\textwidth}
-    %\centering
-    %\includegraphics[width=0.5\textwidth]{figures/vi_participant2.jpg}
-    %\caption{A visually impaired participant. }
-  %\end{subfigure}
-  %\caption{Participants in the study using the Tango device during the target-search task. }
-  %\label{fig:participants}
-%\end{figure}
-
 We are only evaluating the interface in the pan and tilt dimensions and the 3D targets are therefore generated at a constant distance of \SI{2}{\metre} from the participant.
 Throughout the experiments, various parameters of the targets and participants were recorded and streamed in real-time to a laptop computer via a WiFi connection.
-%Prior to the target search experiment, the blindfolded participant group was given a few minutes without a blindfold to familiarise themselves with the system and confirm the target's location with their own eyes.
-%This was done verbally with the participants with limited vision.
-
-%\subsection{Participant Characterisation}
-
-%\subsubsection{Spatial Awareness}
-
-%In this experiment, we evaluated a participant's ability to determine the lateral direction a sound is coming from.
-%To do this, we played a continuous \SI{512}{\hertz} sinusoidal tone to the participant through the headphones and applied an HRTF to spatialise and place its source to the participant's left or right.
-%The participant then had to select the direction the sound came from.
-%The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly difficult to localise.
-
-%For this progressive increase in difficulty, a 2-up, 1-down step process is used~\cite{wetherill1965sequential,levitt1971transformed}, meaning that for every 2 correct answers, the distance to the centre halves, making the lateral direction harder to determine.
-%Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre.
-%We also use 2 different step sequences, one starting at a large distance (\SI{45}{\degree}) from the user and the other at the minimum distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' step respectively.
-%The terminating condition for the experiment is when the 2 step sequences converge to within 2 step ranges of one another for 3 consecutive guesses.
-%This gives a distance band within which the participant is capable of localising the sound source. Each participant performed this experiment three times.
-
-%\subsubsection{Pitch Discrimination}
-
-%Here we determined a participant's ability to differentiate pitch, i.e.\ how well they can tell if a tone is high or low pitched.
-%We played 2 tones to the participants in succession with the second tone being higher or lower-pitched than the first.
-%The participants were then asked to select whether they interpreted the second tone as higher or lower-pitched than the first.
-
-%The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first one.
-%The tone difference depends on how well the participant can tell the tones apart.
-%Like the spatial awareness experiment, a 2-up, 1-down step process is used: for every 2 consecutive correct answers, the pitch difference between the tones is halved, and the difference is doubled for every incorrect answer.
-%Two step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
-%The termination condition is when the two step sequences are within one octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2^1$) for 3 consecutive answers.
-%Each participant performed this experiment twice.
-
-%\subsection{Target Search}
-
-\subsection{Task Description}
-
-%The final experiment is the main one and will answer the question we are most interested in: how well does a spatial tone with varying pitch direct a user to look in a specific direction and how do the parameters of this tone affect the user's performance in this task?
 
@@
 Then, depending on the direction the participant was currently pointing the camera relative to the target's position, the Tango generated and played a tone via the bone-conducting headphones to indicate the pan and tilt angle adjustment required to point the camera to the target.
-%These instructions are spatialised tones with varying pitch: an HRTF indicates the pan direction (left or right) and the pitch indicates whether the participant should be looking up (high pitch) or down (low pitch) to find the target.
 
@@
 
-\subsection{Metrics}
-
-We use two different metrics to compare the 3 different pitch gradient settings: the acquisition accuracy and search time.
+In this case, the system's measure of performance is given by the target acquisition accuracy.
 The accuracy is given as the difference between the device's orientation at the time the participant confirmed they were on target, and the target's actual angular position.
@@
 
-\todo{Needed?}We also compare the performance of the 3 pitch gradient settings in terms of the time it takes each participant to find a target.
-However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
-Instead, we use Fitts's Law~\cite{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\cite{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty (the ratio between the distance to the target and its width).
-It also provides a so-called `index of performance' that we can use as a metric to compare the results between the 3 configurations.
+\section{Experiment Results and Discussion}\label{sec:results}
 
-Here we briefly summarise the equations and quantities involved in our metric.
-Fitts's Law is given by
-
-\begin{equation}
-  \label{eq:fitts-base}
-  t = a + bID,
-\end{equation}
-
-\noindent
-where $t$ is the time it takes to find a target, $a$ and $b$ are constants determined through regression and $ID$ is a description of the difficulty of the target, given as logarithmic function of the ratio between the distance to the target and the target's width.
-In our case, the targets have no width, since they are points in space, and we therefore use MacKenzie's modified form for $ID$, given by
-
-\begin{equation}
-  \label{eq:fitts-id}
-  ID = \log_2\left(\frac{\theta}{w_e} + 1\right).
-\end{equation}
-
-\noindent
-Here $\theta$ is the angular distance between subsequent target centres and $w_e$ is the targets' effective angular width~\cite{welford1968fundamentals}, given by
-
-\begin{equation}
-  \label{eq:fitts-we}
-  w_e = \sqrt{2\pi e}\sigma = 4.133\sigma,
-\end{equation}
-
-\noindent
-where $\sigma$ is the standard deviation of the error data, taken as the angle between the participant's target selection and target's actual angular position.
-Fitts's index of performance, $IP$, can then be calculated using
-
-\begin{equation}
-  \label{eq:fitts-performance}
-  IP = \frac{ID}{t},
-\end{equation}
-
-\noindent
-where $IP = \frac{1}{t}$ when $\sigma=0$.
-
-\section{Experiment Results and Discussion}
-\label{sec:results}
-
-%\subsection{Participant Characterisation}
-%\label{sec:character}
-
-%\cref{fig:location-guesses} shows the results for the spatial awareness experiment in the pan direction where the participants had to determine the location of the sound they were played.
-
-%\begin{figure}
-  %\centering
-  %\includegraphics[clip, trim=100 20 150 100, width=0.4\textwidth]{figures/location_guesses.png}
-  %\caption{Histograms of the spatial awareness experiment in the pan dimension showing the proportion of correct/incorrect guesses per bin interval. }
-  %\label{fig:location-guesses}
-%\end{figure}
-
-%With the relatively low number of erroneous guesses, we see that the participants were accurate in guessing the location of the sound source.
-%This is further supported by the large number of samples at the minimum difference of \textasciitilde\SI{3}{\cm}, indicating that the participants reached this level more frequently and consistently.
-%We can therefore conclude that the participants had little difficulty determining the pan angle of a sound source.
-%These results are in line with what we expected and they are supported by literature which indicates that humans are very adept at localising a sound source, and this ability was apparent for the HRTF-generated pan locations.
-
-%The results recorded during the pitch discrimination experiment are shown in \cref{fig:tone-guesses}, where a bar plot is used to show the number of correct guesses for each tone difference level.
-%The latter is given in terms of the relative semitone difference between the tones which are obtained using the following relation:
-
-%\begin{equation}
-%\label{eq:semitone-difference}
-  %\Delta f = 12\log_2\frac{f_0}{f_1}.
-%\end{equation}
-
-%From \cref{fig:tone-guesses}, we can see that the guesses are normally spread around a 0 semitone difference.
-%As expected, a larger proportion of incorrect guesses occur around the smaller differences with the majority of samples for correct and incorrect guesses being recorded in the $[-0.25, 0.25]$ semitone difference level.
-%Assuming these differences are normally distributed, we fitted a cumulative distribution function (CDF) over each participant's set of results for their correct guesses and used the CDF's parameters to determine the semitone difference threshold, where the participant could no longer reliably tell two tones apart, for each participant.
-%See \cref{fig:cdf-semitone} for an example showing the actual CDF of a participant and its approximated normal CDF\@.
-%We set this threshold at 75\% of the correct guesses, since this represents a significant majority of samples.
-%We found that the median threshold is approximately 0.43 semitones for the sighted participants in a range of [$9.2\times10^-4$, 3.12] semitones.
-%We use the median given the skewness of the distribution.
-%The plot showing the participants' threshold distribution can be seen in \cref{fig:tone-threshold}.
-
-%\begin{figure}
-  %\centering
-  %\includegraphics[clip, trim=80 0 150 100, width=0.4\textwidth]{figures/tone_guesses.png}
-  %\caption{Results of the tone limit experiment. }
-  %\label{fig:tone-guesses}
-%\end{figure}
-
-%\begin{figure}
-  %\centering
-  %\includegraphics[clip, trim=120 0 120 70, width=0.4\textwidth]{figures/cdf_tone_guesses.png}
-  %\caption{Cumulative distribution of the number of correct guesses for one participant. }
-  %\label{fig:cdf-semitone}
-%\end{figure}
-
-%\begin{figure}
-  %\centering
-  %\includegraphics[clip, trim=80 20 120 0, width=0.4\textwidth]{figures/tone_threshold.png}
-  %\caption{A distribution of the 75\% cut-off frequencies. }
-  %\label{fig:tone-threshold}
-%\end{figure}
-%\begin{figure}
-  %\centering
-  %\includegraphics[clip, trim=80 20 120 0, width=0.4\textwidth]{figures/tone_medians.png}
-  %\caption{A distribution of the median cut-off frequency thresholds along with the median 75\% cut-off threshold. }
-  %\label{fig:tone-medians}
-%\end{figure}
-
-%\subsection{Target Search}
-
-\subsection{Panning Results}
+\subsection{Pan Results}
 
@@
 A set of box-plots of the pan errors' median and standard deviations are also given in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} for each of the $m_l, m_m$ and $m_h$ setting. 
-The results are summarised in Table~\ref{tab:results}.
+The results are summarised in \cref{tab:results}.
 
@@
   \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_lo.png}
-  %\includegraphics[width=1.0\columnwidth]{figures/err_lo.png}
   \caption{Angular error data for $G1$ and the $m_l$ setting. }\label{fig:err-results-lo}
@@
   \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_med.png}
-  %\includegraphics[width=1.0\columnwidth]{figures/err_med.png}
   \caption{Angular error data for $G1$ and the $m_m$ setting. }\label{fig:err-results-med}
@@
   \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_hi.png}
-  %\includegraphics[width=1.0\columnwidth]{figures/err_hi.png}
   \caption{Angular error data for $G1$ and the $m_h$ setting. }\label{fig:err-results-hi}
@@
 The data collected from $G2$ follow a similar trend to that of $G1$: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all 3 settings.
-These results are summarised in Table~\ref{tab:vi-results}.
+These results are summarised in \cref{tab:vi-results}.
 Unfortunately, not enough samples could be collected to draw any final conclusions.
@@
 
-%Based on previous research~\cite{zwiers2001spatial}, these results were somewhat expected.
-
 \subsection{Tilt Results}\label{sec:tilt-results}
@@
 This indicates there is an inflection point where increasing $\frac{df}{d\theta}$ produces diminishing returns.
-%This is supported by the earlier observations made on the average and standard deviations of the error data which indicate that the $m_l$ setting gives the highest average errors, while $m_m$ and $m_h$ produce similar error levels.
 
@@
 Future improvements to our audio interface should consider a non-linear increase in pitch as a function of tilt angle instead of the linear one we used in this work to remedy this bias.
-%\cref{fig:tone-threshold} shows the distribution of the cut-off frequency thresholds that were found in Section~\ref{sec:character}, as well as a plot of the median values of the errors in the tilt dimension, transformed to a frequency using each dataset's respective pitch-gain gradient.
-
-%In particular, \cref{fig:tone-medians} indicates that the participants, on average, searched for the target until they could no longer detect a difference between the tone they were played and the \SI{512}{\hertz} on-target tone they were searching for.
-%This is shown by the vast majority of the error data being located below the 75\% cut-off threshold frequency of \SI{12.9}{\hertz} (0.43 semitones around \SI{512}{\hertz}).
-%Furthermore, it can be seen that the \emph{hi} dataset comes the closest to the cut-off frequency.
-%This could explain why it produces the strongest correlation between the targets' true perceived position, since the \emph{hi} pitch gradient is the most sensitive to changes in the tilt angle, it allowed the participants to get closer to the true tilt by playing a more easily distinguishable tone.
-
-Given the small sample size in $G2$, there is limited meaningful statistical analysis we can do on the data collected from the participants with visual impairments.
-However, it could be seen from the results in \cref{tab:vi-results} that these participants displayed the same behaviour in our experiments with a clear bias toward the lower angles (i.e.\ the floor) and not-insignificant variability between the 3 settings.
-%Similarly, the pan dimension remains more stable throughout the 3 settings.
-The participants also confirmed that they preferred the increased response rate of the \emph{hi} setting, reporting that it gave them a clearer idea of the direction they needed to point to.
 
@@
 They also highlight a clear and significant difference between the 3 different pitch gain gradients, with the $m_l$ setting giving the lowest acquisition accuracy, while $m_m$ and $m_h$ give similar accuracy levels closest to the true tilt.
-
-\subsection{Time to Target}
-
-\crefrange{fig:fitts-lo}{fig:fitts-hi} shows the box-plots of the target-search time as a function of the \emph{ID} of the targets.
-Here, the bin interval is the smallest effective width, calculated from \cref{eq:fitts-performance}, between the 3 gradient settings.
-We used the relation from \cref{eq:fitts-base} and fitted a logarithmic regression line for each participant.
-The medians of the $a$ and $b$ parameters, from \cref{eq:fitts-base}, for all the subjects' regressions were used to plot the resulting lines of best fit, shown in \crefrange{fig:fitts-lo}{fig:fitts-hi}.
-
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_lo.png}
-  \caption{\emph{Lo} setting. }\label{fig:fitts-lo}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_med.png}
-  \caption{\emph{Med} setting. }\label{fig:fitts-med}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=120 20 120 20, width=0.4\textwidth]{figures/fitts_hi.png}
-  \caption{\emph{Hi} setting. }\label{fig:fitts-hi}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=90 20 130 20, width=0.4\textwidth]{figures/fitts_performance.png}
-  \caption{Boxplots of the indices of performance.}\label{fig:fitts-performance}
-\end{figure}
-
-From these figures we can see that the data are consistent with Fitts's Law where the logarithmic line of best fit very closely approximates the median values of the binned data for all 3 pitch gradient settings, with each settings giving Pearson scores of 0.95, 0.87 and 0.93 for the \emph{lo}, \emph{med} and \emph{hi} settings respectively ($p < 0.05$ for all settings).
-This result enabled us to compute the index of performance, $IP$, given by Equation~\ref{eq:fitts-performance}, for all of the subjects.
-These results were used to plot \cref{fig:fitts-performance}, which shows that the \emph{lo} and \emph{med} configurations give similar results, but slightly different spreads, while the \emph{hi} gives a lower $IP$.
-The Friedman score for the 3 settings gives a $p$-value of 0.017, comfortably achieving statistical significance with a threshold of $\alpha=0.05$.
-The Wilcoxon test comparing the \emph{lo} and \emph{hi} settings achieves significance after applying a Bonferroni correction ($\alpha=0.016$), but the other comparisons do not achieve significance.
-
-A possible explanation for the observed behaviour is that the more distinguishable changes in the audio pitch with the \emph{hi} configuration better informs the user when they are on target, leading to a more accurate estimate, but also increases the time it takes to point in the right direction.
-Conversely, the \emph{lo} and \emph{med} gradients make it more difficult for the user to know when they are on target, leading to a shorter search time, but at the cost of lower accuracy.
-This is confirmed by the results obtained in Section~\ref{sec:tilt-results} and the Wilcoxon test results.
-
-The results collected from the participants with partial eyesight follow the same trends observed in the blindfolded participants, giving $IPs$ of 0.58, 1.3 and 0.35 for the \emph{lo}, \emph{med} and \emph{hi} gradient settings respectively.
 
@@
 
-%The final major suggestion was to add some form of on-target confirmation, either voice, vibration or some other audio cue.
+The final major suggestion was to add some form of on-target confirmation, either voice, vibration or some other audio cue.
 For the purposes of this experiment, we purposefully opted to not inform the participant when they were on target, since we are interested in the target acquisition accuracy.
@@
 The steeper, $m_h$ and $m_m$ pitch-gains were found to produce the best results in this respect.
-Furthermore, we discovered a logarithmic relationship between the index of difficulty of a target and the time taken by a participant to find it, confirming that the results with our interface adhere to Fitts's Law.
-However, there is a compromise to be made between speed and accuracy, with the $m_h$ pitch-gain gradient directing the user to the target in the longest time.
+%Furthermore, we discovered a logarithmic relationship between the index of difficulty of a target and the time taken by a participant to find it, confirming that the results with our interface adhere to Fitts's Law.
+%However, there is a compromise to be made between speed and accuracy, with the $m_h$ pitch-gain gradient directing the user to the target in the longest time.
 

### 2019-05-14 article.tex
Revised lit review

@@
 \todo{chop up this section. Make anonymous}
-Attempting to deliver a system that allows people with visual impairments to independently navigate and accomplish everyday tasks is not new; in fact, there are multiple commercial systems and research prototypes already available on the market.
-One approach that has been investigated is to outfit the existing white walking cane with various sensors, such as sonar, radar, motor encoders, etc.~\cite{ulrich1997, marion2008batcane} to warn the user of upcoming obstacles, instead of relying on haptic feedback from the impact between the cane and the obstacle.
-Another approach is to outfit a walking cane to act as a radio-frequency identification (RFID) antenna that can read a set of RFID tags placed at strategic locations around the environment at key spots or along a path~\cite{faria2010electronic, willis2005}.
-This modification to the traditional cane is more discreet than the systems mentioned earlier and has been shown to work well.
-Bluetooth tags and a smartphone can also be used in a similar manner~\cite{sato2017navcog3}.
-However, the major drawbacks here are the significant cost and effort of modifying existing infrastructure with RFID and Bluetooth tags and maintaining them to stay up to date with a changing environment.
-GPS-based systems~\cite{ran2004drishti, loomis2001navigating, kammoun2012navigation}, while cheap and reliable in outdoor environments, are not applicable in built-up urban areas and indoors where GPS signals are notoriously unreliable.
-Computer vision-based systems provide a good compromise between usability, cost and accuracy and have been the focus of much research recently~\cite{manduchi2014last}.
-One increasingly popular solution is to use RGB-D depth sensing cameras, which are becoming increasingly more accurate and cost-effective, to build a 3D image map of the environment, allowing a user to safely traverse through it~\cite{lee2015, rodriguez2012obstacle}.
-Another approach is to use vision-based object recognition techniques to detect various objects and landmarks, such as doors, staircases, etc., and communicate their relative location to the user~\cite{schauerte2012assistive, tian2013b, fiannaca2014headlock}, or use audio instructions to instruct a user with vision impairment to fully capture an object of interest~\cite{vazquez2012helping}.
 
-An important feature of user-centric systems is a human-machine interface (HMI) that enables effective and seamless two-way communication between the system and the user.
-In previous surveys, researchers found that people with visual impairments prefer receiving feedback and instructions in the form of speech and haptic feedback cues~\cite{khoo2016multimodal, ross2000wearable, vazquez2012helping}.
-However, haptic feedback modes typically have a lower bandwidth when compared to audio feedback and also require the user to wear a special device in order to transmit the haptic signals to the user effectively.
+Earlier attempts at improving a person with visual impairment's navigation experience involved outfitting the commonly-used walking cane with remote detection systems, such as sonar, radar and RFID tags, to transform a cane into an early-warning system~\cite{ulrich1997,marion2008batcane,faria2010electric,willis2005}.
+Bluetooth tags and a smartphone can be used in a similar manner~\cite{sato2017navcog3}.
+However, the expense and effort of maintaining such tags make them less attractive for wide-scale adoption.
+Computer vision-based systems provide a good compromise between usability, cost and accuracy.
+One increasingly popular solution is to use RGB-D depth sensing cameras, which are becoming increasingly accurate and cost-effective, to build a 3D image map of the environment, and guiding a user through it~\cite{lee2015, rodriguez2012obstacle}.
+Alternatively, object recognition techniques can be used to detect various objects and landmarks, such as doors, staircases, etc., and communicate their relative location to the user~\cite{schauerte2012assistive, tian2013b, fiannaca2014headlock}, or use audio instructions to instruct a user with vision impairment to fully capture an object of interest~\cite{vazquez2012helping}.
+
+%Attempting to deliver a system that allows people with visual impairments to independently navigate and accomplish everyday tasks is not new; in fact, there are multiple commercial systems and research prototypes already available on the market.
+%One approach that has been investigated is to outfit the existing white walking cane with various sensors, such as sonar, radar, motor encoders, etc.~\cite{ulrich1997, marion2008batcane} to warn the user of upcoming obstacles, instead of relying on haptic feedback from the impact between the cane and the obstacle.
+%Another approach is to outfit a walking cane to act as a radio-frequency identification (RFID) antenna that can read a set of RFID tags placed at strategic locations around the environment at key spots or along a path~\cite{faria2010electronic, willis2005}.
+%This modification to the traditional cane is more discreet than the systems mentioned earlier and has been shown to work well.
+%Bluetooth tags and a smartphone can also be used in a similar manner~\cite{sato2017navcog3}.
+%However, the major drawbacks here are the significant cost and effort of modifying existing infrastructure with RFID and Bluetooth tags and maintaining them to stay up to date with a changing environment.
+%GPS-based systems~\cite{ran2004drishti, loomis2001navigating, kammoun2012navigation}, while cheap and reliable in outdoor environments, are not applicable in built-up urban areas and indoors where GPS signals are notoriously unreliable.
+%Computer vision-based systems provide a good compromise between usability, cost and accuracy and have been the focus of much research recently~\cite{manduchi2014last}.
+%One increasingly popular solution is to use RGB-D depth sensing cameras, which are becoming increasingly more accurate and cost-effective, to build a 3D image map of the environment, allowing a user to safely traverse through it~\cite{lee2015, rodriguez2012obstacle}.
+%Another approach is to use vision-based object recognition techniques to detect various objects and landmarks, such as doors, staircases, etc., and communicate their relative location to the user~\cite{schauerte2012assistive, tian2013b, fiannaca2014headlock}, or use audio instructions to instruct a user with vision impairment to fully capture an object of interest~\cite{vazquez2012helping}.
+
+An important feature of user-centric systems is a human-machine interface (HMI) that enables effective two-way communication between the system and the user.
+In previous surveys, researchers found that people with visual impairments prefer receiving instructions in the form of speech and haptic feedback cues~\cite{khoo2016multimodal, ross2000wearable, vazquez2012helping}.
+However, haptic feedback modes typically have a lower bandwidth when compared to audio feedback and also require the user to wear a special device in order to transmit the signals effectively.
 Work has also been done in translating a visual scene into non-visual formats, with so-called sensory substitution systems (e.g.
 `The Voice'~\cite{meijer2010}) and virtual audio reality (VAR) systems~\cite{frauenberger2003} reporting favourable results.
-However, The Voice, while helpful, has a very steep learning curve that has proven to be a significant barrier to entry.
-With VAR systems, it is not clear how unknown environments, where markers have not yet been encoded, would be handled and described to the user.
+However, The Voice has a very steep learning curve that has proven to be a significant barrier to entry and with VAR systems, it is not clear how unknown environments, where markers have not yet been encoded, would be handled and described to the user.
 
-Spatial audio has also been considered to convey the direction of a target.
-Experiments have previously determined that people are able to find the location of a stationary sound source with an error of $\pm$\SI{35}{\degree}, in both the pan and tilt dimensions~\cite{zwiers2001spatial}, for both early-blind and normally-sighted people.
-However, in~\cite{lewald2013exceptional, lessard1998early} it was found that the blind have a clear advantage in localisation accuracy over sighted people when presented with more difficult tasks, such as targets in motion and narrow-band stimuli, with~\cite{lewald2013exceptional} reporting an average absolute localisation error of around \SI{10}{\degree} in the pan and tilt dimensions.
-Other authors found that the minimum difference in the spatial sound's angle for the user to be able to perceive movement is approximately \SI{1.7}{\degree}. 
-During these experiments, an audio speaker was physically manoeuvred to provide the participant with a spatialised sound tone~\cite{ashmead1998spatial}.
-Researchers have also tried using simulated spatial audio to inform the user from which direction a sound is originating~\cite{holland2002audiogps, kammoun2012navigation, rebillat2009smart, menelas2010audio, wilson2007swan, zotkin2004rendering}.
+%Spatial audio has also been considered to convey the direction of a target.
+Previous experiments have determined that people are able to find the location of a stationary sound source with an error of $\pm$\SI{35}{\degree}, in both the pan and tilt dimensions~\cite{zwiers2001spatial}, for both early-blind and normally-sighted people.
+However, in~\cite{lewald2013exceptional, lessard1998early} it was found that the blind have a clear advantage in localisation accuracy over sighted people when presented with more complex tasks, such as targets in motion and narrow-band stimuli, with~\cite{lewald2013exceptional} reporting an average absolute localisation error of around \SI{10}{\degree} in the pan and tilt dimensions.
+%Other authors found that the minimum difference in the spatial sound's angle for the user to be able to perceive movement is approximately \SI{1.7}{\degree}. 
+%During these experiments, an audio speaker was physically manoeuvred to provide the participant with a spatialised sound tone~\cite{ashmead1998spatial}.
+Researchers have used simulated spatialised audio to inform the user of the sound source's direction~\cite{holland2002audiogps, kammoun2012navigation, rebillat2009smart, menelas2010audio, wilson2007swan, zotkin2004rendering}.
 In these works, a sound was played through a set of headphones and the source spatialised with a head-related transfer function (HRTF), tricking the listener into thinking the sound source was located at some arbitrary 3D location.
-Various audition techniques and methods were then used to guide the user along a path.
-Other authors have also provided a framework for evaluating the quality of this 3D sound in terms of its psychoacoustic properties~\cite{guastavino2004perceptual, nicol2014roadmap}.
+%Various audition techniques and methods were then used to guide the user along a path.
+%Other authors have also provided a framework for evaluating the quality of this 3D sound in terms of its psychoacoustic properties~\cite{guastavino2004perceptual, nicol2014roadmap}.
 There are also experimental results about how well users can find targets presented with spatial sound in the tilt and panning dimensions with normal headphones~\cite{katz2011spatial, zwiers2001spatial}, as well as work that has shown similar levels of localisation performance between normal and bone-conducting headphones in the pan dimension~\cite{macdonald2006spatial}.
-However, to our knowledge no extensive work or experiments have been done to determine how well users respond to tilt adjustment instructions using a tone with \emph{varying pitch}, in particular when using bone-conducting headphones, and how changes to this tone's behaviour affects performance.
+However, to our knowledge no extensive work or experiments have been done to determine how well users respond to tilt adjustment instructions using a tone with \textit{varying pitch}, in particular when using bone-conducting headphones, and how changes to this tone's behaviour affects performance.
 

### 2019-05-14 article.tex
Revised system description

@@
 
-Our ultimate goal is to deliver a navigation system that is capable of guiding a user with visual impairments on the last leg of their journey, e.g.\ to a specific aisle and shelf in a shop, using only a mobile phone.
+Our ultimate goal is to deliver a navigation system that can guide a user with visual impairments on the last leg of their journey, e.g.\ to a specific aisle and shelf in a shop, using only a mobile phone.
 A large amount of data need to be translated from a visual form into a format that is useful to people with limited or no vision.
 We therefore plan to use a combination of voice, audio and vibration cues to translate visual navigation data as effectively as possible and overcome the bandwidth limitation of the human ear. 
+However, for this paper, we only considered the spatialised audio mode and its variation in pitch in order to determine its effectiveness in conveying a target's pan and tilt angles.
 
@@
 \end{anonsuppress}
-The system is based on a Google Tango tablet, an Android-based device that comes equipped with an RGB-D cameras to sense colour and depth.
+The navigation system is based on a Google Tango tablet, an Android-based device that comes equipped with an RGB-D cameras to sense colour and depth.
 It combines an inertial measurement unit with powerful and robust landmark recognition and image processing algorithms to localise itself in real-time.
 An added benefit of this platform is its familiar, compact form-factor which will help overcome the hurdle of user-acceptance and usability.
+We also use a set of bone-conducting headphones (see \cref{fig:tango-headphone}) that are placed externally on a user's head so that the system does not occlude the perception of real-world sounds and does not interfere with a user's normal hearing function.
+%In the future, we will use multiple feedback modes to provide the user with navigation and obstacle avoidance instructions.
 
-We use a set of bone-conducting headphones (see \cref{fig:tango-headphone}) that are placed externally on a user's head so that the system does not occlude the perception of real-world sounds and does not interfere with a user's normal hearing function.
-In the future, we will use multiple feedback modes to provide the user with navigation and obstacle avoidance instructions.
-However, for this paper, we only considered the spatialised audio mode and its variation in pitch in order to determine its effectiveness in conveying a target's pan and tilt angles.
-
-A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}.
-Here, the arrows indicate the direction of the flow of information.
-When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the Tango's current position and orientation.
-The audio generator then produces a tone based on the difference between the Tango and the target's positions (in the Tango's global coordinate system) and sends it to the audio output channel, which plays it back to the user.
-The WiFi recording module is constantly monitoring the different parameter values of the Tango and target's positions, as well as the system's output, and records it to a remotely stored datafile.
+A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}, where the arrows indicate the direction of the flow of information.
+When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the device's current position and orientation.
+The audio generator then produces a tone based on the difference between the device and target's positions and sends it to the audio output channel, which plays it back to the user.
+The WiFi recording module is constantly monitoring the different parameter values of the device and target's positions, as well as the system's output, and records it to a remotely stored datafile.
 
@@
 
-For the series of experiments performed in this work, only the audio feedback mode was used to interface with the user.
-The audio component is responsible for conveying the 2D position of a target on the vertical plane w.r.t.\ the Tango's coordinate system, showed in \cref{fig:cam-coords}, in terms of pan and tilt angles.
-In future system iterations, the distance to a target can be rendered by adjusting the audio signal's amplitude as a function of the distance.
+%For the series of experiments performed in this work, only the audio feedback mode was used to interface with the user.
+The audio component is responsible for conveying the 2D position of a target on the vertical plane, showed in \cref{fig:cam-coords}, in terms of pan and tilt angles.
+%In future system iterations, the distance to a target can be rendered by adjusting the audio signal's amplitude as a function of the distance.
 The audio signal is a continuous $\sim$\SI{10}{\hertz} sinusoidal sound wave that is played to the user through bone-conducting headphones.
-We select a sinusoidal wave because it is relatively simple to manipulate and analyse, which will be replaced by a richer, more natural tone at a later stage of the project.
+We use a sinusoidal wave here because it is relatively simple to manipulate and analyse and will be replaced by a richer, more natural tone at a later stage.
 
 The audio is spatialised in the pan dimension using the OpenAL\footnote{http://openal.org} sound library's HRTF, while the tilt angle is conveyed by varying the audio tone's pitch.
-We use this approach because the external set of bone-conducting headphones plays the sound through a user's cheekbones instead of their outer ears, bypassing the ears' pennae that provide humans their ability to localise elevated sound sources~\cite{roffler1968factors, algazi2001elevation}.
-This makes an HRTF less effective in conveying the target's tilt angle and therefore needs to be conveyed using another method; a varying pitch tone in this case.
+We use this approach because the external set of bone-conducting headphones plays the sound through a user's cheekbones instead of their outer ears, bypassing the ears' pennae that provide the ability to localise elevated sound sources~\cite{roffler1968factors, algazi2001elevation}.
+This makes an HRTF less effective in conveying the target's elevation and therefore needs to be conveyed using another method; by varying the tone's pitch in this case.
 The difference between the target's angular position and the device's angular orientation are used to generate the audio signals.
@@
 
-We wish to determine how the gradient of the pitch gain as a function of $\theta$ (i.e.\ $m = \frac{df}{d\theta}$) affects a user's performance, e.g.\ does steeper $\frac{df}{d\theta}$ lead to an increased target acquisition rate?
+We wish to determine how the gradient of the pitch gain as a function of $\theta$ (i.e.\ $m = \frac{df}{d\theta}$) affects a user's performance, e.g.\ does a greater $m$ lead to an increased target acquisition rate?
 For this we select 3 different pitch settings, referred to henceforth as $m_l$, $m_m$ and $m_h$ for the smallest, middle and highest gain gradients respectively. 
@@
 For $m_m$, the $f_{max}$ and $f_{min}$ are set to 2 octaves higher and lower than $f_{512}$ (\SI{2048}{\hertz} and \SI{128}{\hertz}) and $m_h$ to 3 octaves higher and lower (\SI{4096}{\hertz} and \SI{64}{\hertz}).
-We selected these limits for practical reasons, given the fact that the bone conducting headphones we use have low volume gain at very high and low frequencies, making it difficult to hear. 
+We selected these limits for practical reasons, given the fact that the bone conducting headphones we use have low volume gain at the frequency spectrum extremes, making it difficult to hear. 
 The values of $m_l, m_m, m_h$ are visualised in \cref{fig:pitch-gain}.

### 2019-05-15 article.tex
Rewrote the experiment description

@@
 
-\section{Experiments}\label{sec:experiments}
+\section{Target Search Experiment}\label{sec:experiments}
 
-We performed a set of experiments with our audio interface to determine its effectiveness at directing a user to adjust a camera's $\phi$ and $\theta$ to point it to a target.
-The results from the experiments allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimise the behaviour of the feedback modes in our portable navigation aid.
+We conducted a set of experiments to evaluate the audio interface's effectiveness at driving a user to point the camera at a target in the pan and tilt dimensions.
+Furthermore, we wish to see how changes to $\frac{df}{d\theta}$ affect a user's performance.
 
-The participants were given time before the experiments to familiarise themselves with the device and the tones it emits, as well as what the $f_{512}$ `on-target' tone sounds like.
-We also tested the system with 3 legally blind participants and compared their data to the blindfolded dataset.
-These latter experiments in particular provided us with valuable subjective feedback that can be used to improve future iterations.
+We recruited 2 groups of participants for the experiments.
+Group $G1$ consists of 42 young adults (mostly students) with healthy eyesight, with 10 males and 32 females being $20\pm1.5$ years old on average.
+This group was blindfolded throughout the experiment and forms the bulk of the participant population.
+Group $G2$ is made up of 3 legally blind adults with varying levels of vision limits (3 males, average age of $40\pm8$ years). 
+This group makes up less than 10\% of the total population, but provided valuable subjective feedback that will help improve the system before evaluating it with a larger group of people with vision impairments.
+All participants joined the experiment on a voluntary basis with written consent and none have any other impairments that affects their interpretation of the audio guidance cues.
 
-For the experiments we used two groups of participants, with one ($G1$) including 42 sighted and blindfolded participants and the other ($G2$) 3 legally blind volunteers with varying degrees of vision impairment.
-They performed a series of experiments using our system with a pair of `AfterShockz Sport3' bone-conducting headphones.
-The participants were recruited on a volunteer-basis and consisted of a diverse group of undergraduate students and professionals with ages ranging between 17 and 40 years ($\mu=22\pm3.5$ years, 13 male, 32 female) and did not not have significant hearing issues or any other disability that could affect the experiment.
+For the experiment, the participants were given a Tango tablet device, running an app written for this experiment, and a pair of AfterShockz Sportz3' bone conducting headphones (both pictured in \cref{fig:tango-headphone}) and were blindfolded where appropriate.
+The app generates a virtual target, one at a time and a constant \SI{2}{\metre} from the participant, and uses the device's measurements to determine $\phi$ and $\theta$.
+These angles are then used to generate and present the user with the audio signal to direct them to the target. 
+As the participant rotates the camera, $\phi$ and $\theta$ are adjusted and the audio signal changes according to reflect the changes.
+When a participant was satisfied that they were on target, they tapped the screen which generated a new target target which they were then directed to. 
+Each participant was given 28 targets in total that were randomly generated and equally spread across 4 quadrants to avoid clustering. 
+After the 28 targets were found, the gradient setting ($m$ in \cref{eq:frequency}) was adjusted and the experiment was repeated. 
+The order in which the gradient setting was changed for each participant was randomised to minimise any the learning effect.
+The app streams various data on the current device and target poses to a laptop computer via a WiFi connection in real-time. 
+Before the experiment session started, each participant was given some time to familiarise themselves with the device and the audio tone and was given the oppertunity to learn what the $f_{512}$ `on-target' and on-centre tone sounds like that will confirm that they are level with the target.
 
-We are only evaluating the interface in the pan and tilt dimensions and the 3D targets are therefore generated at a constant distance of \SI{2}{\metre} from the participant.
-Throughout the experiments, various parameters of the targets and participants were recorded and streamed in real-time to a laptop computer via a WiFi connection.
+The measure of performance here is the accuracy with which a user points the camera towards a target.
+The accuracy is taken as the angular difference between the device's and target's poses at the time the participant tapped the screen and a smaller error would indicate more accurate results.
+The pan and tilt results are separated to understand the effect of changing the gradient setting has on either dimension's accuracy.
+To minimise the speed/accuracy biases in the results, we asked the participants to focus on finding the targets as well as they could without worrying about the time it took.
 
-For the experiment, the participants were blindfolded where necessary and given a Tango device running an app purpose-written for this experiment.
-When started, a set of virtual targets were presented one at a time to the participant on the device.
-Then, depending on the direction the participant was currently pointing the camera relative to the target's position, the Tango generated and played a tone via the bone-conducting headphones to indicate the pan and tilt angle adjustment required to point the camera to the target.
+%We performed a set of experiments with our audio interface to determine its effectiveness at directing a user to adjust a camera's $\phi$ and $\theta$ to point it to a target.
+%The results from the experiments allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimise the behaviour of the feedback modes in our portable navigation aid.
 
-Once the participant pointed the camera toward where they thought the target was located, they had to tap the screen to confirm the target's perceived location at which point a new target was presented and the search-process was repeated.
-28 targets were presented to each participant per run.
-The positions of these targets were randomly generated and equally spread across the 4 quadrants on the vertical plane to prevent a clustering of targets at the same location.
-After every experiment run, the gradient ($m$ in \cref{eq:frequency}) was adjusted to make the pitch increase at a lower or higher rate.
-This was done to see whether, for example, a more rapid increase in pitch would help the participant find the target faster or more accurately.
+%The participants were given time before the experiments to familiarise themselves with the device and the tones it emits, as well as what the $f_{512}$ `on-target' tone sounds like.
+%We also tested the system with 3 legally blind participants and compared their data to the blindfolded dataset.
+%These latter experiments in particular provided us with valuable subjective feedback that can be used to improve future iterations.
 
-To minimise any speed/accuracy trade-off bias in the results, we asked the participants to search for the targets without placing particular emphasis on accuracy or time. 
-The order in which the settings were set for each participant was randomised in order to minimise any learning effect the participant population might display between each experiment.
+%For the experiments we used two groups of participants, with one ($G1$) including 42 sighted and blindfolded participants and the other ($G2$) 3 legally blind volunteers with varying degrees of vision impairment.
+%They performed a series of experiments using our system with a pair of `AfterShockz Sport3' bone-conducting headphones.
+%The participants were recruited on a volunteer-basis and consisted of a diverse group of undergraduate students and professionals with ages ranging between 17 and 40 years ($\mu=22\pm3.5$ years, 13 male, 32 female) and did not not have significant hearing issues or any other disability that could affect the experiment.
 
-In this case, the system's measure of performance is given by the target acquisition accuracy.
-The accuracy is given as the difference between the device's orientation at the time the participant confirmed they were on target, and the target's actual angular position.
-We separate the results of the tilt and pan dimensions in order to determine how the different pitch settings affect pointing accuracy.
+%We are only evaluating the interface in the pan and tilt dimensions and the 3D targets are therefore generated at a constant distance of \SI{2}{\metre} from the participant.
+%Throughout the experiments, various parameters of the targets and participants were recorded and streamed in real-time to a laptop computer via a WiFi connection.
 
-\section{Experiment Results and Discussion}\label{sec:results}
+%For the experiment, the participants were blindfolded where necessary and given a Tango device running an app purpose-written for this experiment.
+%When started, a set of virtual targets were presented one at a time to the participant on the device.
+%Then, depending on the direction the participant was currently pointing the camera relative to the target's position, the Tango generated and played a tone via the bone-conducting headphones to indicate the pan and tilt angle adjustment required to point the camera to the target.
+
+%Once the participant pointed the camera toward where they thought the target was located, they had to tap the screen to confirm the target's perceived location at which point a new target was presented and the search-process was repeated.
+%28 targets were presented to each participant per run.
+%The positions of these targets were randomly generated and equally spread across the 4 quadrants on the vertical plane to prevent a clustering of targets at the same location.
+%After every experiment run, the gradient ($m$ in \cref{eq:frequency}) was adjusted to make the pitch increase at a lower or higher rate.
+%This was done to see whether, for example, a more rapid increase in pitch would help the participant find the target faster or more accurately.
+
+%To minimise any speed/accuracy trade-off bias in the results, we asked the participants to search for the targets without placing particular emphasis on accuracy or time. 
+%The order in which the settings were set for each participant was randomised in order to minimise any learning effect the participant population might display between each experiment.
+
+%In this case, the system's measure of performance is given by the target acquisition accuracy.
+%The accuracy is given as the difference between the device's orientation at the time the participant confirmed they were on target, and the target's actual angular position.
+%We separate the results of the tilt and pan dimensions in order to determine how the different pitch settings affect pointing accuracy.
+
+\section{Results}\label{sec:results}
 

### 2019-05-15 article.tex
Rewrote the experiment description

@@
 
-\section{Results}\label{sec:results}
+\section{Results and Discussion}\label{sec:results}
 
-\subsection{Pan Results}
-
-The results from the target search experiment for the participants in $G1$ in the pan dimension are given on the abscissa of the 2D histograms in \crefrange{fig:err-results-lo}{fig:err-results-hi}, where the angular errors in the pan and tilt directions are plotted against each other.
-A set of box-plots of the pan errors' median and standard deviations are also given in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} for each of the $m_l, m_m$ and $m_h$ setting. 
-The results are summarised in \cref{tab:results}.
+The results for the participants in $G1$ given if the 2D histograms in \crefrange{fig:err-results-lo}{fig:err-results-hi}, where the pan error is on the abscissa and the tilt error on the ordinates.
+A set of box-plots of the angular errors' median and standard deviations are given in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} for the $m_l, m_m$ and $m_h$ settings. 
+The results for $G1$ are summarised in \cref{tab:results}.
 
@@
 \end{table}
+
+\subsection{Pan Results}
 

### 2019-05-15 article.tex
Rewrote the results section

@@
 
-The results for the participants in $G1$ given if the 2D histograms in \crefrange{fig:err-results-lo}{fig:err-results-hi}, where the pan error is on the abscissa and the tilt error on the ordinates.
+The results for the participants are given if the 2D histograms in \crefrange{fig:err-results-lo}{fig:err-results-hi}, where the pan error is on the abscissa and the tilt error on the ordinates.
 A set of box-plots of the angular errors' median and standard deviations are given in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} for the $m_l, m_m$ and $m_h$ settings. 
-The results for $G1$ are summarised in \cref{tab:results}.
+The results for $G1$ are summarised in \cref{tab:results}, while the results for $G2$ are given in \cref{tab:vi-results}.
 
@@
   \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_lo.png}
-  \caption{Angular error data for $G1$ and the $m_l$ setting. }\label{fig:err-results-lo}
+  \caption{Angular error data for the $m_l$ setting. }\label{fig:err-results-lo}
 \end{figure}
@@
   \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_med.png}
-  \caption{Angular error data for $G1$ and the $m_m$ setting. }\label{fig:err-results-med}
+  \caption{Angular error data for the $m_m$ setting. }\label{fig:err-results-med}
 \end{figure}
@@
   \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_hi.png}
-  \caption{Angular error data for $G1$ and the $m_h$ setting. }\label{fig:err-results-hi}
+  \caption{Angular error data for and the $m_h$ setting. }\label{fig:err-results-hi}
 \end{figure}
@@
   \includegraphics[clip, trim=20 -70 100 100, width=0.8\columnwidth]{figures/err_boxplot_medians.png}
-  \caption{Error medians for $G1$.}\label{fig:err-boxplot-median}
+  \caption{Error medians for the pan and tilt dimension and each gradient setting.} \label{fig:err-boxplot-median}
 \end{figure}
@@
   \includegraphics[clip, trim=80 -70 100 0, width=0.8\columnwidth]{figures/err_boxplot_std.png}
-  \caption{Error standard deviations for $G1$.}\label{fig:err-boxplot-std}
+  \caption{Error standard deviations for the pan and tilt dimensions and each gradient setting.}\label{fig:err-boxplot-std}
 \end{figure}
@@
 
-\subsection{Pan Results}
-
-\crefrange{fig:err-results-lo}{fig:err-results-hi} and the median and mean points from the box-plots in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} show that the data in the pan dimension is approximately normally distributed around zero.
-However, $p$-scores below the critical 0.05 level from the Shapiro-Wilkes test and inspection of the quantile-quantile (Q-Q) plots do not give enough confidence to consider the data as normally distributed and we therefore analyse the data through non-parametric techniques.
-
-For the data collected from $G1$, there is a strong linear correlation between the participants' guesses and the targets' true pan angles, shown by the high Spearman correlation scores of approximately 0.75 ($p < 0.01$) for all of the datasets, with the $m_m$ setting displaying the marginally best result of 0.77.
-The 3 settings have similar average errors and standard deviations, with the $m_m$ setting again producing the marginally best results with the smallest average error and standard deviation.
-However, the differences are relatively small (approximately 6\%) and are not significant enough (Friedman test $p \gg 0.05$) to conclude that the pitch gradient has an effect on the target acquisition accuracy performance in the pan dimension.
-
-The data collected from $G2$ follow a similar trend to that of $G1$: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all 3 settings.
-These results are summarised in \cref{tab:vi-results}.
-Unfortunately, not enough samples could be collected to draw any final conclusions.
-However, these results are in line with results from previous work~\cite{zwiers2001spatial}, indicating that the groups with partial and normal eyesight respond with similar levels of accuracy to spatialised sound when presented with simple tasks.
-In addition, they also confirm that a participant's target search capability in the pan dimension is robust to the changing pitch for the target's tilt angle which is a useful result in support of the effectiveness of our audio interface.
-
 \begin{table}
@@
 
+\subsection{Pan Results}
+
+\crefrange{fig:err-results-lo}{fig:err-results-hi} and the median and mean points from the box-plots in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} show that the data in the pan dimension are approximately normally distributed around zero.
+However, a Shapiro-Wilkes test score below the critical threshold do not give enough confidence to consider the data as normally distributed and we therefore analyse the data through non-parametric techniques.
+
+For the data collected from $G1$, there is a strong linear correlation between the participants' guesses and the targets' true pan angles, shown by the high Spearman correlation scores of approximately 0.75 ($p < 0.01$) for all of the datasets, with the $m_m$ setting displaying the marginally best result of 0.77.
+The 3 settings have similar average errors and standard deviations, with the $m_m$ setting again producing the marginally best results with the smallest average error and standard deviation.
+However, the differences are relatively small (approximately 6\%) and are not significant enough (Friedman test $p = 0.92$) to conclude that the pitch gradient has an effect on the target acquisition accuracy performance in the pan dimension.
+
+The data collected from $G2$ follow a similar trend to that of $G1$: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all 3 settings.
+These results are summarised in \cref{tab:vi-results}.
+Unfortunately, not enough samples could be collected to draw any final conclusions.
+However, these results are in line with results from previous work~\cite{zwiers2001spatial}, indicating that the groups with partial and normal eyesight respond with similar levels of accuracy to spatialised sound when presented with simple tasks.
+
+These results show that both groups managed to find the targets with reasonable level of accuracy and that the pan error is robust to changes to the pitch and its rate of change; a useful result in support of the effectiveness of this audio interface.
+
 \subsection{Tilt Results}\label{sec:tilt-results}
 
-The ordinates in \crefrange{fig:err-results-lo}{fig:err-results-hi} also show the results recorded during the experiment with $G1$ in the tilt direction.
-A set of box-plots are given in \cref{fig:err-boxplot-median} to show the average tilt error between the participants in $G1$'s guesses and the targets' true positions.
-All of the results are summarised in \cref{tab:results}. 
-The data here are also considered not normally distributed following inspections of the Q-Q plots and Shapiro-Wilkes test results and are analysed accordingly.
+%The ordinates in \crefrange{fig:err-results-lo}{fig:err-results-hi} also show the results recorded during the experiment with $G1$ in the tilt direction.
+%A set of box-plots are given in \cref{fig:err-boxplot-median} to show the average tilt error between the participants in $G1$'s guesses and the targets' true positions.
+%All of the results are summarised in \cref{tab:results}. 
+%The data here are also considered not normally distributed following inspections of the Q-Q plots and Shapiro-Wilkes test results and are analysed accordingly.
 
-We found that there is reasonably significant correlation between the participants' guesses and the actual locations of the targets, shown by moderate Spearman correlation scores of approximately 0.38 for \emph{lo}, 0.48 for \emph{med} and the \emph{hi} gradient giving the strongest R-scores of the 3 with a score of 0.55 ($p < 0.01$ for all 3 settings).
-This indicates that the varying pitch is working as expected and the participants are generally interpreting the cues correctly.
+The data within the tilt dimension are also found to be non-normal following scored below the critical threshold from the Shapiro-Wilkes test.
+The Spearman test for the data reveals a reasonably significant correlation between the participants' guesses and the actual locations of the targets, with correlation scores of approximately 0.38 for $m_l$, 0.48 for $m_m$ and the $m_h$ gradient giving the strongest correlation score with 0.55 ($p < 0.01$ for all 3 settings).
+This indicates that the participants generally interpret the cues from the varying the pitch correctly and are mostly successful at pointing the camera in the correct tilt angle.
 
-The average errors of the datasets are relatively close to one another, with the $m_l$ setting producing the largest absolute error and standard deviation at \SI{0.40}{\radian} and \SI{0.46}{\radian}.
+The average errors of the datasets are relatively close to one another, with the $m_l$ setting producing the largest absolute error and standard deviation at \SI{0.40}{\radian} and \SI{0.46}{\radian} respectively.
 The $m_m$ and $m_h$ settings have similar absolute errors of \SI{0.32}{\radian} and \SI{0.34}{\radian} respectively.
-This is in line with the correlation scores, with $m_l$ giving a worst result and $m_h$ giving the best results overall, with highest correlation score and relatively low absolute angular errors and standard deviation, marginally beating $m_m$.
+This is in line with the correlation scores, with $m_l$ giving the worst result and $m_h$ giving the best results overall, with highest correlation score and relatively low absolute angular errors and standard deviation, marginally beating $m_m$.
 
-We use the Friedman test on the medians of the data to better understand the difference differences between the datasets.
-We use the median values here since the data are not normally spread and there is significant noise within the data which may contaminate the mean values.
-The Friedman test indicates a statistically significant difference between the 3 settings ($p < 0.01$).
-A post-hoc analysis with a Wilcoxon signed rank test and a critical threshold with a Bonferroni correction applied for the 3 settings ($\alpha=0.016=\frac{0.04}{3}$) shows that both the $m_m$ and $m_h$ settings are significantly different than the $m_l$ setting ($p=0.0014$ for both settings), but that the $m_m$ and $m_h$ settings do not produce significantly different results from one another ($p=0.42$).
-This indicates there is an inflection point where increasing $\frac{df}{d\theta}$ produces diminishing returns.
+Since the data are not normally spread and there is significant levels of noise within the data which may contaminate the mean values, we use the medians to analyse the datasets.
+For this, the Friedman test is used on the medians and it was found that there is a significant difference between the 3 settings' datasets ($p < 0.01$).
+A post-hoc analysis with a Wilcoxon signed rank test and a critical threshold with a Bonferroni correction applied for the 3 settings ($\alpha=0.016=\frac{0.05}{3}$) shows that both the $m_m$ and $m_h$ settings are significantly different from the $m_l$ setting ($p=0.0014<\alpha$ for both settings), but that the $m_m$ and $m_h$ settings do not produce significantly different results from one another ($p=0.42>\alpha$).
+This indicates there is an inflection point where increasing $\frac{df}{d\theta}$ produces diminishing returns and that we cannot conclude that the $m_h$ setting is better than the $m_m$ gradient.
+However, both settings conclusively produce more accurate results than the $m_l$ setting.
+
+%We use the Friedman test on the medians of the data to better understand the difference differences between the datasets.
+%We use the median values here since the data are not normally spread and there is significant noise within the data which may contaminate the mean values.
+%The Friedman test indicates a statistically significant difference between the 3 settings ($p < 0.01$).
+%A post-hoc analysis with a Wilcoxon signed rank test and a critical threshold with a Bonferroni correction applied for the 3 settings ($\alpha=0.016=\frac{0.04}{3}$) shows that both the $m_m$ and $m_h$ settings are significantly different than the $m_l$ setting ($p=0.0014$ for both settings), but that the $m_m$ and $m_h$ settings do not produce significantly different results from one another ($p=0.42$).
+%This indicates there is an inflection point where increasing $\frac{df}{d\theta}$ produces diminishing returns.
 
@@
 
-After and during the experiments involving the participants with visual impairments, we had the opportunity to collect their feedback on the current system implementation and suggestions for future improvements.
+After the experiments with the participants with visual impairments in $G2$ were completed, we took the opportunity to collect their feedback on the audio interface's current implementation and gather suggestions for improvements for future iterations.
+When asked about their opinions on current assistive systems available on the market, the general consensus was that these systems are typically too prohibitively expensive, too complex and cumbersome to be useful for everyday use.
+Indeed, they seemed quite enthusiastic about a guidance system that they can use on a mobile phone.
 
-In general, they were satisfied with the current implementation and had little difficulty using it.
-Furthermore, the prohibitive cost, complexity and cumbersomeness of other existing systems discouraged our subjects from purchasing and using them, so they were quite enthusiastic about our goal of developing a mobile or tablet-based indoor navigation system.
+They were also generally satisfied with the guidance interface in its current form and had little problem learning how to use it.
+However, they, along with the participants in $G1$, reported auditory fatigue caused by long-term exposure to the sinusoidal audio tone.
+We were aware of this issue before the experiments were conducted and have considered replacing the simple sine wave tone with more natural and pleasant sounds.
+For example, musical instruments can be used to play different notes and scales to indicate different elevation angles~\cite{brewster1998using}.
+Furthermore, they suggested adding some voice component or tone prompt to confirm when they are on target, inform them of other important events or happenings or simply to intermittently assure them that the system is still active and that they are still on course.
+The former 2 suggestions were intentionally ignored in order to purely evaluate how accurately the audio tone can guide a user to the target.
+Going forward, however, these suggestions will be helpful for a commercial release version of the guidance system to make the guidance instructions clearer and to reassure users that the app has not crashed, for example.
 
-One aspect of the audio interface that requires improvement is the tone used during the experiments was not very pleasant and led to auditory fatigue after a long period of use.
-We are aware of this issue and we are already investigating more natural, `pleasant' and rich sounds to replace the basic sinusoidal wave that was used in the experiments.
-One possibility is to use musical instruments (e.g.\ MIDI sound files) to play notes and scales~\cite{brewster1998using}.
+On the hardware, only one participant had reservations regarding the choice of bone-conducting headphones, citing cost concerns. 
+However, he indicated that he could justify purchasing a set of bone-conducting headphones if he were to use them throughout the day to avoid cutting off environmental sounds.
+None of the participants had any technical issues using the headphones or mobile device and were able to properly use and interpret the guidance instructions.
 
-Concerning the bone-conducting headsets, only one participant had reservations about this choice, citing cost concerns.
-None of the participants had any technical issues in using the headset or misunderstanding audio cues.
-They all agreed that this is a valid choice to avoid cutting a person with visual impairments off from environmental sounds.
-Furthermore, they suggested to add some voice component to the system to inform the user of important events (e.g.
+%A last suggestion
+
+%After and during the experiments involving the participants with visual impairments, we had the opportunity to collect their feedback on the current system implementation and suggestions for future improvements.
+
+%In general, they were satisfied with the current implementation and had little difficulty using it.
+%Furthermore, the prohibitive cost, complexity and cumbersomeness of other existing systems discouraged our subjects from purchasing and using them, so they were quite enthusiastic about our goal of developing a mobile or tablet-based indoor navigation system.
+
+%One aspect of the audio interface that requires improvement is the tone used during the experiments was not very pleasant and led to auditory fatigue after a long period of use.
+%We are aware of this issue and we are already investigating more natural, `pleasant' and rich sounds to replace the basic sinusoidal wave that was used in the experiments.
+%One possibility is to use musical instruments (e.g.\ MIDI sound files) to play notes and scales~\cite{brewster1998using}.
+
+%Concerning the bone-conducting headsets, only one participant had reservations about this choice, citing cost concerns.
+%None of the participants had any technical issues in using the headset or misunderstanding audio cues.
+%They all agreed that this is a valid choice to avoid cutting a person with visual impairments off from environmental sounds.
+%Furthermore, they suggested to add some voice component to the system to inform the user of important events (e.g.
 \emph{`Target has been found'}, \emph{`You are veering off course'}, etc.) or to simply confirm and reassure the user that they are still on course.
 
-The final major suggestion was to add some form of on-target confirmation, either voice, vibration or some other audio cue.
-For the purposes of this experiment, we purposefully opted to not inform the participant when they were on target, since we are interested in the target acquisition accuracy.
-However, going forward we intend on adding an on-target notification in the form of an additional tone overlaid over the main tone.
+%The final major suggestion was to add some form of on-target confirmation, either voice, vibration or some other audio cue.
+%For the purposes of this experiment, we purposefully opted to not inform the participant when they were on target, since we are interested in the target acquisition accuracy.
+%However, going forward we intend on adding an on-target notification in the form of an additional tone overlaid over the main tone.
 

### 2019-05-15 article.tex
Rewrote conculsion

@@
 
-\subsection{Participant with Visual Impairments' Feedback}
+\subsection{Participants with Visual Impairment's Feedback}
 
@@
 
-In this paper, we presented a spatial audio interface to direct a user with visual impairments to point a camera toward a target.
-We also discussed a set of experiments to determine its effectiveness and performance, as well as some subjective feedback collected from participants with partial eyesight.
+In this work, we present an audio-based guidance interface that uses a spatialised audio tone with varying pitch to direct a user with visual impairments to point a camera toward a target. 
+We also present and discuss a set of experiments that were conducted  to determine the interface's effectiveness and performance, as well as some subjective feedback that was collected from participants with partial eyesight.
 
-We found that a spatial audio tone with a varying pitch can be used to convey the pan and tilt angles of a target using a set of bone-conducting headphones.
-The angular errors made by the participants are in line with those found in previous studies using similar audio interfaces.
-We also found that varying the pitch-gain gradient of our interface influences the accuracy of the system in the tilt dimension, as well as the time to target, without affecting the performance in the pan dimension.
-The steeper, $m_h$ and $m_m$ pitch-gains were found to produce the best results in this respect.
+Using a set of bone-conducting headphones, we found that a spatialised audio tone with a varying pitch can successfully convey the pan and tilt angles of a target.
+The angular errors made by the participants are in line with those from previous research using similar audio guidance instructions.
+We also found that varying the pitch's rate of change influences the accuracy of the system in the tilt dimension without affecting the performance in the pan dimension.
+The steeper, $m_h$ and $m_m$ pitch gradients were found to produce the best results in this respect.
 %Furthermore, we discovered a logarithmic relationship between the index of difficulty of a target and the time taken by a participant to find it, confirming that the results with our interface adhere to Fitts's Law.
@@
 Feedback from the participants with visual impairments was mostly positive and they agreed with the choice of bone-conduction headphones that do not inhibit normal hearing.
-However, they noted that the sine wave audio signal induced some audio fatigue, something noted by the other participants as well, and suggested suggested that more full-bodied, natural sounds be used instead.
+However, they noted that the sine wave audio signal induced audio fatigue after extended exposure, something noted by the other participants as well, and suggested that more full-bodied, natural sounds be used instead.
 Using vocal feedback in conjunction with the current audio signal was also suggested.
 
-Future research will focus on integrating voice and vibration feedback cues into the system.
-We are also investigating solutions to automatically refine the parameters of the HMI and better match the individual user's navigation habits and capability, thereby increasing navigation performance and user satisfaction.
+These results are more interesting from a design point of view than an end-user's. 
+Indeed, we have shown that this audio guidance interface is effective at driving an average person, but more data are needed with the intended audience (i.e.\ people with vision impairments) in order to decisively conclude that this interface will be effective in an indoor guidance system for people with vision impairments.
+Nevertheless, these data are a good indication of what to expect when we evaluate this audio interface with a greater number of people with limited vision.
+Once we have determined that the intended audience can effectively use this type of guidance instruction, we can start adding more user-orientated features (e.g.\ voice prompts, more pleasant tones, etc.) and star working on integrating it into our guidance system prototype.
+
+%Future research will focus on integrating voice and vibration feedback cues into the system.
+%We are also investigating solutions to automatically refine the parameters of the HMI and better match the individual user's navigation habits and capability, thereby increasing navigation performance and user satisfaction.
 

### 2019-05-15 article.tex
Fixed bib entry, re-added bib to paper

@@
 % For editing
-\usepackage{ulem}
+%\usepackage{ulem}
 \usepackage{todonotes}
@@
 
-\todo{chop up this section. Make anonymous}
-
-Earlier attempts at improving a person with visual impairment's navigation experience involved outfitting the commonly-used walking cane with remote detection systems, such as sonar, radar and RFID tags, to transform a cane into an early-warning system~\cite{ulrich1997,marion2008batcane,faria2010electric,willis2005}.
+Earlier attempts at improving a person with visual impairment's navigation experience involved outfitting the commonly-used walking cane with remote detection systems, such as sonar, radar and RFID tags, to transform a cane into an early-warning system~\cite{ulrich1997,marion2008batcane,faria2010electronic,willis2005}.
 Bluetooth tags and a smartphone can be used in a similar manner~\cite{sato2017navcog3}.
@@
 \bibliographystyle{ACM-Reference-Format}
-%\bibliography{bib}
+\bibliography{bib}
 

### 2019-05-15 article.tex
Added blurred image of participant

@@
 %\usepackage{ulem}
-\usepackage{todonotes}
+%\usepackage{todonotes}
 
@@
 
-To this end, we are developing a mobile navigation system using a Google Project Tango tablet device\footnote{https://developers.google.com/tango}, pictured in \cref{fig:tango-headphone}, that caters to the perception limitations of people with limited vision by using a non-visual interface.
+To this end, we are developing a mobile navigation system using a Google Project Tango tablet device\footnote{https://developers.google.com/tango}, pictured in \cref{fig:tango-headphone}, that caters to the perception limitations of people with vision impairments by using a non-visual interface.
 This system will ultimately allow users with visual impairments to reach a target location in the final leg of their journey, i.e.\ the so-called `last 10 yards' problem~\cite{google2016blind,bellotto2013}.
@@
 
-For this work, we implemented and evaluate an audio guidance mode that will be implemented in the guidance system to provide navigation instructions to the user. 
-To evaluate this guidance mode, we conducted a set of experiments involving a target-search task where the participants were guided to point a camera to a set of virtual targets with the audio instructions.
+For this work, we implement and evaluate an audio guidance interface that will be implemented in the guidance system to provide navigation instructions to the user. 
+To evaluate this guidance mode, we conducted a set of experiments involving a target-search task where the participants were guided with the audio instructions to point a camera at a set of virtual targets.
 The system uses a set of bone-conducting headphones to provide the audio instructions, with the latter being used to avoid interfering with a user's normal hearing function; something people with limited vision typically rely upon.
@@
 Computer vision-based systems provide a good compromise between usability, cost and accuracy.
-One increasingly popular solution is to use RGB-D depth sensing cameras, which are becoming increasingly accurate and cost-effective, to build a 3D image map of the environment, and guiding a user through it~\cite{lee2015, rodriguez2012obstacle}.
+One solution is to use RGB-D depth sensing cameras, which are becoming increasingly accurate and cost-effective, to build a 3D image map of the environment, and guiding a user through it~\cite{lee2015, rodriguez2012obstacle}.
 Alternatively, object recognition techniques can be used to detect various objects and landmarks, such as doors, staircases, etc., and communicate their relative location to the user~\cite{schauerte2012assistive, tian2013b, fiannaca2014headlock}, or use audio instructions to instruct a user with vision impairment to fully capture an object of interest~\cite{vazquez2012helping}.
@@
 An important feature of user-centric systems is a human-machine interface (HMI) that enables effective two-way communication between the system and the user.
-In previous surveys, researchers found that people with visual impairments prefer receiving instructions in the form of speech and haptic feedback cues~\cite{khoo2016multimodal, ross2000wearable, vazquez2012helping}.
+Surveys found that people with visual impairments prefer receiving instructions in the form of speech and haptic feedback cues~\cite{khoo2016multimodal, ross2000wearable, vazquez2012helping}.
 However, haptic feedback modes typically have a lower bandwidth when compared to audio feedback and also require the user to wear a special device in order to transmit the signals effectively.
@@
 \end{anonsuppress}
-The navigation system is based on a Google Tango tablet, an Android-based device that comes equipped with an RGB-D cameras to sense colour and depth.
-It combines an inertial measurement unit with powerful and robust landmark recognition and image processing algorithms to localise itself in real-time.
+The navigation system is based on a Google Tango tablet, an Android-based device that comes equipped with an RGB-D cameras to sense colour and depth and combines an inertial measurement unit with powerful and robust landmark recognition and image processing algorithms to localise itself in real-time.
 An added benefit of this platform is its familiar, compact form-factor which will help overcome the hurdle of user-acceptance and usability.
@@
 %For the series of experiments performed in this work, only the audio feedback mode was used to interface with the user.
-The audio component is responsible for conveying the 2D position of a target on the vertical plane, showed in \cref{fig:cam-coords}, in terms of pan and tilt angles.
+The audio component is responsible for conveying the 2D position of a target on the vertical plane, shown by \cref{fig:cam-coords}, in terms of pan and tilt angles.
 %In future system iterations, the distance to a target can be rendered by adjusting the audio signal's amplitude as a function of the distance.
-The audio signal is a continuous $\sim$\SI{10}{\hertz} sinusoidal sound wave that is played to the user through bone-conducting headphones.
+The audio signal is a continuous \SI{10}{\hertz} sinusoidal sound wave that is played to the user through bone-conducting headphones.
 We use a sinusoidal wave here because it is relatively simple to manipulate and analyse and will be replaced by a richer, more natural tone at a later stage.
@@
 
-We wish to determine how the gradient of the pitch gain as a function of $\theta$ (i.e.\ $m = \frac{df}{d\theta}$) affects a user's performance, e.g.\ does a greater $m$ lead to an increased target acquisition rate?
+We wish to determine how the gradient, $m$, of the pitch gain as a function of $\theta$ (i.e.\ $m = \frac{df}{d\theta}$) affects a user's performance, e.g.\ does a greater $m$ lead to an increased target acquisition rate?
 For this we select 3 different pitch settings, referred to henceforth as $m_l$, $m_m$ and $m_h$ for the smallest, middle and highest gain gradients respectively. 
@@
 The \SI{0}{\radian} position is directly in front of the user.
-With these limits, $f$ can be determined with \cref{eq:frequency}, where $m$ is the given setting's gradient, $\frac{df}{d\theta}$, and $c$ can be found using the current setting's pitch and angle limits.
+With these limits, $f$ can be determined with \cref{eq:frequency}, where $m$ is the given setting's gradient while $c$ can be found using the current setting's pitch and angle limits.
 
@@
 We conducted a set of experiments to evaluate the audio interface's effectiveness at driving a user to point the camera at a target in the pan and tilt dimensions.
-Furthermore, we wish to see how changes to $\frac{df}{d\theta}$ affect a user's performance.
+Furthermore, we wish to see how changes to $m$ affect a user's performance.
 
@@
 
-For the experiment, the participants were given a Tango tablet device, running an app written for this experiment, and a pair of AfterShockz Sportz3' bone conducting headphones (both pictured in \cref{fig:tango-headphone}) and were blindfolded where appropriate.
+For the experiment, the participants were given a Tango tablet device, running an app written for this experiment, and a pair of AfterShockz Sportz3' bone conducting headphones (both pictured in use in \cref{fig:participant}) and were blindfolded where appropriate.
 The app generates a virtual target, one at a time and a constant \SI{2}{\metre} from the participant, and uses the device's measurements to determine $\phi$ and $\theta$.
 These angles are then used to generate and present the user with the audio signal to direct them to the target. 
-As the participant rotates the camera, $\phi$ and $\theta$ are adjusted and the audio signal changes according to reflect the changes.
-When a participant was satisfied that they were on target, they tapped the screen which generated a new target target which they were then directed to. 
+As the participant rotates the camera, $\phi$ and $\theta$ are adjusted and the audio signal changes to reflect these changes.
+When a participant believed that they were pointing at the target, they tapped the screen which generated a new target target which they were then directed to. 
 Each participant was given 28 targets in total that were randomly generated and equally spread across 4 quadrants to avoid clustering. 
-After the 28 targets were found, the gradient setting ($m$ in \cref{eq:frequency}) was adjusted and the experiment was repeated. 
+After the 28 targets were found, $m$ was adjusted and the experiment was repeated. 
 The order in which the gradient setting was changed for each participant was randomised to minimise any the learning effect.
 The app streams various data on the current device and target poses to a laptop computer via a WiFi connection in real-time. 
-Before the experiment session started, each participant was given some time to familiarise themselves with the device and the audio tone and was given the oppertunity to learn what the $f_{512}$ `on-target' and on-centre tone sounds like that will confirm that they are level with the target.
+Before the experiment session started, each participant was given some time to familiarise themselves with the device and the audio tone and was given the opportunity to learn what the $f_{512}$ `on-target' and on-centre tone sounds like that will mean that they are pointing at the target.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\columnwidth]{figures/vi_participant.pdf}
+  \caption{A picture of the Tango device and bone-conducting headphones in use during an experiment.}\label{fig:participant}
+\end{figure}
 
 The measure of performance here is the accuracy with which a user points the camera towards a target.
-The accuracy is taken as the angular difference between the device's and target's poses at the time the participant tapped the screen and a smaller error would indicate more accurate results.
+The accuracy is taken as the angular difference between the device's and target's poses at the time the participant tapped the screen.
+A smaller error indicates more accurate results.
 The pan and tilt results are separated to understand the effect of changing the gradient setting has on either dimension's accuracy.
@@
 
-The results for the participants are given if the 2D histograms in \crefrange{fig:err-results-lo}{fig:err-results-hi}, where the pan error is on the abscissa and the tilt error on the ordinates.
+The results for the participants are given by the 2D histograms in \crefrange{fig:err-results-lo}{fig:err-results-hi}, where the pan error is on the abscissa and the tilt error on the ordinates.
 A set of box-plots of the angular errors' median and standard deviations are given in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} for the $m_l, m_m$ and $m_h$ settings. 
@@
   \centering
-  \includegraphics[clip, trim=20 -70 100 100, width=0.8\columnwidth]{figures/err_boxplot_medians.png}
+  \includegraphics[clip, trim=20 -70 100 100, width=1.0\columnwidth]{figures/err_boxplot_medians.png}
   \caption{Error medians for the pan and tilt dimension and each gradient setting.} \label{fig:err-boxplot-median}
@@
   \centering
-  \includegraphics[clip, trim=80 -70 100 0, width=0.8\columnwidth]{figures/err_boxplot_std.png}
+  \includegraphics[clip, trim=80 -70 100 0, width=1.0\columnwidth]{figures/err_boxplot_std.png}
   \caption{Error standard deviations for the pan and tilt dimensions and each gradient setting.}\label{fig:err-boxplot-std}
@@
 
-The data within the tilt dimension are also found to be non-normal following scored below the critical threshold from the Shapiro-Wilkes test.
+The data within the tilt dimension are also found to be non-normal following scores below the critical threshold from the Shapiro-Wilkes test.
 The Spearman test for the data reveals a reasonably significant correlation between the participants' guesses and the actual locations of the targets, with correlation scores of approximately 0.38 for $m_l$, 0.48 for $m_m$ and the $m_h$ gradient giving the strongest correlation score with 0.55 ($p < 0.01$ for all 3 settings).
@@
 Since the data are not normally spread and there is significant levels of noise within the data which may contaminate the mean values, we use the medians to analyse the datasets.
-For this, the Friedman test is used on the medians and it was found that there is a significant difference between the 3 settings' datasets ($p < 0.01$).
-A post-hoc analysis with a Wilcoxon signed rank test and a critical threshold with a Bonferroni correction applied for the 3 settings ($\alpha=0.016=\frac{0.05}{3}$) shows that both the $m_m$ and $m_h$ settings are significantly different from the $m_l$ setting ($p=0.0014<\alpha$ for both settings), but that the $m_m$ and $m_h$ settings do not produce significantly different results from one another ($p=0.42>\alpha$).
-This indicates there is an inflection point where increasing $\frac{df}{d\theta}$ produces diminishing returns and that we cannot conclude that the $m_h$ setting is better than the $m_m$ gradient.
+For this, the Friedman test is used on the participants' error medians and it was found that there is a significant difference between the 3 settings' datasets ($p < 0.01$).
+A post-hoc analysis with a Wilcoxon signed rank test and a critical threshold with a Bonferroni correction applied ($\alpha=0.016=\frac{0.05}{3}$) shows that both the $m_m$ and $m_h$ settings are significantly different from the $m_l$ setting ($p=0.0014<\alpha$ for both settings), but that the $m_m$ and $m_h$ settings do not produce significantly different results from one another ($p=0.42>\alpha$).
+This indicates there is an inflection point where increasing $m$ produces diminishing returns and that we cannot conclude that the $m_h$ setting is better than the $m_m$ gradient.
 However, both settings conclusively produce more accurate results than the $m_l$ setting.

### 2019-05-16 article.tex
Nicola edits

@@
 \usepackage{multirow}
+\usepackage{subcaption}
 \usepackage[capitalise]{cleveref}
@@
 	Such a system requires a non-visual feedback interface and in this paper we investigate the effectiveness of a spatial audio tone with a varying pitch component, played through bone-conducting headphones, in conveying the pan and tilt angles of a target to the user in a pointing task.
-	The goal is to determine how changes to the rate of change of the pitch affects a user's performance.
-	For this, we conducted a set of experiments with blindfolded and visually impaired users and found that the varying pitch component gives an average error of approximately \SI{20}{\degree} when searching for a target; in line with previous results from other authors.
+	The secondary goal is to determine how variations to the pitch rate of change of the pitch affects a user's performance.
+	For this, we conducted a set of experiments with blindfolded and user with visual impairments and found that, with some limitations, a spatialised audio tone with a varying pitch component can successfully convey a target's pan and tilt angles.
 \end{abstract} 
-
  \begin{CCSXML}
@@
 
-To this end, we are developing a mobile navigation system using a Google Project Tango tablet device\footnote{https://developers.google.com/tango}, pictured in \cref{fig:tango-headphone}, that caters to the perception limitations of people with vision impairments by using a non-visual interface.
+To this end, we are developing a mobile navigation system using a Google Project Tango tablet device\footnote{https://web.archive.org/web/20170714185918/https://developers.google.com/tango/}, pictured in \cref{fig:tango-headphone}, that caters to the perception limitations of people with vision impairments by using a non-visual interface.
 This system will ultimately allow users with visual impairments to reach a target location in the final leg of their journey, i.e.\ the so-called `last 10 yards' problem~\cite{google2016blind,bellotto2013}.
@@
 
+%\begin{figure}
+  %\centering
+  %\includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}
+  %\caption{The Tango device and bone-conducting headset the system is based on. }\label{fig:tango-headphone}
+%\end{figure}
 \begin{figure}
   \centering
-  \includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}
-  \caption{The Tango device and bone-conducting headset the system is based on. }\label{fig:tango-headphone}
+  \begin{subfigure}[t]{0.5\columnwidth}
+    \includegraphics[width=1.0\columnwidth]{figures/tango_headphone.png}
+    \caption{}\label{fig:tango-headphone}
+  \end{subfigure}%
+  ~
+  \begin{subfigure}[t]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figures/vi_participant.pdf}
+    \caption{}\label{fig:participant}
+  \end{subfigure}
+  \caption{Pictures of the Tango device and bone-conducting headphones the system is based on (left) and them in use in an experiment (right).}
 \end{figure}
@@
   \centering
-  \includegraphics[width=1.0\columnwidth]{figures/pitch_gain_functions.png}
-  \caption{The pitch gain functions for the 3 different gain settings. }\label{fig:pitch-gain}
+  \includegraphics[clip, trim=0 0 0 40, width=1.0\columnwidth]{figures/pitch_gain_functions.png}
+  \caption{The pitch gain functions for the 3 different gain settings ($y$-axis in log scale). }\label{fig:pitch-gain}
 \end{figure}
@@
 The \SI{0}{\radian} position is directly in front of the user.
-With these limits, $f$ can be determined with \cref{eq:frequency}, where $m$ is the given setting's gradient while $c$ can be found using the current setting's pitch and angle limits.
+With these limits, $f$ can be determined with
 
 \begin{equation}\label{eq:frequency}
-  f(\theta) = 2^{-m\theta + c}
+  f(\theta) = 2^{b\theta + c},
 \end{equation}
+
+where $b$ and $c$ for each setting can be calculated with the given setting's pitch and angle limits and a linear graph equation (i.e.\ $f - f_1 = b(\theta - \theta_1), b=\frac{\Delta f}{\Delta\theta}$).
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.4\columnwidth]{figures/vi_participant.pdf}
-  \caption{A picture of the Tango device and bone-conducting headphones in use during an experiment.}\label{fig:participant}
-\end{figure}
+%\begin{figure}
+  %\centering
+  %\includegraphics[width=0.4\columnwidth]{figures/vi_participant.pdf}
+  %\caption{A picture of the Tango device and bone-conducting headphones in use during an experiment.}\label{fig:participant}
+%\end{figure}
 
@@
 Furthermore, they suggested adding some voice component or tone prompt to confirm when they are on target, inform them of other important events or happenings or simply to intermittently assure them that the system is still active and that they are still on course.
-The former 2 suggestions were intentionally ignored in order to purely evaluate how accurately the audio tone can guide a user to the target.
-Going forward, however, these suggestions will be helpful for a commercial release version of the guidance system to make the guidance instructions clearer and to reassure users that the app has not crashed, for example.
+The former two suggestions were intentionally ignored in order to purely evaluate how accurately the audio tone can guide a user to the target.
+Going forward, however, these suggestions will be helpful for a potential commercial release version of the guidance system to make the guidance instructions clearer and to intermittently reassure users that they are still on the right course, for example.
 
@@
 These results are more interesting from a design point of view than an end-user's. 
-Indeed, we have shown that this audio guidance interface is effective at driving an average person, but more data are needed with the intended audience (i.e.\ people with vision impairments) in order to decisively conclude that this interface will be effective in an indoor guidance system for people with vision impairments.
+Indeed, we have shown that this audio guidance interface is effective at driving an average person, but more data are needed with the intended audience in order to decisively conclude that this interface will be effective in an indoor guidance system for people with vision impairments.
 Nevertheless, these data are a good indication of what to expect when we evaluate this audio interface with a greater number of people with limited vision.
-Once we have determined that the intended audience can effectively use this type of guidance instruction, we can start adding more user-orientated features (e.g.\ voice prompts, more pleasant tones, etc.) and star working on integrating it into our guidance system prototype.
+Once we have determined that the intended audience can effectively use this type of guidance instruction, we can start adding more user-oriented features (e.g.\ voice prompts, more pleasant tones, etc.) and integrate them into our guidance system prototype.
 

### 2019-05-16 article.tex
Minor edits to remote hanging lines

@@
 
-For this work, we implement and evaluate an audio guidance interface that will be implemented in the guidance system to provide navigation instructions to the user. 
+For this work, we implement and evaluate an audio interface that will be implemented in the guidance system to provide navigation instructions to the user. 
 To evaluate this guidance mode, we conducted a set of experiments involving a target-search task where the participants were guided with the audio instructions to point a camera at a set of virtual targets.
@@
 
-The remainder of this paper is organised as follows: \cref{sec:lit-review} gives an overview of existing navigation systems and audio interfaces for people living with visual impairments.
+The remainder of this paper is organised as follows: \cref{sec:lit-review} gives an overview of existing navigation systems and audio interfaces for people with visual impairments.
 \cref{sec:portable-navigation} discusses the navigation device's hardware and interface setup and describes how the target's position is conveyed to the user.
 The experiment we conducted are explained in \cref{sec:experiments} and the results are presented and discussed in \cref{sec:results}. 
-Finally, \cref{sec:conclusion} concludes this paper with a summary of the findings and comments on our future work.
+Finally, \cref{sec:conclusion} concludes this paper with a summary of the findings and comments on future work.
 
@@
 One solution is to use RGB-D depth sensing cameras, which are becoming increasingly accurate and cost-effective, to build a 3D image map of the environment, and guiding a user through it~\cite{lee2015, rodriguez2012obstacle}.
-Alternatively, object recognition techniques can be used to detect various objects and landmarks, such as doors, staircases, etc., and communicate their relative location to the user~\cite{schauerte2012assistive, tian2013b, fiannaca2014headlock}, or use audio instructions to instruct a user with vision impairment to fully capture an object of interest~\cite{vazquez2012helping}.
+Alternatively, object recognition techniques can be used to detect various objects and landmarks, such as doors, staircases, etc., and communicate their relative location to the user~\cite{schauerte2012assistive, tian2013b, fiannaca2014headlock}, or use audio instructions to guide a user to fully capture an object of interest~\cite{vazquez2012helping}.
 
@@
 \end{equation}
-
 where $b$ and $c$ for each setting can be calculated with the given setting's pitch and angle limits and a linear graph equation (i.e.\ $f - f_1 = b(\theta - \theta_1), b=\frac{\Delta f}{\Delta\theta}$).
@@
 
-The data collected from $G2$ follow a similar trend to that of $G1$: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all 3 settings.
+The data collected from $G2$ follow a similar trend to $G1$: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all 3 settings.
 These results are summarised in \cref{tab:vi-results}.
@@
 
-These results show that both groups managed to find the targets with reasonable level of accuracy and that the pan error is robust to changes to the pitch and its rate of change; a useful result in support of the effectiveness of this audio interface.
+These results show that both groups managed to find the targets with reasonable level of accuracy and that the pan error is robust to variations in the pitch's rate of change; a useful result in support of the effectiveness of this audio interface.
 
@@
 
-From \cref{fig:err-boxplot-median} it can also be seen that the data show a significant skewing to the negative side, indicating a potential bias amongst the experiment's participant-base that must be taken into account.
+From \cref{fig:err-boxplot-median} it can be seen that the data show a significant skewing to the negative side, indicating a potential bias amongst the experiment's participant-base that must be taken into account.
 From the results, it is not completely clear what causes this negative bias in the pitch dimension.

### 2019-05-16 article.tex
minor fixes

@@
 	Such a system requires a non-visual feedback interface and in this paper we investigate the effectiveness of a spatial audio tone with a varying pitch component, played through bone-conducting headphones, in conveying the pan and tilt angles of a target to the user in a pointing task.
-	The secondary goal is to determine how variations to the pitch rate of change of the pitch affects a user's performance.
+	The secondary goal is to determine how variations to the pitch rate of change affect the user's performance.
 	For this, we conducted a set of experiments with blindfolded and user with visual impairments and found that, with some limitations, a spatialised audio tone with a varying pitch component can successfully convey a target's pan and tilt angles.
@@
 
-To this end, we are developing a mobile navigation system using a Google Project Tango tablet device\footnote{https://web.archive.org/web/20170714185918/https://developers.google.com/tango/}, pictured in \cref{fig:tango-headphone}, that caters to the perception limitations of people with vision impairments by using a non-visual interface.
+To this end, we are developing a mobile navigation system using a Google Project Tango tablet device\footnote{\url{https://en.wikipedia.org/wiki/Tango_(platform)}}, pictured in \cref{fig:tango-headphone}, that caters to the perception limitations of people with vision impairments by using a non-visual interface.
 This system will ultimately allow users with visual impairments to reach a target location in the final leg of their journey, i.e.\ the so-called `last 10 yards' problem~\cite{google2016blind,bellotto2013}.
@@
 
-The audio is spatialised in the pan dimension using the OpenAL\footnote{http://openal.org} sound library's HRTF, while the tilt angle is conveyed by varying the audio tone's pitch.
+The audio is spatialised in the pan dimension using the OpenAL\footnote{\url{http://openal.org}} sound library's HRTF, while the tilt angle is conveyed by varying the audio tone's pitch.
 We use this approach because the external set of bone-conducting headphones plays the sound through a user's cheekbones instead of their outer ears, bypassing the ears' pennae that provide the ability to localise elevated sound sources~\cite{roffler1968factors, algazi2001elevation}.
@@
 
-We implement OpenAL's default HRTF, based on the MIT's KEMAR dataset\footnote{sound.media.mit.edu/resources/KEMAR.html}, to generate a sinusoidal sound wave based on the difference between the user and target's positions.
+We implement OpenAL's default HRTF, based on the MIT's KEMAR dataset\footnote{\url{http://sound.media.mit.edu/resources/KEMAR.html}}, to generate a sinusoidal sound wave based on the difference between the user and target's positions.
 The library takes position values as input and outputs a tone based on the angle between the two position vectors.
@@
 \end{equation}
-where $b$ and $c$ for each setting can be calculated with the given setting's pitch and angle limits and a linear graph equation (i.e.\ $f - f_1 = b(\theta - \theta_1), b=\frac{\Delta f}{\Delta\theta}$).
+where $b$ and $c$ for each setting can be calculated according to the given setting's pitch and angle limits.% and a linear graph equation (i.e.\ $f - f_1 = b(\theta - \theta_1), b=\frac{\Delta f}{\Delta\theta}$).
 

### 2019-05-20 article.tex
Added descriptions to Nicola's changes to rollback and fix a merge issue

@@
   \caption{Pictures of the Tango device and bone-conducting headphones the system is based on (left) and them in use in an experiment (right).}
+  \Description{A pictures of the Tango device and bone conducting headset and another of them both in-use. }
 \end{figure}
@@
   \caption{A diagram showing the device's frame of reference and the target's pan and tilt angles.}\label{fig:cam-coords}
+  \Description{A diagram of the device's frame of reference. }
 \end{figure}
@@
   \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }\label{fig:pipeline}
+  \Description{Diagram of the system pipeline.  }
 \end{figure}
@@
   \caption{The pitch gain functions for the 3 different gain settings ($y$-axis in log scale). }\label{fig:pitch-gain}
+  \Description{Plots showing the 3 different pitch gradient settings. }
 \end{figure}
@@
   \caption{Angular error data for the $m_l$ setting. }\label{fig:err-results-lo}
+  \Description{Angular error results for the low setting.}
 \end{figure}
@@
   \caption{Angular error data for the $m_m$ setting. }\label{fig:err-results-med}
+  \Description{Angular error results for the medium setting.}
 \end{figure}
@@
   \caption{Angular error data for and the $m_h$ setting. }\label{fig:err-results-hi}
+  \Description{Angular error results for the high setting.}
 \end{figure}
@@
   \caption{Error medians for the pan and tilt dimension and each gradient setting.} \label{fig:err-boxplot-median}
+  \Description{Angular error medians for each gradient setting. }
 \end{figure}
@@
   \caption{Error standard deviations for the pan and tilt dimensions and each gradient setting.}\label{fig:err-boxplot-std}
+  \Description{Angular error standard deviations for each gradient setting. }
 \end{figure}

### 2019-05-21 article.tex
Added template requirements

@@
 % Metadata Information
-\acmConference{SAP}{September 2019}{Barcelona}
+\acmConference[SAP '19]{Barcelona '19: ACM Symposium on Applied Perception}{September 2019}{Barcelona, Spain}
 %\acmVolume{9}
@@
 %Copyright
-\setcopyright{usgovmixed}
+\setcopyright{acmcopyright}
+\copyrightyear{2019}
 
@@
 \acmDOI{0000001.0000001}
+\acmYear{2019}
 
@@
 
-\title{Audio Interface of an Active Perception Navigation Aid for People with Visual Impairments}
+\title[Active Perception Interface for People with Visual Impairments]{Audio Interface of an Active Perception Navigation Aid for People with Visual Impairments}
 
@@
 
-\begin{abstract}
-	Our aim is to build a portable active navigation system for the visually impaired that uses active perception techniques and a combination of feedback modes to identify a scene and guide a user to their destination.
-	Such a system requires a non-visual feedback interface and in this paper we investigate the effectiveness of a spatial audio tone with a varying pitch component, played through bone-conducting headphones, in conveying the pan and tilt angles of a target to the user in a pointing task.
-	The secondary goal is to determine how variations to the pitch rate of change affect the user's performance.
-	For this, we conducted a set of experiments with blindfolded and user with visual impairments and found that, with some limitations, a spatialised audio tone with a varying pitch component can successfully convey a target's pan and tilt angles.
-\end{abstract} 
 \begin{CCSXML}
@@
 \renewcommand{\shortauthors}{JC Lock et al.}
+
+\begin{abstract}
+	Our aim is to build a portable active navigation system for the visually impaired that uses active perception techniques and a combination of feedback modes to identify a scene and guide a user to their destination.
+	Such a system requires a non-visual feedback interface and in this paper we investigate the effectiveness of a spatial audio tone with a varying pitch component, played through bone-conducting headphones, in conveying the pan and tilt angles of a target to the user in a pointing task.
+	The secondary goal is to determine how variations to the pitch rate of change affect the user's performance.
+	For this, we conducted a set of experiments with blindfolded and user with visual impairments and found that, with some limitations, a spatialised audio tone with a varying pitch component can successfully convey a target's pan and tilt angles.
+\end{abstract}
 

### 2019-05-21 article.tex
Minor edits, changed figures to subplots to keep the relevant figures groupoed together

@@
 \begin{abstract}
-	Our aim is to build a portable active navigation system for the visually impaired that uses active perception techniques and a combination of feedback modes to identify a scene and guide a user to their destination.
+	Our aim is to build a portable active navigation system for people with visual impairments that uses active perception techniques and a combination of feedback modes to identify a scene and guide a user to their destination.
 	Such a system requires a non-visual feedback interface and in this paper we investigate the effectiveness of a spatial audio tone with a varying pitch component, played through bone-conducting headphones, in conveying the pan and tilt angles of a target to the user in a pointing task.
-	The secondary goal is to determine how variations to the pitch rate of change affect the user's performance.
-	For this, we conducted a set of experiments with blindfolded and user with visual impairments and found that, with some limitations, a spatialised audio tone with a varying pitch component can successfully convey a target's pan and tilt angles.
+	The secondary goal is to determine how variations to the pitch's rate of change affect the user's performance.
+	For this, we conducted a set of experiments with both blindfolded participants and participants with visual impairments and found that, with some limitations, a spatialised audio tone with a varying pitch component can successfully convey a target's pan and tilt angles.
 \end{abstract}
@@
 In recent years, governments have spearheaded numerous initiatives to support people with disabilities and enable them to play a more active role in modern society.
-In the UK, the Royal National Institute of Blind People (RNIB) has prioritised enabling people with visual impairments to use some of the services and products many people take for granted, such as public transport and cellphones~\cite{rnib-objectives}.
-Improvements in modern computing have made it possible for new and innovative solutions for these problems to come to the fore.
+In the UK, the Royal National Institute of Blind People (RNIB) has prioritised enabling people with visual impairments to use some of the services and products many people take for granted, such as public transport and mobile apps~\cite{rnib-objectives}.
+Improvements in modern computing have made it possible for new and innovative solutions to these problems to come to the fore.
 In particular, researchers in the active vision field have have made much progress in enabling machines to autonomously manipulate cameras to gather information about an environment for mapping and object and face tracking tasks~\cite{bajcsy2018revisiting}.
@@
 
-%\begin{figure}
-  %\centering
-  %\includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}
-  %\caption{The Tango device and bone-conducting headset the system is based on. }\label{fig:tango-headphone}
-%\end{figure}
 \begin{figure}
@@
   \end{subfigure}
-  \caption{Pictures of the Tango device and bone-conducting headphones the system is based on (left) and them in use in an experiment (right).}
+  \caption{Pictures of the Tango device and bone-conducting headphones the system is based on (left) and both in use in an experiment (right).}
   \Description{A pictures of the Tango device and bone conducting headset and another of them both in-use. }
@@
 
-For this work, we implement and evaluate an audio interface that will be implemented in the guidance system to provide navigation instructions to the user. 
+For this work, we implement and evaluate an audio interface that will be integrated into the guidance system to provide navigation instructions to the user. 
 To evaluate this guidance mode, we conducted a set of experiments involving a target-search task where the participants were guided with the audio instructions to point a camera at a set of virtual targets.
@@
 However, they did not investigate this interface's target-finding accuracy.
-Furthermore, we wish to determine how changing the pitch's rate of change will affect target-finding performance. 
-Therefore, this work contributes by determining how accurately a spatialised tone with varying pitch can direct a user towards a target, and how the pitch's rate of change affects this accuracy.
+Furthermore, we wish to determine how modifying the pitch's rate of change will affect target-finding performance. 
+Therefore, this work contributes to the body of knowledge by determining how accurately a spatialised tone with varying pitch can direct a user towards a target, and how the pitch's rate of change affects this accuracy.
 
@@
 
-Our ultimate goal is to deliver a navigation system that can guide a user with visual impairments on the last leg of their journey, e.g.\ to a specific aisle and shelf in a shop, using only a mobile phone.
+Our ultimate goal is to deliver a navigation system that can guide a user with visual impairments on the last leg of their journey (e.g.\ to a specific aisle and shelf in a shop) using only a mobile phone.
 A large amount of data need to be translated from a visual form into a format that is useful to people with limited or no vision.
@@
 \end{anonsuppress}
-The navigation system is based on a Google Tango tablet, an Android-based device that comes equipped with an RGB-D cameras to sense colour and depth and combines an inertial measurement unit with powerful and robust landmark recognition and image processing algorithms to localise itself in real-time.
+The navigation system is based on a Google Tango tablet, an Android-based device that comes equipped with an RGB-D camera to sense colour and depth and combines an inertial measurement unit (IMU) with powerful and robust landmark recognition and image processing algorithms to localise itself in real-time.
 An added benefit of this platform is its familiar, compact form-factor which will help overcome the hurdle of user-acceptance and usability.
-We also use a set of bone-conducting headphones (see \cref{fig:tango-headphone}) that are placed externally on a user's head so that the system does not occlude the perception of real-world sounds and does not interfere with a user's normal hearing function.
+The guidance instructions are presented through a set of bone-conducting headphones (see \cref{fig:tango-headphone}) that are placed externally on a user's head so that the system does not occlude the perception of real-world sounds and does not interfere with a user's normal hearing function.
 %In the future, we will use multiple feedback modes to provide the user with navigation and obstacle avoidance instructions.
@@
 
-The system adjusts the tone's pitch ($f$) to convey the target's tilt angle ($\theta$) w.r.t.\ $C$, as shown in \cref{fig:cam-coords}. 
+The system adjusts the tone's pitch ($f$) to convey the target's tilt angle ($\theta$) w.r.t.\ $C$. 
 Here, a high pitch means the target is above $C$ (i.e.\ the user should look up) and a low pitch means the target is below $C$ (the user should look down).
@@
 For $m_m$, the $f_{max}$ and $f_{min}$ are set to 2 octaves higher and lower than $f_{512}$ (\SI{2048}{\hertz} and \SI{128}{\hertz}) and $m_h$ to 3 octaves higher and lower (\SI{4096}{\hertz} and \SI{64}{\hertz}).
-We selected these limits for practical reasons, given the fact that the bone conducting headphones we use have low volume gain at the frequency spectrum extremes, making it difficult to hear. 
+These limits were selected for practical reasons, because the bone conducting headphones have low volume gain at the frequency spectrum extremes, making it difficult to hear. 
 The values of $m_l, m_m, m_h$ are visualised in \cref{fig:pitch-gain}.
@@
 This group was blindfolded throughout the experiment and forms the bulk of the participant population.
-Group $G2$ is made up of 3 legally blind adults with varying levels of vision limits (3 males, average age of $40\pm8$ years). 
-This group makes up less than 10\% of the total population, but provided valuable subjective feedback that will help improve the system before evaluating it with a larger group of people with vision impairments.
-All participants joined the experiment on a voluntary basis with written consent and none have any other impairments that affects their interpretation of the audio guidance cues.
+Group $G2$ is made up of 3 legally blind adults with little to no light perception (3 males, average age of $40\pm8$ years). 
+This group makes up less than 10\% of the total experiment population, but provided valuable subjective feedback that will help improve the system before evaluating it with a larger group of people with vision impairments.
+All participants joined the experiment on a voluntary basis with written consent and have no other impairments that affected their interpretation of the audio guidance cues.
 
 For the experiment, the participants were given a Tango tablet device, running an app written for this experiment, and a pair of AfterShockz Sportz3' bone conducting headphones (both pictured in use in \cref{fig:participant}) and were blindfolded where appropriate.
-The app generates a virtual target, one at a time and a constant \SI{2}{\metre} from the participant, and uses the device's measurements to determine $\phi$ and $\theta$.
+The app generates a virtual target, one at a time at a constant \SI{2}{\metre} from the participant, and uses the device's pose measurements to determine $\phi$ and $\theta$.
 These angles are then used to generate and present the user with the audio signal to direct them to the target. 
 As the participant rotates the camera, $\phi$ and $\theta$ are adjusted and the audio signal changes to reflect these changes.
-When a participant believed that they were pointing at the target, they tapped the screen which generated a new target target which they were then directed to. 
+When a participant believes that they are pointing at the target, they tap the screen which generates a new target target which they are then directed to. 
 Each participant was given 28 targets in total that were randomly generated and equally spread across 4 quadrants to avoid clustering. 
 After the 28 targets were found, $m$ was adjusted and the experiment was repeated. 
-The order in which the gradient setting was changed for each participant was randomised to minimise any the learning effect.
+The order in which the gradient setting was changed for each participant was randomised to minimise the learning effect.
 The app streams various data on the current device and target poses to a laptop computer via a WiFi connection in real-time. 
-Before the experiment session started, each participant was given some time to familiarise themselves with the device and the audio tone and was given the opportunity to learn what the $f_{512}$ `on-target' and on-centre tone sounds like that will mean that they are pointing at the target.
+Before the experiment session started, each participant was given some time to familiarise themselves with the device and was given the opportunity to learn what the $f_{512}$ `on-target' and on-centre tone sounds like that will mean that they are pointing at the target.
 
@@
 The measure of performance here is the accuracy with which a user points the camera towards a target.
-The accuracy is taken as the angular difference between the device's and target's poses at the time the participant tapped the screen.
+The accuracy is taken as the angular difference between $C$ and the target's position at the time the participant tapped the screen.
 A smaller error indicates more accurate results.
@@
 
-The results for the participants are given by the 2D histograms in \crefrange{fig:err-results-lo}{fig:err-results-hi}, where the pan error is on the abscissa and the tilt error on the ordinates.
-A set of box-plots of the angular errors' median and standard deviations are given in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} for the $m_l, m_m$ and $m_h$ settings. 
+The results for the participants are given by the 2D histograms in \cref{fig:err-results}, where the pan error is on the abscissa and the tilt error on the ordinates.
+A set of box-plots of the angular errors' median and standard deviations are given in \cref{fig:err-boxplot} for the $m_l, m_m$ and $m_h$ settings. 
 The results for $G1$ are summarised in \cref{tab:results}, while the results for $G2$ are given in \cref{tab:vi-results}.
+
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_lo.png}
+  %\caption{Angular error data for the $m_l$ setting. }\label{fig:err-results-lo}
+  %\Description{Angular error results for the low setting.}
+%\end{figure}
+
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_med.png}
+  %\caption{Angular error data for the $m_m$ setting. }\label{fig:err-results-med}
+  %\Description{Angular error results for the medium setting.}
+%\end{figure}
+
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_hi.png}
+  %\caption{Angular error data for the $m_h$ setting. }\label{fig:err-results-hi}
+  %\Description{Angular error results for the high setting.}
+%\end{figure}
 
@@
   \centering
-  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_lo.png}
-  \caption{Angular error data for the $m_l$ setting. }\label{fig:err-results-lo}
-  \Description{Angular error results for the low setting.}
+  \begin{subfigure}[t]{0.8\columnwidth}
+    \centering
+    \includegraphics[clip, trim=450 0 450 110, width=1.0\columnwidth]{figures/err_lo.png}
+    \caption{Results for the $m_l$ setting. }\label{fig:err-results-lo}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.8\columnwidth}
+    \centering
+    \includegraphics[clip, trim=450 0 450 110, width=1.0\columnwidth]{figures/err_med.png}
+    \caption{Results for the $m_m$ setting. }\label{fig:err-results-med}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.8\columnwidth}
+    \centering
+    \includegraphics[clip, trim=450 0 450 110, width=1.0\columnwidth]{figures/err_hi.png}
+    \caption{Results for the $m_h$ setting. }\label{fig:err-results-hi}
+  \end{subfigure}
+  \caption{Angular error data for the 3 gradient settings. }\label{fig:err-results}
+  \Description{Angular error results  for the 3 different gradient settings.}
 \end{figure}
+
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=20 -70 100 100, width=1.0\columnwidth]{figures/err_boxplot_medians.png}
+  %\caption{Error medians for the pan and tilt dimension and each gradient setting.} \label{fig:err-boxplot-median}
+  %\Description{Angular error medians for each gradient setting. }
+%\end{figure}
+
+%\begin{figure}
+  %\centering
+  %\includegraphics[clip, trim=80 -70 100 0, width=1.0\columnwidth]{figures/err_boxplot_std.png}
+  %\caption{Error standard deviations for the pan and tilt dimensions and each gradient setting.}\label{fig:err-boxplot-std}
+  %\Description{Angular error standard deviations for each gradient setting. }
+%\end{figure}
 
@@
   \centering
-  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_med.png}
-  \caption{Angular error data for the $m_m$ setting. }\label{fig:err-results-med}
-  \Description{Angular error results for the medium setting.}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_hi.png}
-  \caption{Angular error data for and the $m_h$ setting. }\label{fig:err-results-hi}
-  \Description{Angular error results for the high setting.}
-\end{figure}
-
-\begin{figure}
+  \begin{subfigure}[t]{1.0\columnwidth}
     \centering
     \includegraphics[clip, trim=20 -70 100 100, width=1.0\columnwidth]{figures/err_boxplot_medians.png}
-  \caption{Error medians for the pan and tilt dimension and each gradient setting.} \label{fig:err-boxplot-median}
-  \Description{Angular error medians for each gradient setting. }
-\end{figure}
-
-\begin{figure}
+    \caption{The medians. }\label{fig:err-boxplot-median}
+  \end{subfigure}
+  \begin{subfigure}[t]{1.0\columnwidth}
     \centering
     \includegraphics[clip, trim=80 -70 100 0, width=1.0\columnwidth]{figures/err_boxplot_std.png}
-  \caption{Error standard deviations for the pan and tilt dimensions and each gradient setting.}\label{fig:err-boxplot-std}
-  \Description{Angular error standard deviations for each gradient setting. }
+    \caption{The standard deviations. }\label{fig:err-boxplot-std}
+  \end{subfigure}
+  \caption{Boxplots for the error medians and standard deviations. }\label{fig:err-boxplot}
+  \Description{A set of boxplots showing the spread of the error standard deviations and medians. }
 \end{figure}
@@
 
-\crefrange{fig:err-results-lo}{fig:err-results-hi} and the median and mean points from the box-plots in \crefrange{fig:err-boxplot-median}{fig:err-boxplot-std} show that the data in the pan dimension are approximately normally distributed around zero.
+\cref{fig:err-results} and the median and mean points from the boxplots in \cref{fig:err-boxplot} show that the data in the pan dimension are approximately normally distributed around zero.
 However, a Shapiro-Wilkes test score below the critical threshold do not give enough confidence to consider the data as normally distributed and we therefore analyse the data through non-parametric techniques.
@@
 The data collected from $G2$ follow a similar trend to $G1$: the error in the pan dimension is centred around \SI{0}{\radian} with similar standard deviations across all 3 settings.
-These results are summarised in \cref{tab:vi-results}.
+%These results are summarised in \cref{tab:vi-results}.
 Unfortunately, not enough samples could be collected to draw any final conclusions.
@@
 
-The data within the tilt dimension are also found to be non-normal following scores below the critical threshold from the Shapiro-Wilkes test.
+The data within the tilt dimension were also found to be non-normal following scores below the critical threshold from the Shapiro-Wilkes test.
 The Spearman test for the data reveals a reasonably significant correlation between the participants' guesses and the actual locations of the targets, with correlation scores of approximately 0.38 for $m_l$, 0.48 for $m_m$ and the $m_h$ gradient giving the strongest correlation score with 0.55 ($p < 0.01$ for all 3 settings).
@@
 
-From \cref{fig:err-boxplot-median} it can be seen that the data show a significant skewing to the negative side, indicating a potential bias amongst the experiment's participant-base that must be taken into account.
+From \cref{fig:err-boxplot-median} it can be seen that the median data show a significant skewing to the negative side, indicating a potential bias amongst the experiment's participant-base that must be taken into account.
 From the results, it is not completely clear what causes this negative bias in the pitch dimension.
-However, a possible explanation is that the floor introduces a position constraint within the participants' minds, since the target cannot appear below the ground.
-It can potentially appear above the participants' head though, giving variable upper an lower limits that depend on the participants' height and individual perception.
+However, a possible explanation is that the floor introduces a position constraint within a user's mind, since the target cannot appear below the ground.
+It can potentially appear above the user's head though, giving variable upper an lower limits that depend on the user's height and individual perception.
 Future improvements to our audio interface should consider a non-linear increase in pitch as a function of tilt angle instead of the linear one we used in this work to remedy this bias.
@@
 The results collected from $G1$ and $G2$ show that a varying pitch tone can convey the tilt angle of a target to a human using bone-conducting headphones with accuracy levels similar to that in literature~\cite{bujacz2011sonification, katz2011spatial, zotkin2004rendering}.
-They also highlight a clear and significant difference between the 3 different pitch gain gradients, with the $m_l$ setting giving the lowest acquisition accuracy, while $m_m$ and $m_h$ give similar accuracy levels closest to the true tilt.
+They also highlight a clear and significant difference between the 3 different pitch gain gradients, with the $m_l$ setting giving the lowest acquisition accuracy, while $m_m$ and $m_h$ give similar accuracy levels closest to the target's true tilt.
 
@@
 After the experiments with the participants with visual impairments in $G2$ were completed, we took the opportunity to collect their feedback on the audio interface's current implementation and gather suggestions for improvements for future iterations.
-When asked about their opinions on current assistive systems available on the market, the general consensus was that these systems are typically too prohibitively expensive, too complex and cumbersome to be useful for everyday use.
+When asked about their opinions on current assistive systems available on the market, the general consensus was that these systems are typically prohibitively expensive, too complex and cumbersome to be useful for everyday use.
 Indeed, they seemed quite enthusiastic about a guidance system that they can use on a mobile phone.
 
-They were also generally satisfied with the guidance interface in its current form and had little problem learning how to use it.
+They were generally satisfied with the guidance interface in its current form and had little problem learning how to use it.
 However, they, along with the participants in $G1$, reported auditory fatigue caused by long-term exposure to the sinusoidal audio tone.
@@
 For example, musical instruments can be used to play different notes and scales to indicate different elevation angles~\cite{brewster1998using}.
-Furthermore, they suggested adding some voice component or tone prompt to confirm when they are on target, inform them of other important events or happenings or simply to intermittently assure them that the system is still active and that they are still on course.
+Furthermore, they suggested adding some voice component or tone prompt to confirm when they are on target, inform them of other important events or happenings or simply to intermittently assure them that the system is still active.
 The former two suggestions were intentionally ignored in order to purely evaluate how accurately the audio tone can guide a user to the target.
@@
 In this work, we present an audio-based guidance interface that uses a spatialised audio tone with varying pitch to direct a user with visual impairments to point a camera toward a target. 
-We also present and discuss a set of experiments that were conducted  to determine the interface's effectiveness and performance, as well as some subjective feedback that was collected from participants with partial eyesight.
+We also present and discuss a set of experiments that were conducted to determine the interface's effectiveness and performance, as well as some subjective feedback that was collected from legally blind participants.
 
@@
 We also found that varying the pitch's rate of change influences the accuracy of the system in the tilt dimension without affecting the performance in the pan dimension.
-The steeper, $m_h$ and $m_m$ pitch gradients were found to produce the best results in this respect.
+The steeper, $m_h$ and $m_m$ pitch gradients were found to produce the best accuracy results in general.
 %Furthermore, we discovered a logarithmic relationship between the index of difficulty of a target and the time taken by a participant to find it, confirming that the results with our interface adhere to Fitts's Law.
@@
 These results are more interesting from a design point of view than an end-user's. 
-Indeed, we have shown that this audio guidance interface is effective at driving an average person, but more data are needed with the intended audience in order to decisively conclude that this interface will be effective in an indoor guidance system for people with vision impairments.
+Indeed, we have shown that this audio guidance interface is effective at directing an average person, but more data are needed with the intended audience in order to decisively conclude that this interface will be effective in an indoor guidance system for people with vision impairments.
 Nevertheless, these data are a good indication of what to expect when we evaluate this audio interface with a greater number of people with limited vision.
